### 2021-03-16 Manuscript/CC4.tex
manuscript

\documentclass[aps,prb,reprint,noshowkeys,superscriptaddress]{revtex4-1}
\usepackage{graphicx,dcolumn,bm,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,wrapfig,txfonts}
\usepackage[version=4]{mhchem}

\newcommand{\ie}{\textit{i.e.}}
\newcommand{\eg}{\textit{e.g.}}
\newcommand{\alert}[1]{\textcolor{black}{#1}}
\usepackage[normalem]{ulem}
\newcommand{\titou}[1]{\textcolor{red}{#1}}
\newcommand{\trashPFL}[1]{\textcolor{red}{\sout{#1}}}
\newcommand{\PFL}[1]{\titou{(\underline{\bf PFL}: #1)}}
\newcommand{\toto}[1]{\textcolor{green}{#1}}
\newcommand{\trashAS}[1]{\textcolor{green}{\sout{#1}}}
\newcommand{\AS}[1]{\toto{(\underline{\bf AS}: #1)}}

\newcommand{\Ec}{E_\text{c}}
\newcommand{\mEh}{$mE_h$}
\newcommand{\Eh}{$E_h$}
\newcommand{\mc}{\multicolumn}
\newcommand{\fnm}{\footnotemark}
\newcommand{\fnt}{\footnotetext}
\newcommand{\tabc}[1]{\multicolumn{1}{c}{#1}}
\newcommand{\QP}{\textsc{quantum package}}

\usepackage[
	colorlinks=true,
    citecolor=blue,
    breaklinks=true
	]{hyperref}
\urlstyle{same}

\begin{document}

\newcommand{\LCPQ}{Laboratoire de Chimie et Physique Quantiques (UMR 5626), Universit\'e de Toulouse, CNRS, UPS, France}
\newcommand{\CEISAM}{Universit\'e de Nantes, CNRS,  CEISAM UMR 6230, F-44000 Nantes, France}

\title{Reference correlation energies in finite Hilbert spaces: five- and six-membered rings}

\author{Micka\"el V\'eril}
\affiliation{\LCPQ}
\author{Yann Damour}
\affiliation{\LCPQ}
\author{Anthony Scemama}
\affiliation{\LCPQ}
\author{Denis Jacquemin}
\affiliation{\CEISAM}
\author{Pierre-Fran\c{c}ois Loos}
\email{loos@irsamc.ups-tlse.fr}
\affiliation{\LCPQ}

% Abstract
\begin{abstract}
We report (frozen-core) full configuration interaction (FCI) energies in finite Hilbert spaces for various five- and six-membered rings.
In the continuity of our recent work on the benzene molecule [\href{https://doi.org/10.1063/5.0027617}{J. Chem. Phys. \textbf{153}, 176101 (2020)}], itself motivated by the blind challenge of Eriksen \textit{et al.} [\href{https://doi.org/10.1021/acs.jpclett.0c02621}{J. Phys. Chem. Lett. \textbf{11}, 8922 (2020)}] on the same system, we report reference frozen-core correlation energies for twelve cyclic molecules (cyclopentadiene, furan, imidazole, pyrrole, thiophene, benzene, pyrazine, pyridazine, pyridine, pyrimidine, tetrazine, and triazine) in the standard correlation-consistent double-$\zeta$ Dunning basis set (cc-pVDZ).
This corresponds to Hilbert spaces with sizes ranging from $10^{20}$ (for thiophene) to $10^{36}$ (for benzene).
Our estimates are based on localized-orbital-based selected configuration interaction (SCI) calculations performed with the \textit{Configuration Interaction using a Perturbative Selection made Iteratively} (CIPSI) algorithm.
The performance and convergence properties of several series of methods are investigated. 
In particular, we study the convergence properties of ii) the M{\o}ller-Plesset perturbation series up to fifth-order (MP2, MP3, MP4, and MP5), ii) the iterative approximate single-reference coupled-cluster series CC2, CC3, and CC4, and ii) the single-reference coupled-cluster series CCSD, CCSDT, and CCSDTQ.
The performance of the ground-state gold standard CCSD(T) is also investigated.
\end{abstract}

% Title
\maketitle

\section{Introduction}

\begin{figure*}
	\includegraphics[width=\linewidth]{mol}
	\caption{
	Five-membered rings (top) and six-membered rings (bottom) considered in this study.
	\label{fig:mol}}
\end{figure*}

\section{Computational details}
The geometries of the twelve systems considered in the present study have been all obtained at the CC3/aug-cc-pVTZ level of geometry and have been extracted from a previous study. \cite{Loos_2020a}
The MP2, MP3, MP4, CC2, CC3, CC4, CCSD, CCSDT, and CCSDTQ calculations have been performed with Cfour, \cite{cfour} while the CCSD(T) and MP5 calculations have been performed in Gaussian 09. \cite{g09}
For all these calculations, we consider Dunning's correlation-consistent double-$\zeta$ basis (cc-pVDZ) which consists of Hilbert space sizes ranging from $10^{20}$ (for thiophene) to $10^{36}$ (for benzene).
We follow our usual procedure \cite{Scemama_2018,Scemama_2018b,Scemama_2019,Loos_2018a,Loos_2019,Loos_2020a,Loos_2020b,Loos_2020c} by performing a preliminary SCI calculation using Hartree-Fock orbitals in order to generate a SCI wave function with at least $10^7$ determinants.
Natural orbitals are then computed based on this wave function, and a second run is performed with localized orbitals.
This has the advantage to produce a smoother and faster convergence of the SCI energy toward the FCI limit by taking benefit of the local character of electron correlation.\cite{Angeli_2003,Angeli_2009,BenAmor_2011,Suaud_2017,Chien_2018,Eriksen_2020}
The Boys-Foster localization procedure \cite{Boys_1960} that we apply to the natural orbitals is performed in several orbital windows: i) core, ii) valence $\sigma$, iii) valence $\pi$, iv) valence $\pi^*$, v) valence $\sigma^*$, vi) the higher-lying $\sigma$ orbitals, and vii) the higher-lying $\pi$ orbitals. 
Like Pipek-Mezey, \cite{Pipek_1989} this choice of orbital windows allows to preserve a strict $\sigma$-$\pi$ separation in planar systems like benzene.

The total SCI energy is defined as the sum of the variational energy $E_\text{var.}$ (computed via diagonalization of the CI matrix in the reference space) and a second-order perturbative correction $E_\text{(r)PT2}$ which takes into account the external determinants, \ie, the determinants which do not belong to the variational space but are linked to the reference space via a nonzero matrix element. 
The magnitude of $E_\text{(r)PT2}$ provides a qualitative idea of the ``distance'' to the FCI limit.
We then linearly extrapolate the total SCI energy to $E_\text{(r)PT2} = 0$ (which effectively corresponds to the FCI limit). 
Note that, unlike excited-state calculations where it is important to enforce that the wave functions are eigenfunctions of the $\Hat{S}^2$ spin operator, \cite{Applencourt_2018} the present wave functions do not fulfil this property as we aim for the lowest possible energy of a singlet state. 
We have found that $\expval*{\Hat{S}^2}$ is, nonetheless, very close to zero for each system.

\section{Results and discussion}

\begin{table*}
	\caption{Total energy $E$ (in \Eh) and correlation energy $\Ec$ (in \mEh) for the frozen-core ground state of five-membered rings in the cc-pVDZ basis set.
	\label{tab:Tab5-VDZ}}
	\begin{ruledtabular}
	\begin{tabular}{lcccccccccc}
				&	\mc{2}{c}{Cyclopentadiene}	&	\mc{2}{c}{Furan}	&	\mc{2}{c}{Imidazole}	&	\mc{2}{c}{Pyrrole}	&	\mc{2}{c}{Thiophene}	\\
					\cline{2-3}	\cline{4-5}	\cline{6-7} \cline{8-9} \cline{10-11}
		Method	&	$E$&	$\Ec$	&	$E$	&	$\Ec$	&	$E$	&	$\Ec$	&	$E$	&	$\Ec$	&	$E$	&	$\Ec$ 	\\
		\hline
		HF		&	$-192.8083$	&				&	$-228.6433$	&				&	$-224.8354$	&				&	$-208.8286$	&		&	-551.3210	&	\\
		\hline
		MP2		&	$-193.4717$	&	$-663.4$	&	$-229.3508$	&	$-707.5$	&	$-225.5558$ &	$-720.4$	&	$-209.5243$	&	$-695.7$	&	$-551.9825$	 &	$-661.5$	\\
		MP3		&	$-193.5094$	&	$-701.0$	&	$-229.3711$	&	$-727.8$	&	$-225.5732$	&	$-737.8$	&	$-209.5492$	&	$-720.6$	&	$-552.0104$	&	$-689.4$	\\
		MP4		&	$-193.5428$	&	$-734.5$	&	$-229.4099$	&	$-766.6$	&	$-225.6126$	&	$-777.2$	&	$-209.5851$	&	$-756.5$	&	$-552.0476$	&	$-726.6$	\\
		MP5		&	$-193.5418$	&	$-733.4$	&	$-229.4032$	&	$-759.9$	&	$-225.6061$	&	$-770.8$	&	$-209.5809$	&	$-752.3$	&	$-552.0426$	&	$-721.6$\\	
		\hline
		CC2		&	$-193.4782$	&	$-669.9$	&	$-229.3605$	&	$-717.2$	&	$-225.5644$	&	$-729.0$	&	$-209.5311$	&	$-702.5$	&	$-551.9905$	&	$-669.5$	\\
		CC3		&	$-193.5449$	&	$-736.6$	&	$-229.4090$	&	$-765.7$	&	$-225.6115$	&	$-776.1$	&	$-209.5849$	&	$-756.3$	&	$-552.0473$	&	$-726.3$	\\
		CC4		&	$-193.5467$	&	$-738.4$	&	$-229.4102$	&	$-766.9$	&	$-225.6126$	&	$-777.2$	&	$-209.5862$	&	$-757.6$	&	$-552.0487$	&	$-727.7$	\\
		\hline
		CCSD	&	$-193.5156$	&	$-707.2$	&	$-229.3783$	&	$-735.0$	&	$-225.5796$	&	$-744.2$	&	$-209.5543$	&	$-725.7$	&	$-552.0155$	&	$-694.5$	\\
		CCSDT	&	$-193.5446$	&	$-736.2$	&	$-229.4076$	&	$-764.3$	&	$-225.6099$	&	$-774.6$	&	$-209.5838$	&	$-755.2$	&	$-552.0461$	&	$-725.1$	\\
		CCSDTQ	&	$-193.5465$	&	$-738.2$	&	$-229.4100$	&	$-766.7$	&	$-225.6123$	&	$-776.9$	&	$-209.5860$	&	$-757.4$	&	$-552.0485$	&	$-727.5$	\\	
		\hline
		CCSD(T)	&	$-193.5439$	&	$-735.6$	&	$-229.4073$	&	$-764.0$	&	$-225.6099$	&	$-774.5$	&	$-209.5836$	&	$-754.9$	&	$-552.0458$	&	$-724.8$
\\
		\hline
		CIPSI	&					&				&					&				&					&				&					&				&			&	\\	
	\end{tabular}
	\end{ruledtabular}
\end{table*}

\begin{squeezetable}
\begin{table*}
	\caption{Total energy $E$ (in \Eh) and correlation energy $\Ec$ (in \mEh) for the frozen-core ground state of six-membered rings in the cc-pVDZ basis set.
	\label{tab:Tab6-VDZ}}
	\begin{ruledtabular}
	\begin{tabular}{lcccccccccccccc}
				&	\mc{2}{c}{Benzene}	&	\mc{2}{c}{Pyrazine}	&	\mc{2}{c}{Pyridazine}	&	\mc{2}{c}{Pyridine}	&	\mc{2}{c}{Pyrimidine}	&	\mc{2}{c}{Tetrazine}	&	\mc{2}{c}{Triazine}	\\
					\cline{2-3}	\cline{4-5}	\cline{6-7} \cline{8-9} \cline{10-11} \cline{12-13} \cline{14-15}
	Method		&	$E$	&	$\Ec$	&	$E$	&	$\Ec$	&	$E$	&	$\Ec$	&	$E$	&	$\Ec$	
				&	$E$	&	$\Ec$	&	$E$	&	$\Ec$	&	$E$	&	$\Ec$	\\
	\hline
		HF		&	$-230.7222$	&			&	$-262.7030$	&			&	$-262.6699$	&			&	$-246.7152$	&			&	$-262.7137$	&			&	$-294.6157$		&		&	$-278.7173$	\\
		\hline
		MP2		&	$-231.5046$  	&	$-782.3$	&	$-263.5376$ 	&	$-834.6$ 	&	$-263.5086$ &	$-838.7$	&	$-247.5227$	&	$-807.5$	&	$-263.5437$   &	$-830.1$	&	$-295.5117$    &   $-895.9$	&			$-279.5678$   &   $-850.5$\\
		MP3		&	$-231.5386$	&	$-816.4$	&	$-263.5567$	&	$-853.7$	&	$-263.5271$	&	$-857.3$	&	$-247.5492$	&	$-834.0$	&	$-263.5633$	&	$-849.6$	&	$-295.5152$   &	$-899.5$	&	$-279.5809$   &	$-863.6$	\\
		MP4		&	$-231.5808$	&	$-858.5$	&	$-263.6059$	&	$-902.9$	&	$-263.5778$	&	$-907.9$	&	$-247.5951$	&	$-879.9$	&	$-263.6129$	&	$-899.3$	&	$-295.5743$	&  $-958.6$	&	$-279.6340$    &	$-916.7$	\\
		MP5		&	$-231.5760$   &          $-853.8$	&	$-263.5968$	&	$-893.8$	&	$-263.5681$	&	$-898.3$	&	$-247.5881$	&	$-872.9$	&	$-263.6036$ &            $-890.0$	&	$-295.5600$	&	$-944.3$	&	$-279.6228$	&	$-905.4$	\\
		\hline
		CC2		&	$-231.5117$  	&	$-789.4$	&	$-263.5475$	&	$-844.5$	&	$-263.5188$	&	$-848.9$	&	$-247.5315$   &	$-816.3$	&	$-263.5550$ 	&	$-841.3$	&	$-295.5247$    &   $-909.0$		&	$-279.5817$       &	$-864.4$	\\
		CC3		&	$-231.5814$	&	$-859.1$	&	$-263.6045$	&	$-901.5$	&	$-263.5761$	&	$-906.2$	&	$-247.5948$	&	$-879.6$	&	$-263.6120$	&	$-898.4$	&	$-295.5706$  &	$-954.9$	&	$-279.6329$    &	$-915.6$	\\
		CC4		&	$-231.5828$	&	$-860.6$	&	$-263.6056$	&	$-902.6$	&	$-263.5773$	&	$-907.5$	&	$-247.5960$		&	$-880.8$		&	$-263.6129$	&	$-899.3$		&	$-295.5716$	&	$-955.9$	&	$-279.6334$	&	$-916.1$			\\
		\hline
		CCSD	&	$-231.5440$	&	$-821.8$	&	$-263.5640$	&	$-861.0$	&	$-263.5347$	&	$-864.9$	&	$-247.5559$	&	$-840.7$	&	$-263.5716$	&	$-858.0$	&	$-295.5248$   &	$-909.1$	&	$-279.5911$   &	 $-873.8$	\\
		CCSDT	&	$-231.5802$	&	$-857.9$	&	$-263.6024$	&	$-899.4$	&	$-263.5739$	&	$-904.0$	&	$-247.5931$	&	$-877.9$	&	$-263.6097$	&	$-896.1$	&	$-295.5673$  &  $-951.6$	&	$-279.6300$    &	$-912.7$	\\
		CCSDTQ	&	$-231.5826$	&	$-860.4$		&	$-263.6053$	&	$-902.3$		&	$-263.5770$	&	$-907.1$	&	$-247.5960$	&	$-880.8$	&	$-263.6126$  & $-899.0$		&			$-295.5712$		&	$-955.4$		&	$-279.6331$		&	$-915.8$		\\
		\hline
		CCSD(T)	&	$-231.5798$	&	$-857.5$	&	$-263.6024$		&	$-899.4$	&	$-263.5740$	&	$-904.1$	&	$-247.5929$	&	$-877.7$	&	$-263.6099$	&	$-896.2$	&	$-295.5680$		&	$-952.2$	&	$-279.6305$		&	$-913.1$	\\
		\hline
		CIPSI	&				&			&				&			&				&			&				&			&				&			\\
	\end{tabular}
	\end{ruledtabular}
\end{table*}
\end{squeezetable}

\section{Conclusion}

\begin{acknowledgements}
This work was performed using HPC resources from GENCI-TGCC (2020-gen1738) and from CALMIP (Toulouse) under allocation 2020-18005.
PFL and AS have received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481).
\end{acknowledgements}

\section*{Data availability statement}
The data that support the findings of this study are openly available in Zenodo at \href{http://doi.org/XX.XXXX/zenodo.XXXXXXX}{http://doi.org/XX.XXXX/zenodo.XXXXXXX}.

\bibliography{Ec}

\end{document}

### 2021-03-16 Manuscript/CC4.tex
manuscript

@@
 
-\title{Reference correlation energies in finite Hilbert spaces: five- and six-membered rings}
+\title{How accurate is CC4 for vertical excitation energies?}
 
-\author{Micka\"el V\'eril}
-\affiliation{\LCPQ}
-\author{Yann Damour}
-\affiliation{\LCPQ}
-\author{Anthony Scemama}
-\affiliation{\LCPQ}
-\author{Denis Jacquemin}
-\affiliation{\CEISAM}
 \author{Pierre-Fran\c{c}ois Loos}
@@
 \affiliation{\LCPQ}
+\author{Denis Jacquemin}
+\email{Denis.Jacquemin@univ-nantes.fr}
+\affiliation{\CEISAM}
 
@@
 \begin{abstract}
-We report (frozen-core) full configuration interaction (FCI) energies in finite Hilbert spaces for various five- and six-membered rings.
-In the continuity of our recent work on the benzene molecule [\href{https://doi.org/10.1063/5.0027617}{J.
-Chem.
-Phys.
-\textbf{153}, 176101 (2020)}], itself motivated by the blind challenge of Eriksen \textit{et al.} [\href{https://doi.org/10.1021/acs.jpclett.0c02621}{J.
-Phys.
-Chem.
-Lett.
-\textbf{11}, 8922 (2020)}] on the same system, we report reference frozen-core correlation energies for twelve cyclic molecules (cyclopentadiene, furan, imidazole, pyrrole, thiophene, benzene, pyrazine, pyridazine, pyridine, pyrimidine, tetrazine, and triazine) in the standard correlation-consistent double-$\zeta$ Dunning basis set (cc-pVDZ).
-This corresponds to Hilbert spaces with sizes ranging from $10^{20}$ (for thiophene) to $10^{36}$ (for benzene).
-Our estimates are based on localized-orbital-based selected configuration interaction (SCI) calculations performed with the \textit{Configuration Interaction using a Perturbative Selection made Iteratively} (CIPSI) algorithm.
-The performance and convergence properties of several series of methods are investigated. 
-In particular, we study the convergence properties of ii) the M{\o}ller-Plesset perturbation series up to fifth-order (MP2, MP3, MP4, and MP5), ii) the iterative approximate single-reference coupled-cluster series CC2, CC3, and CC4, and ii) the single-reference coupled-cluster series CCSD, CCSDT, and CCSDTQ.
-The performance of the ground-state gold standard CCSD(T) is also investigated.
 \end{abstract}
@@
 
-\begin{figure*}
-	\includegraphics[width=\linewidth]{mol}
-	\caption{
-	Five-membered rings (top) and six-membered rings (bottom) considered in this study.
-	\label{fig:mol}}
-\end{figure*}
-
 \section{Computational details}
-The geometries of the twelve systems considered in the present study have been all obtained at the CC3/aug-cc-pVTZ level of geometry and have been extracted from a previous study. \cite{Loos_2020a}
-The MP2, MP3, MP4, CC2, CC3, CC4, CCSD, CCSDT, and CCSDTQ calculations have been performed with Cfour, \cite{cfour} while the CCSD(T) and MP5 calculations have been performed in Gaussian 09.
-\cite{g09}
-For all these calculations, we consider Dunning's correlation-consistent double-$\zeta$ basis (cc-pVDZ) which consists of Hilbert space sizes ranging from $10^{20}$ (for thiophene) to $10^{36}$ (for benzene).
-We follow our usual procedure \cite{Scemama_2018,Scemama_2018b,Scemama_2019,Loos_2018a,Loos_2019,Loos_2020a,Loos_2020b,Loos_2020c} by performing a preliminary SCI calculation using Hartree-Fock orbitals in order to generate a SCI wave function with at least $10^7$ determinants.
-Natural orbitals are then computed based on this wave function, and a second run is performed with localized orbitals.
-This has the advantage to produce a smoother and faster convergence of the SCI energy toward the FCI limit by taking benefit of the local character of electron correlation.\cite{Angeli_2003,Angeli_2009,BenAmor_2011,Suaud_2017,Chien_2018,Eriksen_2020}
-The Boys-Foster localization procedure \cite{Boys_1960} that we apply to the natural orbitals is performed in several orbital windows: i) core, ii) valence $\sigma$, iii) valence $\pi$, iv) valence $\pi^*$, v) valence $\sigma^*$, vi) the higher-lying $\sigma$ orbitals, and vii) the higher-lying $\pi$ orbitals.
-Like Pipek-Mezey, \cite{Pipek_1989} this choice of orbital windows allows to preserve a strict $\sigma$-$\pi$ separation in planar systems like benzene.
-
-The total SCI energy is defined as the sum of the variational energy $E_\text{var.}$ (computed via diagonalization of the CI matrix in the reference space) and a second-order perturbative correction $E_\text{(r)PT2}$ which takes into account the external determinants, \ie, the determinants which do not belong to the variational space but are linked to the reference space via a nonzero matrix element.
-The magnitude of $E_\text{(r)PT2}$ provides a qualitative idea of the ``distance'' to the FCI limit.
-We then linearly extrapolate the total SCI energy to $E_\text{(r)PT2} = 0$ (which effectively corresponds to the FCI limit). 
-Note that, unlike excited-state calculations where it is important to enforce that the wave functions are eigenfunctions of the $\Hat{S}^2$ spin operator, \cite{Applencourt_2018} the present wave functions do not fulfil this property as we aim for the lowest possible energy of a singlet state.
-We have found that $\expval*{\Hat{S}^2}$ is, nonetheless, very close to zero for each system.
 
@@
 	\begin{tabular}{lcccccccccc}
-				&	\mc{2}{c}{Cyclopentadiene}	&	\mc{2}{c}{Furan}	&	\mc{2}{c}{Imidazole}	&	\mc{2}{c}{Pyrrole}	&	\mc{2}{c}{Thiophene}	\\
-					\cline{2-3}	\cline{4-5}	\cline{6-7} \cline{8-9} \cline{10-11}
-		Method	&	$E$&	$\Ec$	&	$E$	&	$\Ec$	&	$E$	&	$\Ec$	&	$E$	&	$\Ec$	&	$E$	&	$\Ec$ 	\\
-		\hline
-		HF		&	$-192.8083$	&				&	$-228.6433$	&				&	$-224.8354$	&				&	$-208.8286$	&		&	-551.3210	&	\\
-		\hline
-		MP2		&	$-193.4717$	&	$-663.4$	&	$-229.3508$	&	$-707.5$	&	$-225.5558$ &	$-720.4$	&	$-209.5243$	&	$-695.7$	&	$-551.9825$	 &	$-661.5$	\\
-		MP3		&	$-193.5094$	&	$-701.0$	&	$-229.3711$	&	$-727.8$	&	$-225.5732$	&	$-737.8$	&	$-209.5492$	&	$-720.6$	&	$-552.0104$	&	$-689.4$	\\
-		MP4		&	$-193.5428$	&	$-734.5$	&	$-229.4099$	&	$-766.6$	&	$-225.6126$	&	$-777.2$	&	$-209.5851$	&	$-756.5$	&	$-552.0476$	&	$-726.6$	\\
-		MP5		&	$-193.5418$	&	$-733.4$	&	$-229.4032$	&	$-759.9$	&	$-225.6061$	&	$-770.8$	&	$-209.5809$	&	$-752.3$	&	$-552.0426$	&	$-721.6$\\	
-		\hline
-		CC2		&	$-193.4782$	&	$-669.9$	&	$-229.3605$	&	$-717.2$	&	$-225.5644$	&	$-729.0$	&	$-209.5311$	&	$-702.5$	&	$-551.9905$	&	$-669.5$	\\
-		CC3		&	$-193.5449$	&	$-736.6$	&	$-229.4090$	&	$-765.7$	&	$-225.6115$	&	$-776.1$	&	$-209.5849$	&	$-756.3$	&	$-552.0473$	&	$-726.3$	\\
-		CC4		&	$-193.5467$	&	$-738.4$	&	$-229.4102$	&	$-766.9$	&	$-225.6126$	&	$-777.2$	&	$-209.5862$	&	$-757.6$	&	$-552.0487$	&	$-727.7$	\\
-		\hline
-		CCSD	&	$-193.5156$	&	$-707.2$	&	$-229.3783$	&	$-735.0$	&	$-225.5796$	&	$-744.2$	&	$-209.5543$	&	$-725.7$	&	$-552.0155$	&	$-694.5$	\\
-		CCSDT	&	$-193.5446$	&	$-736.2$	&	$-229.4076$	&	$-764.3$	&	$-225.6099$	&	$-774.6$	&	$-209.5838$	&	$-755.2$	&	$-552.0461$	&	$-725.1$	\\
-		CCSDTQ	&	$-193.5465$	&	$-738.2$	&	$-229.4100$	&	$-766.7$	&	$-225.6123$	&	$-776.9$	&	$-209.5860$	&	$-757.4$	&	$-552.0485$	&	$-727.5$	\\	
-		\hline
-		CCSD(T)	&	$-193.5439$	&	$-735.6$	&	$-229.4073$	&	$-764.0$	&	$-225.6099$	&	$-774.5$	&	$-209.5836$	&	$-754.9$	&	$-552.0458$	&	$-724.8$
-\\
-		\hline
-		CIPSI	&					&				&					&				&					&				&					&				&			&	\\	
 	\end{tabular}
@@
 
-\begin{squeezetable}
-\begin{table*}
-	\caption{Total energy $E$ (in \Eh) and correlation energy $\Ec$ (in \mEh) for the frozen-core ground state of six-membered rings in the cc-pVDZ basis set.
-	\label{tab:Tab6-VDZ}}
-	\begin{ruledtabular}
-	\begin{tabular}{lcccccccccccccc}
-				&	\mc{2}{c}{Benzene}	&	\mc{2}{c}{Pyrazine}	&	\mc{2}{c}{Pyridazine}	&	\mc{2}{c}{Pyridine}	&	\mc{2}{c}{Pyrimidine}	&	\mc{2}{c}{Tetrazine}	&	\mc{2}{c}{Triazine}	\\
-					\cline{2-3}	\cline{4-5}	\cline{6-7} \cline{8-9} \cline{10-11} \cline{12-13} \cline{14-15}
-	Method		&	$E$	&	$\Ec$	&	$E$	&	$\Ec$	&	$E$	&	$\Ec$	&	$E$	&	$\Ec$	
-				&	$E$	&	$\Ec$	&	$E$	&	$\Ec$	&	$E$	&	$\Ec$	\\
-	\hline
-		HF		&	$-230.7222$	&			&	$-262.7030$	&			&	$-262.6699$	&			&	$-246.7152$	&			&	$-262.7137$	&			&	$-294.6157$		&		&	$-278.7173$	\\
-		\hline
-		MP2		&	$-231.5046$  	&	$-782.3$	&	$-263.5376$ 	&	$-834.6$ 	&	$-263.5086$ &	$-838.7$	&	$-247.5227$	&	$-807.5$	&	$-263.5437$   &	$-830.1$	&	$-295.5117$    &   $-895.9$	&			$-279.5678$   &   $-850.5$\\
-		MP3		&	$-231.5386$	&	$-816.4$	&	$-263.5567$	&	$-853.7$	&	$-263.5271$	&	$-857.3$	&	$-247.5492$	&	$-834.0$	&	$-263.5633$	&	$-849.6$	&	$-295.5152$   &	$-899.5$	&	$-279.5809$   &	$-863.6$	\\
-		MP4		&	$-231.5808$	&	$-858.5$	&	$-263.6059$	&	$-902.9$	&	$-263.5778$	&	$-907.9$	&	$-247.5951$	&	$-879.9$	&	$-263.6129$	&	$-899.3$	&	$-295.5743$	&  $-958.6$	&	$-279.6340$    &	$-916.7$	\\
-		MP5		&	$-231.5760$   &          $-853.8$	&	$-263.5968$	&	$-893.8$	&	$-263.5681$	&	$-898.3$	&	$-247.5881$	&	$-872.9$	&	$-263.6036$ &            $-890.0$	&	$-295.5600$	&	$-944.3$	&	$-279.6228$	&	$-905.4$	\\
-		\hline
-		CC2		&	$-231.5117$  	&	$-789.4$	&	$-263.5475$	&	$-844.5$	&	$-263.5188$	&	$-848.9$	&	$-247.5315$   &	$-816.3$	&	$-263.5550$ 	&	$-841.3$	&	$-295.5247$    &   $-909.0$		&	$-279.5817$       &	$-864.4$	\\
-		CC3		&	$-231.5814$	&	$-859.1$	&	$-263.6045$	&	$-901.5$	&	$-263.5761$	&	$-906.2$	&	$-247.5948$	&	$-879.6$	&	$-263.6120$	&	$-898.4$	&	$-295.5706$  &	$-954.9$	&	$-279.6329$    &	$-915.6$	\\
-		CC4		&	$-231.5828$	&	$-860.6$	&	$-263.6056$	&	$-902.6$	&	$-263.5773$	&	$-907.5$	&	$-247.5960$		&	$-880.8$		&	$-263.6129$	&	$-899.3$		&	$-295.5716$	&	$-955.9$	&	$-279.6334$	&	$-916.1$			\\
-		\hline
-		CCSD	&	$-231.5440$	&	$-821.8$	&	$-263.5640$	&	$-861.0$	&	$-263.5347$	&	$-864.9$	&	$-247.5559$	&	$-840.7$	&	$-263.5716$	&	$-858.0$	&	$-295.5248$   &	$-909.1$	&	$-279.5911$   &	 $-873.8$	\\
-		CCSDT	&	$-231.5802$	&	$-857.9$	&	$-263.6024$	&	$-899.4$	&	$-263.5739$	&	$-904.0$	&	$-247.5931$	&	$-877.9$	&	$-263.6097$	&	$-896.1$	&	$-295.5673$  &  $-951.6$	&	$-279.6300$    &	$-912.7$	\\
-		CCSDTQ	&	$-231.5826$	&	$-860.4$		&	$-263.6053$	&	$-902.3$		&	$-263.5770$	&	$-907.1$	&	$-247.5960$	&	$-880.8$	&	$-263.6126$  & $-899.0$		&			$-295.5712$		&	$-955.4$		&	$-279.6331$		&	$-915.8$		\\
-		\hline
-		CCSD(T)	&	$-231.5798$	&	$-857.5$	&	$-263.6024$		&	$-899.4$	&	$-263.5740$	&	$-904.1$	&	$-247.5929$	&	$-877.7$	&	$-263.6099$	&	$-896.2$	&	$-295.5680$		&	$-952.2$	&	$-279.6305$		&	$-913.1$	\\
-		\hline
-		CIPSI	&				&			&				&			&				&			&				&			&				&			\\
-	\end{tabular}
-	\end{ruledtabular}
-\end{table*}
-\end{squeezetable}
-
 \section{Conclusion}
@@
 \begin{acknowledgements}
-This work was performed using HPC resources from GENCI-TGCC (2020-gen1738) and from CALMIP (Toulouse) under allocation 2020-18005.
-PFL and AS have received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481).
+This work was performed using HPC resources from CALMIP (Toulouse) under allocation 2021-18005.
+PFL has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481).
 \end{acknowledgements}
@@
 The data that support the findings of this study are openly available in Zenodo at \href{http://doi.org/XX.XXXX/zenodo.XXXXXXX}{http://doi.org/XX.XXXX/zenodo.XXXXXXX}.
-
 \bibliography{Ec}

### 2021-03-24 Manuscript/CC4.tex
manuscript AVDZ

@@
 
+\begin{squeezetable}
 \begin{table*}
-	\caption{Total energy $E$ (in \Eh) and correlation energy $\Ec$ (in \mEh) for the frozen-core ground state of five-membered rings in the cc-pVDZ basis set.
-	\label{tab:Tab5-VDZ}}
+	\caption{Vertical excitation energies (in eV) of a selection of molecular excited states obtained at various levels of theory with the aug-cc-pVDZ and aug-cc-pVTZ basis sets.
+	\label{tab:BigTab}}
 	\begin{ruledtabular}
-	\begin{tabular}{lcccccccccc}
+	\begin{tabular}{llrrrrrrrrrrrr}
+				&		&	\mc{7}{c}{aug-cc-pVDZ}		&		\mc{5}{c}{aug-cc-pVTZ}		\\	
+				\cline{3-9} \cline{10-14}
+	Mol.	&	State				&CC3	&CCSDT-3&CCSDT	&CC4	&CCSDTQ	&CCSDTQP	&CIPSI	
+									&CC3	&CCSDT	&CC4	&CCSDTQ	&CIPSI			\\
+	\hline
+	\ce{NH3}	&	$^1A_2$ 		&6.464	&6.472	&6.462	&6.479	&6.480	&6.482	&6.483(1)	&6.573	&6.571	&6.585	&		\\	
+				&	$^1E$			&8.061	&8.065	&8.057	&8.078	&8.079	&8.081	&8.082(1)	&8.146	&8.143	&8.161	&		\\	
+				&	$^1A_1$ 		&9.664	&9.668	&9.659	&9.677	&9.677	&9.680	&9.681(8)	&9.318	&9.314	&9.331	&		\\
+				&	$^1A_2$ 		&10.396	&10.402	&10.391	&10.409	&10.409	&10.411	&10.412(1)	&9.945	&9.939	&9.957	&		\\
+	\ce{BH}		&	$^1\Pi$ 		&2.955	&2.958	&2.946	&2.947	&2.947	&2.947	&2.947(0)	&2.910	&2.900	&2.901	&2.901	&2.901(0)	\\
+	\ce{BF}		&	$^1\Pi$ 		&6.478	&6.491	&6.491	&6.484	&6.485	&6.485	&6.485(1)	&6.410	&6.423	&6.416	&6.417	\\
+	\ce{CO}		&	$^1\Pi$ 		&8.572	&8.591	&8.574	&8.562	&8.563	&8.561	&8.565(2)	&8.486	&8.492	&8.479	&		\\
+				&	$^1\Sigma^-$ 	&10.122	&10.112	&10.062	&10.055	&10.057	&10.057	&10.059(13)	&9.992	&9.940	&9.930	&		\\
+				&	$^1\Delta$ 		&10.225	&10.220	&10.178	&10.167	&10.169	&10.168	&10.171(2)	&10.119	&10.076	&10.064	&		\\
+				&	$^1\Sigma^+$ 	&10.917	&10.989	&10.944	&10.925	&10.926	&10.919	&			&10.943	&10.987	&10.961	&		\\
+				&	$^1\Sigma^+$ 	&11.483	&11.543	&11.518	&11.510	&11.510	&11.506	&			&11.489	&11.540	&11.521	&		\\
+				&	$^1\Pi$ 		&11.737	&11.802	&11.767	&11.757	&11.758	&11.753	&			&11.690	&11.737	&11.719	&		\\
+	\ce{N2}		&	$^1\Pi_g$  		&9.442	&9.450	&9.417	&9.409	&9.411	&9.409	&9.411(3)	&9.344	&9.326	&9.317	&9.319	\\
+				&	$^1\Sigma_u^-$	&10.059	&10.063	&10.060	&10.063	&10.055	&10.054	&10.054(0)	&9.885	&9.890	&9.883	&9.878	\\
+				&	$^1\Delta_u$ 	&10.433	&10.449	&10.436	&10.439	&10.430	&10.428	&10.429(0)	&10.293	&10.302	&10.294	&		\\
+				&	$^1\Sigma_g^+$	&13.229	&13.270	&13.202	&13.171	&13.182	&13.181	&			&13.013	&12.999	&12.962	&12.974\\
+				&	$^1\Pi_u$  		&13.279	&13.323	&13.174	&13.128	&13.131	&13.127	&			&13.223	&13.140	&13.091	&		\\
+				&	$^1\Sigma_u^+$	&13.146	&13.186	&13.130	&13.099	&13.109	&13.107	&			&13.120	&13.118	&13.078	&		\\
+				&	$^1\Pi_u$ 		&13.635	&13.663	&13.591	&13.551	&13.560	&13.558	&			&13.494	&13.455	&13.409	&13.419\\
+	\ce{HCl}	&	$^1\Pi$ 		&7.819	&7.828	&7.815	&7.822	&7.822	&7.823	&7.823(0)	&7.840	&7.834	&7.837	&7.837	\\
+	\ce{H2S}	&	$^1B_1$  		&6.098	&6.110	&6.098	&6.102	&6.103	&6.103	&6.103(1)	&6.240	&6.237	&6.238	&6.238	\\
+				&	$^1A_2$  		&6.293	&6.299	&6.286	&6.286	&6.286	&6.286	&6.286(0)	&6.192	&6.185	&6.181	&6.181	\\
+	\ce{H2O}	&	$^1B_1$  		&7.511	&7.510	&7.497	&7.531	&7.528	&7.532	&7.533(0)	&7.605	&7.591	&7.623	&7.620	\\
+				&	$^1A_2$  		&9.293	&9.291	&9.279	&9.317	&9.313	&9.318	&9.318(0)	&9.382	&9.368	&9.405	&9.400	\\
+				&	$^1A_1$  		&9.921	&9.919	&9.903	&9.940	&9.937	&9.941	&9.941(0)	&9.966	&9.949	&9.986	&9.981	\\
+	\hline
+	MAE			&					&	\\
 	\end{tabular}
@@
 \end{table*}
+\end{squeezetable}
 

### 2021-04-11 Manuscript/CC4.tex
update tex

--- 2021-03-16 Manuscript/CC4.tex
@@
 
+\begin{squeezetable}
 \begin{table*}
-	\caption{Total energy $E$ (in \Eh) and correlation energy $\Ec$ (in \mEh) for the frozen-core ground state of five-membered rings in the cc-pVDZ basis set.
-	\label{tab:Tab5-VDZ}}
+	\caption{Vertical excitation energies (in eV) of a selection of molecular excited states obtained at various levels of theory with the aug-cc-pVDZ and aug-cc-pVTZ basis sets.
+	\label{tab:BigTab}}
 	\begin{ruledtabular}
-	\begin{tabular}{lcccccccccc}
+	\begin{tabular}{llrrrrrrrrrrrr}
+				&		&	\mc{7}{c}{aug-cc-pVDZ}		&		\mc{5}{c}{aug-cc-pVTZ}		\\	
+				\cline{3-9} \cline{10-14}
+	Mol.	&	State				&CC3	&CCSDT-3&CCSDT	&CC4	&CCSDTQ	&CCSDTQP	&CIPSI	
+									&CC3	&CCSDT	&CC4	&CCSDTQ	&CIPSI			\\
+	\hline
+	\ce{NH3}	&	$^1A_2$ 		&6.464	&6.472	&6.462	&6.479	&6.480	&6.482	&6.483(1)	&6.573	&6.571	&6.585	&6.586	&	6.593(22)	\\	
+				&	$^1E$			&8.061	&8.065	&8.057	&8.078	&8.079	&8.081	&8.082(1)	&8.146	&8.143	&8.161	&8.161	&	8.171(20)	\\	
+				&	$^1A_1$ 		&9.664	&9.668	&9.659	&9.677	&9.677	&9.680	&9.681(8)	&9.318	&9.314	&9.331	&9.331	&	9.340(19)	\\
+				&	$^1A_2$ 		&10.396	&10.402	&10.391	&10.409	&10.409	&10.411	&10.412(1)	&9.945	&9.939	&9.957	&9.957	&	9.967(19)	\\
+	\ce{BH}		&	$^1\Pi$ 		&2.955	&2.958	&2.946	&2.947	&2.947	&2.947	&2.947(0)	&2.910	&2.900	&2.901	&2.901	&2.901(0)	\\
+	\ce{BF}		&	$^1\Pi$ 		&6.478	&6.491	&6.491	&6.484	&6.485	&6.485	&6.485(1)	&6.410	&6.423	&6.416	&6.417	&6.418(2)\\
+	\ce{CO}		&	$^1\Pi$ 		&8.572	&8.591	&8.574	&8.562	&8.563	&8.561	&8.565(2)	&8.486	&8.492	&8.479	&8.480	&	\\
+				&	$^1\Sigma^-$ 	&10.122	&10.112	&10.062	&10.055	&10.057	&10.057	&10.056(1)	&9.992	&9.940	&9.930	&9.932	&	\\
+				&	$^1\Delta$ 		&10.225	&10.220	&10.178	&10.167	&10.169	&10.168	&10.168(1)	&10.119	&10.076	&10.064	&10.066	&	\\
+				&	$^1\Sigma^+$ 	&10.917	&10.989	&10.944	&10.925	&10.926	&10.919	&			&10.943	&10.987	&10.961	&10.963	&	\\
+				&	$^1\Sigma^+$ 	&11.483	&11.543	&11.518	&11.510	&11.510	&11.506	&			&11.489	&11.540	&11.521	&11.523	&	\\
+				&	$^1\Pi$ 		&11.737	&11.802	&11.767	&11.757	&11.758	&11.753	&			&11.690	&11.737	&11.719	&11.720	&	\\
+	\ce{N2}		&	$^1\Pi_g$  		&9.442	&9.450	&9.417	&9.409	&9.411	&9.409	&9.411(3)	&9.344	&9.326	&9.317	&9.319	&	\\
+				&	$^1\Sigma_u^-$	&10.059	&10.063	&10.060	&10.063	&10.055	&10.054	&10.054(0)	&9.885	&9.890	&9.883	&9.878	&	\\
+				&	$^1\Delta_u$ 	&10.433	&10.449	&10.436	&10.439	&10.430	&10.428	&10.429(0)	&10.293	&10.302	&10.294	&10.287	&	\\
+				&	$^1\Sigma_g^+$	&13.229	&13.270	&13.202	&13.171	&13.182	&13.181	&13.180(1)	&13.013	&12.999	&12.962	&12.974	&	\\
+				&	$^1\Pi_u$  		&13.279	&13.323	&13.174	&13.128	&13.131	&13.127	&			&13.223	&13.140	&13.091	&13,095	&	\\
+				&	$^1\Sigma_u^+$	&13.146	&13.186	&13.130	&13.099	&13.109	&13.107	&			&13.120	&13.118	&13.078	&13.090	&	\\
+				&	$^1\Pi_u$ 		&13.635	&13.663	&13.591	&13.551	&13.560	&13.558	&			&13.494	&13.455	&13.409	&13.419\\
+	\ce{HCl}	&	$^1\Pi$ 		&7.819	&7.828	&7.815	&7.822	&7.822	&7.823	&7.823(0)	&7.840	&7.834	&7.837	&7.837	&7.838(1)\\
+	\ce{H2S}	&	$^1B_1$  		&6.098	&6.110	&6.098	&6.102	&6.103	&6.103	&6.103(1)	&6.240	&6.237	&6.238	&6.238	&6.240(7)\\
+				&	$^1A_2$  		&6.293	&6.299	&6.286	&6.286	&6.286	&6.286	&6.286(0)	&6.192	&6.185	&6.181	&6.181	&6.181(6) \\
+	\ce{H2O}	&	$^1B_1$  		&7.511	&7.510	&7.497	&7.531	&7.528	&7.532	&7.533(0)	&7.605	&7.591	&7.623	&7.620	&7.626(3)\\
+				&	$^1A_2$  		&9.293	&9.291	&9.279	&9.317	&9.313	&9.318	&9.318(0)	&9.382	&9.368	&9.405	&9.400	&9.407(7)\\
+				&	$^1A_1$  		&9.921	&9.919	&9.903	&9.940	&9.937	&9.941	&9.941(0)	&9.966	&9.949	&9.986	&9.981	&9.987(8)\\
+	\hline
+	MAE			&					&	\\
 	\end{tabular}

### 2021-05-01 Manuscript/CC4.tex
writing intro

@@
-\documentclass[aps,prb,reprint,noshowkeys,superscriptaddress]{revtex4-1}
-\usepackage{graphicx,dcolumn,bm,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,wrapfig,txfonts}
+\documentclass[aip,jcp,reprint,noshowkeys,superscriptaddress]{revtex4-1}
+\usepackage{graphicx,dcolumn,bm,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,wrapfig,txfonts,siunitx}
 \usepackage[version=4]{mhchem}
 
-\newcommand{\ie}{\textit{i.e.}}
-\newcommand{\eg}{\textit{e.g.}}
 \newcommand{\alert}[1]{\textcolor{black}{#1}}
@@
 \newcommand{\PFL}[1]{\titou{(\underline{\bf PFL}: #1)}}
-\newcommand{\toto}[1]{\textcolor{green}{#1}}
-\newcommand{\trashAS}[1]{\textcolor{green}{\sout{#1}}}
-\newcommand{\AS}[1]{\toto{(\underline{\bf AS}: #1)}}
 
-\newcommand{\Ec}{E_\text{c}}
-\newcommand{\mEh}{$mE_h$}
-\newcommand{\Eh}{$E_h$}
+\newcommand{\ie}{\textit{i.e.}}
+\newcommand{\eg}{\textit{e.g.}}
 \newcommand{\mc}{\multicolumn}
@@
 \newcommand{\tabc}[1]{\multicolumn{1}{c}{#1}}
+
+% Softwares
 \newcommand{\QP}{\textsc{quantum package}}
+\newcommand{\MRCC}{\textsc{mrcc}}
+\newcommand{\CFOUR}{\textsc{cfour}}
+
+% variables
+\newcommand{\hH}{\Hat{H}}
+\newcommand{\hT}{\Hat{T}}
+\newcommand{\bH}{\Bar{H}}
 
@@
 \newcommand{\LCPQ}{Laboratoire de Chimie et Physique Quantiques (UMR 5626), Universit\'e de Toulouse, CNRS, UPS, France}
+\newcommand{\SMU}{Department of Chemistry, Southern Methodist University, Dallas, Texas 75275, USA}
+\newcommand{\UOP}{Dipartimento di Chimica e Chimica Industriale, University of Pisa, Via Moruzzi 3, 56124 Pisa, Italy}
 \newcommand{\CEISAM}{Universit\'e de Nantes, CNRS,  CEISAM UMR 6230, F-44000 Nantes, France}
@@
 	\affiliation{\LCPQ}
+\author{Devin A.~Matthews}
+	\affiliation{\SMU}
+\author{Filippo Lipparini}
+	\affiliation{\UOP}
 \author{Denis Jacquemin}
@@
 \begin{abstract}
+\titou{Here comes the abstract.}
 \end{abstract}
@@
 
+The hierarchy of coupled cluster (CC) methods provide a route to systematically improvable energies and properties via the systematic increase of the maximum excitation degree of the cluster operator $\hT = \hT_1 + \hT_2 + \ldots + \hT_N$ (where $N$ is the number of electrons).
+Without any truncation, full CC (FCC) is equivalent to full configuration interaction (FCI) and provides the exact energy of the system. 
+However, it is not computationally viable and one usually resorts to truncated CC methods.
+Popular choices are CC with singles and doubles (CCSD), CC with singles, doubles, and triples (CCSDT), CC with singles, doubles, triples, and quadruples (CCSDTQ), and 
+CC with singles, doubles, triples, quadruples, and pentuples (CCSDTQP) with corresponding computational scalings of $\order*{M^{6}}$, $\order*{M^{8}}$,  $\order*{M^{10}}$, and  $\order*{M^{12}}$, respectively (where $M$ denotes the number of orbitals).
+An alternative systematically-improvable family of methods is provided by the CC2, CC3, and CC4 models which have been introduced by the Aarhus group in the context of CC response theory.
+These methods scale as $\order*{M^{5}}$, $\order*{M^{7}}$, and $\order*{M^{9}}$, respectively, and can be seen as a cheap approximation of CCSD, CCSDT, and CCSDTQ, by skipping the most expensive terms and avoiding the storage of the higher-excitation amplitudes.
+A similar strategy has been applied to produce the CCSDT-3 and CCSDTQ-3 models based on arguments stemming from perturbation theory.
+Of course, many more approximate CC methods have been developed and we refer the interested reader to specialized reviews for more details.
+
+Coupled-cluster methods have been particularly successful for small- and medium-sized molecules in the field of thermodynamics and spectroscopy, thanks to the computations of accurate geometries, potential energy surfaces, couplings between electronic states, a vast panel of properties such as oscillator strengths as well as ground- and excited-state dipoles.
+Although originally developed from ground-state energies and properties, CC has been successfully extended to excited states thanks to the equation-of-motion (EOM) and linear-response (LR) formalisms which are known to produce identical excitation energies but different properties.
+In EOM-CC, one obtains vertical excitation energies via the diagonalization of the similarity-transformed Hamiltonian $\bH = e^{-\hT} \hH e^{\hT}$.
+A more general procedure to compute excitation energies that can be straightforwardly applied to any truncated CC family as the ones mentioned above consists in diagonalizing the so-called CC Jacobian obtained via the differentiation of the CC amplitude equations.
+
+The purpose of the present study is to assess the accuracy of the approximate CC4 model against the most expensive CCSDTQ and CCSDTQP methods.
+near-FCI results.
+
 \section{Computational details}
 
+Each method used in the present study is reported in Table \ref{tab:scaling} alongside its formal computational scaling and the electronic structure software used to compute the excitation energies.
+
 \section{Results and discussion}
+
+\begin{table}
+	\caption{Methods considered, their formal computational scaling and the name of the electronic structure software where it has been implemented.
+	Here, $M$ is the number of orbitals.
+	\label{tab:scaling}}
+	\begin{ruledtabular}
+	\begin{tabular}{lccc}
+		Method	&	Scaling					&	Code		&	Ref.					\\
+		\hline
+		CC3			&	$\order*{M^{7}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
+		CCSDT-3		&	$\order*{M^{7}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
+		CCSDT		&	$\order*{M^{8}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
+		CC4			&	$\order*{M^{9}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
+		CCSDTQ-3	&	$\order*{M^{9}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
+		CCSDTQ		&	$\order*{M^{10}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
+		CCSDTQP		&	$\order*{M^{12}}$	&	\MRCC		&	\onlinecite{mrcc}		\\	
+		CIPSI		&	$\order*{e^{M}}$	&	\QP			&	\onlinecite{qp2}		\\
+	\end{tabular}
+	\end{ruledtabular}
+\end{table}
 
@@
 	\ce{N2}		&	$^1\Pi_g$  		&9.442	&9.450	&9.417	&9.409	&9.411	&9.409	&9.411(3)	&9.344	&9.326	&9.317	&9.319	&	\\
-				&	$^1\Sigma_u^-$	&10.059	&10.063	&10.060	&10.063	&10.055	&10.054	&10.054(0)	&9.885	&9.890	&9.883	&9.878	&	\\
-				&	$^1\Delta_u$ 	&10.433	&10.449	&10.436	&10.439	&10.430	&10.428	&10.429(0)	&10.293	&10.302	&10.294	&10.287	&	\\
+				&	$^1\Sigma_u^-$	&10.059	&10.063	&10.060	&10.063	&10.055	&10.054	&10.054(0)	&9.885	&9.890	&9.883	&9.878	&	9.879(4)\\
+				&	$^1\Delta_u$ 	&10.433	&10.449	&10.436	&10.439	&10.430	&10.428	&10.429(0)	&10.293	&10.302	&10.294	&10.287	&	10.289(12)\\
 				&	$^1\Sigma_g^+$	&13.229	&13.270	&13.202	&13.171	&13.182	&13.181	&13.180(1)	&13.013	&12.999	&12.962	&12.974	&	\\
@@
 				&	$^1A_2$  		&9.293	&9.291	&9.279	&9.317	&9.313	&9.318	&9.318(0)	&9.382	&9.368	&9.405	&9.400	&9.407(7)\\
-				&	$^1A_1$  		&9.921	&9.919	&9.903	&9.940	&9.937	&9.941	&9.941(0)	&9.966	&9.949	&9.986	&9.981	&9.987(8)\\
+				&	$^1A_1$  		&9.921	&9.919	&9.903	&9.940	&9.937	&9.941	&9.941(0)	&9.966	&9.949	&9.986	&9.981	&9.986(2)\\
 	\hline
@@
 
+\titou{Here comes the conclusion.}
+
 \begin{acknowledgements}
@@
 The data that support the findings of this study are openly available in Zenodo at \href{http://doi.org/XX.XXXX/zenodo.XXXXXXX}{http://doi.org/XX.XXXX/zenodo.XXXXXXX}.
-\bibliography{Ec}
+
+\bibliography{CC4}
 

### 2021-05-01 Manuscript/CC4.tex
CC4 data

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The hierarchy of coupled cluster (CC) methods provide a route to systematically improvable energies and properties via the systematic increase of the maximum excitation degree of the cluster operator $\hT = \hT_1 + \hT_2 + \ldots + \hT_N$ (where $N$ is the number of electrons).
+Coupled cluster (CC) theory provides a hierarchy of methods that provide systematically improvable energies and properties via the systematic increase of the maximum excitation degree of the cluster operator $\hT = \hT_1 + \hT_2 + \ldots + \hT_N$ (where $N$ is the number of electrons).
 Without any truncation, full CC (FCC) is equivalent to full configuration interaction (FCI) and provides the exact energy of the system. 
@@
 
-Coupled-cluster methods have been particularly successful for small- and medium-sized molecules in the field of thermodynamics and spectroscopy, thanks to the computations of accurate geometries, potential energy surfaces, couplings between electronic states, a vast panel of properties such as oscillator strengths as well as ground- and excited-state dipoles.
+Coupled-cluster methods have been particularly successful for small- and medium-sized molecules in the field of thermodynamics, kinetics, and spectroscopy, thanks to the computations of accurate geometries, potential energy surfaces, couplings between electronic states, a vast panel of properties such as dipoles and higher moments, vibrational frequencies, NMR chemical shifts, magnetizabilities, polarizabilities, etc.
 Although originally developed from ground-state energies and properties, CC has been successfully extended to excited states thanks to the equation-of-motion (EOM) and linear-response (LR) formalisms which are known to produce identical excitation energies but different properties.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Computational details}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 Each method used in the present study is reported in Table \ref{tab:scaling} alongside its formal computational scaling and the electronic structure software used to compute the excitation energies.
+In a nutshell, we have used by default the {\CFOUR} program to compute the CC energies at the notable exception of CCSDTQP where we have employed {\MRCC} and its automated implementation of high-order CC methods based on the strings of spin-orbital indices.
+The FCI estimates were obtained with the CIPSI algorithm implemented in {\QP}.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results and discussion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{acknowledgements}
@@
 \end{acknowledgements}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Data availability statement}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 The data that support the findings of this study are openly available in Zenodo at \href{http://doi.org/XX.XXXX/zenodo.XXXXXXX}{http://doi.org/XX.XXXX/zenodo.XXXXXXX}.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliography{CC4}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2021-05-01 Manuscript/CC4.tex
saving work

@@
 
-Coupled cluster (CC) theory provides a hierarchy of methods that provide systematically improvable energies and properties via the systematic increase of the maximum excitation degree of the cluster operator $\hT = \hT_1 + \hT_2 + \ldots + \hT_N$ (where $N$ is the number of electrons).
-Without any truncation, full CC (FCC) is equivalent to full configuration interaction (FCI) and provides the exact energy of the system. 
-However, it is not computationally viable and one usually resorts to truncated CC methods.
+Coupled cluster (CC) theory provides a hierarchy of methods which delivers increasingly accurate energies and properties via the systematic increase of the maximum excitation degree of the cluster operator $\hT = \hT_1 + \hT_2 + \ldots + \hT_n$ (where $n$ is the number of electrons).
+Without any truncation, the so-called full CC (FCC) method is equivalent to full configuration interaction (FCI), hence providing the exact energy and wave function of the system within a given basis set.
+However, it is not computationally viable due to its exponential scaling with system size, and one has to resort to truncated CC methods for computational convenience.
 Popular choices are CC with singles and doubles (CCSD), CC with singles, doubles, and triples (CCSDT), CC with singles, doubles, triples, and quadruples (CCSDTQ), and 
-CC with singles, doubles, triples, quadruples, and pentuples (CCSDTQP) with corresponding computational scalings of $\order*{M^{6}}$, $\order*{M^{8}}$,  $\order*{M^{10}}$, and  $\order*{M^{12}}$, respectively (where $M$ denotes the number of orbitals).
+CC with singles, doubles, triples, quadruples, and pentuples (CCSDTQP) with corresponding computational scalings of $\order*{N^{6}}$, $\order*{N^{8}}$,  $\order*{N^{10}}$, and  $\order*{N^{12}}$, respectively (where $N$ denotes the number of orbitals).
 An alternative systematically-improvable family of methods is provided by the CC2, CC3, and CC4 models which have been introduced by the Aarhus group in the context of CC response theory.
-These methods scale as $\order*{M^{5}}$, $\order*{M^{7}}$, and $\order*{M^{9}}$, respectively, and can be seen as a cheap approximation of CCSD, CCSDT, and CCSDTQ, by skipping the most expensive terms and avoiding the storage of the higher-excitation amplitudes.
+These methods scale as $\order*{N^{5}}$, $\order*{N^{7}}$, and $\order*{N^{9}}$, respectively, and can be seen as a cheap approximation of CCSD, CCSDT, and CCSDTQ, by skipping the most expensive terms and avoiding the storage of the higher-excitation amplitudes.
 A similar strategy has been applied to produce the CCSDT-3 and CCSDTQ-3 models based on arguments stemming from perturbation theory.
-Of course, many more approximate CC methods have been developed and we refer the interested reader to specialized reviews for more details.
+Of course, many more approximate CC models have been developed and we refer the interested reader to specialized reviews for more details.
 
-Coupled-cluster methods have been particularly successful for small- and medium-sized molecules in the field of thermodynamics, kinetics, and spectroscopy, thanks to the computations of accurate geometries, potential energy surfaces, couplings between electronic states, a vast panel of properties such as dipoles and higher moments, vibrational frequencies, NMR chemical shifts, magnetizabilities, polarizabilities, etc.
+Coupled-cluster methods have been particularly successful for small- and medium-sized molecules in the field of thermodynamics, kinetics, and spectroscopy, thanks to the computations of accurate geometries, potential energy surfaces, couplings between electronic states, and a vast panel of properties such as dipoles (and higher moments), vibrational frequencies, NMR chemical shifts, magnetizabilities, polarizabilities, etc.
 Although originally developed from ground-state energies and properties, CC has been successfully extended to excited states thanks to the equation-of-motion (EOM) and linear-response (LR) formalisms which are known to produce identical excitation energies but different properties.
 In EOM-CC, one obtains vertical excitation energies via the diagonalization of the similarity-transformed Hamiltonian $\bH = e^{-\hT} \hH e^{\hT}$.
-A more general procedure to compute excitation energies that can be straightforwardly applied to any truncated CC family as the ones mentioned above consists in diagonalizing the so-called CC Jacobian obtained via the differentiation of the CC amplitude equations.
+A more general procedure to compute excitation energies that can be straightforwardly applied to any approximate CC model (as the ones mentioned above) consists in diagonalizing the so-called CC Jacobian obtained via the differentiation of the CC amplitude equations.
 
@@
 	\caption{Methods considered, their formal computational scaling and the name of the electronic structure software where it has been implemented.
-	Here, $M$ is the number of orbitals.
+	Here, $N$ is the number of orbitals.
 	\label{tab:scaling}}
@@
 		\hline
-		CC3			&	$\order*{M^{7}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
-		CCSDT-3		&	$\order*{M^{7}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
-		CCSDT		&	$\order*{M^{8}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
-		CC4			&	$\order*{M^{9}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
-		CCSDTQ-3	&	$\order*{M^{9}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
-		CCSDTQ		&	$\order*{M^{10}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
-		CCSDTQP		&	$\order*{M^{12}}$	&	\MRCC		&	\onlinecite{mrcc}		\\	
-		CIPSI		&	$\order*{e^{M}}$	&	\QP			&	\onlinecite{qp2}		\\
+		CC3			&	$\order*{N^{7}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
+		CCSDT-3		&	$\order*{N^{7}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
+		CCSDT		&	$\order*{N^{8}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
+		CC4			&	$\order*{N^{9}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
+		CCSDTQ-3	&	$\order*{N^{9}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
+		CCSDTQ		&	$\order*{N^{10}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
+		CCSDTQP		&	$\order*{N^{12}}$	&	\MRCC		&	\onlinecite{mrcc}		\\	
+		CIPSI		&	$\order*{e^{N}}$	&	\QP			&	\onlinecite{qp2}		\\
 	\end{tabular}

### 2021-05-01 Manuscript/CC4.tex
CC data
saving work

@@
 
-% Softwares
+% softwares
 \newcommand{\QP}{\textsc{quantum package}}
@@
 \newcommand{\CFOUR}{\textsc{cfour}}
+\newcommand{\DALTON}{\textsc{dalton}}
 
@@
 \newcommand{\bH}{\Bar{H}}
+
+% excited states
+\newcommand{\npis}{n \to \pi^*}
+\newcommand{\pipis}{\pi \to \pi^*}
 
@@
 \author{Denis Jacquemin}
-	\email{Denis.Jacquemin@univ-nantes.fr}
+	\email{denis.jacquemin@univ-nantes.fr}
 	\affiliation{\CEISAM}
@@
 An alternative systematically-improvable family of methods is provided by the CC2, CC3, and CC4 models which have been introduced by the Aarhus group in the context of CC response theory.
-These methods scale as $\order*{N^{5}}$, $\order*{N^{7}}$, and $\order*{N^{9}}$, respectively, and can be seen as a cheap approximation of CCSD, CCSDT, and CCSDTQ, by skipping the most expensive terms and avoiding the storage of the higher-excitation amplitudes.
+These methods scale as $\order*{N^{5}}$, $\order*{N^{7}}$, and $\order*{N^{9}}$, respectively, and can be seen as cheaper approximations of CCSD, CCSDT, and CCSDTQ, by skipping the most expensive terms and avoiding the storage of the higher-excitation amplitudes.
 A similar strategy has been applied to produce the CCSDT-3 and CCSDTQ-3 models based on arguments stemming from perturbation theory.
@@
 In EOM-CC, one obtains vertical excitation energies via the diagonalization of the similarity-transformed Hamiltonian $\bH = e^{-\hT} \hH e^{\hT}$.
-A more general procedure to compute excitation energies that can be straightforwardly applied to any approximate CC model (as the ones mentioned above) consists in diagonalizing the so-called CC Jacobian obtained via the differentiation of the CC amplitude equations.
+A more general procedure to compute excitation energies that can be applied to any approximate CC model consists in diagonalizing the so-called CC Jacobian obtained via the differentiation of the CC amplitude equations.
 
-The purpose of the present study is to assess the accuracy of the approximate CC4 model against the most expensive CCSDTQ and CCSDTQP methods.
-near-FCI results.
+\titou{Here comes the paragraph on SCI methods.}
+
+The main purpose of the present study is to assess the relative accuracy of the approximate CC4 model against the most expensive CCSDTQ and CCSDTQP methods in the case of vertical excitation energies.
+We are also interested in its absolute accuracy with respect to FCI.
+To do so, we consider a set of 8 small molecules (\ce{NH3}, \ce{BH}, \ce{BF}, \ce{CO}, \ce{N2}, \ce{HCl}, \ce{H2S}, and \ce{H2O}) and we compare the excitation energies associated with 25 singlet excited states of various natures ($\npis$, $\pipis$, Rydberg, valence, charge-transfer, \ldots) and spatial symmetries obtained with various high-level CC methods.
+Although several studies have been published on the performance of CC4 for ground-state energies and properties, to the best of our knowledge, CC4 has never been used to compute excited-states energies before.
+As we shall see below, CC4 is an excellent approximation to its CCSDTQ parent, and produces excitation energies with sub-kJ/mol accuracy, well below the chemical accuracy threshold.
 
@@
 The FCI estimates were obtained with the CIPSI algorithm implemented in {\QP}.
+The present {\CFOUR} calculations have been performed with the new and very fast CC module (\texttt{xncc}) written by one of author (DAM) which couples a general algebraic
+and graphical interpretation of the non-orthogonal spin-adaptation approach with highly efficient storage format and set of implementation techniques designed to minimize data movement and to avoid costly tensor transposes.
+
+\titou{The error bars at the CIPSI level have been computed using our recently-developed protocol presented in Ref.~\cite{QUEST}.
+Two basis sets are used (aug-cc-pVDZ and aug-cc-pVTZ). 
+For the small ones, we could compute CCSDTQP energies but not in the larger one.}
 
@@
 		\hline
-		CC3			&	$\order*{N^{7}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
+		CC3			&	$\order*{N^{7}}$	&	\DALTON		&	\onlinecite{dalton}		\\
 		CCSDT-3		&	$\order*{N^{7}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
@@
 				\cline{3-9} \cline{10-14}
-	Mol.	&	State				&CC3	&CCSDT-3&CCSDT	&CC4	&CCSDTQ	&CCSDTQP	&CIPSI	
-									&CC3	&CCSDT	&CC4	&CCSDTQ	&CIPSI			\\
+	Mol.	&	State				&CC3	&CCSDT-3&CCSDT	&CC4	&CCSDTQ	&CCSDTQP	&FCI	
+									&CC3	&CCSDT	&CC4	&CCSDTQ	&FCI			\\
 	\hline

### 2021-05-02 Manuscript/CC4.tex
saving work

@@
 
-Coupled cluster (CC) theory provides a hierarchy of methods which delivers increasingly accurate energies and properties via the systematic increase of the maximum excitation degree of the cluster operator $\hT = \hT_1 + \hT_2 + \ldots + \hT_n$ (where $n$ is the number of electrons).
-Without any truncation, the so-called full CC (FCC) method is equivalent to full configuration interaction (FCI), hence providing the exact energy and wave function of the system within a given basis set.
-However, it is not computationally viable due to its exponential scaling with system size, and one has to resort to truncated CC methods for computational convenience.
+Single-reference coupled-cluster (CC) theory provides a hierarchy of size-extensive methods which delivers increasingly accurate energies and properties via the systematic increase of the maximum excitation degree of the cluster operator $\hT = \hT_1 + \hT_2 + \ldots + \hT_k$ (where $k \ge n$ and $n$ is the number of electrons).
+Without any truncation (\ie, $k = n$), the so-called full CC (FCC) method is equivalent to full configuration interaction (FCI), hence providing the exact energy and wave function of the system within a given basis set.
+However, it is not computationally viable due to its exponential scaling with system size, and one has to resort to truncated CC methods  (\ie, $k \ll n$) for computational convenience.
 Popular choices are CC with singles and doubles (CCSD), CC with singles, doubles, and triples (CCSDT), CC with singles, doubles, triples, and quadruples (CCSDTQ), and 
 CC with singles, doubles, triples, quadruples, and pentuples (CCSDTQP) with corresponding computational scalings of $\order*{N^{6}}$, $\order*{N^{8}}$,  $\order*{N^{10}}$, and  $\order*{N^{12}}$, respectively (where $N$ denotes the number of orbitals).
-An alternative systematically-improvable family of methods is provided by the CC2, CC3, and CC4 models which have been introduced by the Aarhus group in the context of CC response theory.
+An alternative, systematically-improvable family of methods is defined by the CC2, CC3, and CC4 series of models which have been introduced by the Aarhus group in the context of CC response theory.
 These methods scale as $\order*{N^{5}}$, $\order*{N^{7}}$, and $\order*{N^{9}}$, respectively, and can be seen as cheaper approximations of CCSD, CCSDT, and CCSDTQ, by skipping the most expensive terms and avoiding the storage of the higher-excitation amplitudes.
-A similar strategy has been applied to produce the CCSDT-3 and CCSDTQ-3 models based on arguments stemming from perturbation theory.
+A somehow similar strategy has been applied to produce the CCSDT-3 and CCSDTQ-3 models based on arguments stemming from perturbation theory.
 Of course, many more approximate CC models have been developed and we refer the interested reader to specialized reviews for more details.
@@
 Coupled-cluster methods have been particularly successful for small- and medium-sized molecules in the field of thermodynamics, kinetics, and spectroscopy, thanks to the computations of accurate geometries, potential energy surfaces, couplings between electronic states, and a vast panel of properties such as dipoles (and higher moments), vibrational frequencies, NMR chemical shifts, magnetizabilities, polarizabilities, etc.
-Although originally developed from ground-state energies and properties, CC has been successfully extended to excited states thanks to the equation-of-motion (EOM) and linear-response (LR) formalisms which are known to produce identical excitation energies but different properties.
-In EOM-CC, one obtains vertical excitation energies via the diagonalization of the similarity-transformed Hamiltonian $\bH = e^{-\hT} \hH e^{\hT}$.
-A more general procedure to compute excitation energies that can be applied to any approximate CC model consists in diagonalizing the so-called CC Jacobian obtained via the differentiation of the CC amplitude equations.
+Although originally developed for ground-state energies and properties, CC has been successfully extended to excited states thanks to the equation-of-motion (EOM) and linear-response (LR) formalisms which are known to produce identical excitation energies but different properties.
+In EOM-CC, one determines vertical excitation energies via the diagonalization of the similarity-transformed Hamiltonian $\bH = e^{-\hT} \hH e^{\hT}$.
+A more general procedure to compute excitation energies that can be applied to any approximate CC model (as the ones mentioned above) consists in diagonalizing the so-called CC Jacobian obtained via the differentiation of the CC amplitude equations.
+Again, by systematically increasing the maximum excitation degree of $\hT$, one can systematically produce increasingly accurate excitation energies with the ``complete'' series CCSD, CCSDT, CCSDTQ, CCSDTP, \ldots or the ``approximate'' series CC2, CC3, CC4, \ldots while retaining the formal scaling of their ground-state analog.
 
-\titou{Here comes the paragraph on SCI methods.}
+Recently, a large collection of deterministic, stochastic or hybrid selected CI (SCI) methods has (re)appeared in the electronic structure landscape providing an alternative route to highly-accurate ground- and excited-state energies.
+The general idea behind SCI methods is simple: rather than exploring the entire FCI space by systematically increasing the maximum excitation degree of the determinants taken into account (leading to the slowly convergent and size-inconsistent series of methods CISD, CISDT, CISDTQ, \ldots), one performs a sparse exploration of the FCI space by selecting only the most energetically-important determinants thanks to a suitable criterion usually based on perturbation theory.
+By iteratively increasing the number of determinants of the variational space and supplemented it with a second-order perturbative correction (PT2), the SCI+PT2 family of methods has been recently shown to produce near-FCI correlation and excitation energies for small- and medium-size molecules in compact basis sets.
+
+Taking advantage of the high accuracy of CC and SCI+PT2 methods, we have very recently created a large dataset of more than 500 highly-accurate vertical excitation energies of various natures in small- and medium-sized molecules, many of which can be reasonably considered as chemically accurate (\ie, within $1$ kcal.mol$^{-1}$ of the FCI limit).
 
@@
 
-\titou{The error bars at the CIPSI level have been computed using our recently-developed protocol presented in Ref.~\cite{QUEST}.
+\titou{The error bars at the CIPSI level have been computed using our recently-developed protocol presented in Ref.~\onlinecite{Veril_2021}.
 Two basis sets are used (aug-cc-pVDZ and aug-cc-pVTZ). 
@@
 	\begin{ruledtabular}
-	\begin{tabular}{llrrrrrrrrrrrr}
-				&		&	\mc{7}{c}{aug-cc-pVDZ}		&		\mc{5}{c}{aug-cc-pVTZ}		\\	
-				\cline{3-9} \cline{10-14}
-	Mol.	&	State				&CC3	&CCSDT-3&CCSDT	&CC4	&CCSDTQ	&CCSDTQP	&FCI	
-									&CC3	&CCSDT	&CC4	&CCSDTQ	&FCI			\\
+	\begin{tabular}{llrrrrrrrrrrrrrr}
+				&		&	\mc{8}{c}{aug-cc-pVDZ}		&		\mc{6}{c}{aug-cc-pVTZ}		\\	
+				\cline{3-10} \cline{11-16}
+	Mol.	&	State				&CCSD	&CC3	&CCSDT-3&CCSDT	&CC4	&CCSDTQ	&CCSDTQP	&FCI	
+									&CCSD	&CC3	&CCSDT	&CC4	&CCSDTQ	&FCI			\\
 	\hline
-	\ce{NH3}	&	$^1A_2$ 		&6.464	&6.472	&6.462	&6.479	&6.480	&6.482	&6.483(1)	&6.573	&6.571	&6.585	&6.586	&	6.593(22)	\\	
-				&	$^1E$			&8.061	&8.065	&8.057	&8.078	&8.079	&8.081	&8.082(1)	&8.146	&8.143	&8.161	&8.161	&	8.171(20)	\\	
-				&	$^1A_1$ 		&9.664	&9.668	&9.659	&9.677	&9.677	&9.680	&9.681(8)	&9.318	&9.314	&9.331	&9.331	&	9.340(19)	\\
-				&	$^1A_2$ 		&10.396	&10.402	&10.391	&10.409	&10.409	&10.411	&10.412(1)	&9.945	&9.939	&9.957	&9.957	&	9.967(19)	\\
-	\ce{BH}		&	$^1\Pi$ 		&2.955	&2.958	&2.946	&2.947	&2.947	&2.947	&2.947(0)	&2.910	&2.900	&2.901	&2.901	&2.901(0)	\\
-	\ce{BF}		&	$^1\Pi$ 		&6.478	&6.491	&6.491	&6.484	&6.485	&6.485	&6.485(1)	&6.410	&6.423	&6.416	&6.417	&6.418(2)\\
-	\ce{CO}		&	$^1\Pi$ 		&8.572	&8.591	&8.574	&8.562	&8.563	&8.561	&8.565(2)	&8.486	&8.492	&8.479	&8.480	&	\\
-				&	$^1\Sigma^-$ 	&10.122	&10.112	&10.062	&10.055	&10.057	&10.057	&10.056(1)	&9.992	&9.940	&9.930	&9.932	&	\\
-				&	$^1\Delta$ 		&10.225	&10.220	&10.178	&10.167	&10.169	&10.168	&10.168(1)	&10.119	&10.076	&10.064	&10.066	&	\\
-				&	$^1\Sigma^+$ 	&10.917	&10.989	&10.944	&10.925	&10.926	&10.919	&			&10.943	&10.987	&10.961	&10.963	&	\\
-				&	$^1\Sigma^+$ 	&11.483	&11.543	&11.518	&11.510	&11.510	&11.506	&			&11.489	&11.540	&11.521	&11.523	&	\\
-				&	$^1\Pi$ 		&11.737	&11.802	&11.767	&11.757	&11.758	&11.753	&			&11.690	&11.737	&11.719	&11.720	&	\\
-	\ce{N2}		&	$^1\Pi_g$  		&9.442	&9.450	&9.417	&9.409	&9.411	&9.409	&9.411(3)	&9.344	&9.326	&9.317	&9.319	&	\\
-				&	$^1\Sigma_u^-$	&10.059	&10.063	&10.060	&10.063	&10.055	&10.054	&10.054(0)	&9.885	&9.890	&9.883	&9.878	&	9.879(4)\\
-				&	$^1\Delta_u$ 	&10.433	&10.449	&10.436	&10.439	&10.430	&10.428	&10.429(0)	&10.293	&10.302	&10.294	&10.287	&	10.289(12)\\
-				&	$^1\Sigma_g^+$	&13.229	&13.270	&13.202	&13.171	&13.182	&13.181	&13.180(1)	&13.013	&12.999	&12.962	&12.974	&	\\
-				&	$^1\Pi_u$  		&13.279	&13.323	&13.174	&13.128	&13.131	&13.127	&			&13.223	&13.140	&13.091	&13,095	&	\\
-				&	$^1\Sigma_u^+$	&13.146	&13.186	&13.130	&13.099	&13.109	&13.107	&			&13.120	&13.118	&13.078	&13.090	&	\\
-				&	$^1\Pi_u$ 		&13.635	&13.663	&13.591	&13.551	&13.560	&13.558	&			&13.494	&13.455	&13.409	&13.419\\
-	\ce{HCl}	&	$^1\Pi$ 		&7.819	&7.828	&7.815	&7.822	&7.822	&7.823	&7.823(0)	&7.840	&7.834	&7.837	&7.837	&7.838(1)\\
-	\ce{H2S}	&	$^1B_1$  		&6.098	&6.110	&6.098	&6.102	&6.103	&6.103	&6.103(1)	&6.240	&6.237	&6.238	&6.238	&6.240(7)\\
-				&	$^1A_2$  		&6.293	&6.299	&6.286	&6.286	&6.286	&6.286	&6.286(0)	&6.192	&6.185	&6.181	&6.181	&6.181(6) \\
-	\ce{H2O}	&	$^1B_1$  		&7.511	&7.510	&7.497	&7.531	&7.528	&7.532	&7.533(0)	&7.605	&7.591	&7.623	&7.620	&7.626(3)\\
-				&	$^1A_2$  		&9.293	&9.291	&9.279	&9.317	&9.313	&9.318	&9.318(0)	&9.382	&9.368	&9.405	&9.400	&9.407(7)\\
-				&	$^1A_1$  		&9.921	&9.919	&9.903	&9.940	&9.937	&9.941	&9.941(0)	&9.966	&9.949	&9.986	&9.981	&9.986(2)\\
+	\ce{NH3}	&	$^1A_2$ 		&6.455	&6.464	&6.472	&6.462	&6.479	&6.480	&6.482	&6.483(1)	&6.600	&6.573	&6.571	&6.585	&6.586	&6.593(22)	\\	
+				&	$^1E$			&8.024	&8.061	&8.065	&8.057	&8.078	&8.079	&8.081	&8.082(1)	&8.148	&8.146	&8.143	&8.161	&8.161	&8.171(20)	\\	
+				&	$^1A_1$ 		&9.649	&9.664	&9.668	&9.659	&9.677	&9.677	&9.680	&9.681(8)	&9.334	&9.318	&9.314	&9.331	&9.331	&9.340(19)	\\
+				&	$^1A_2$ 		&10.376	&10.396	&10.402	&10.391	&10.409	&10.409	&10.411	&10.412(1)	&9.953	&9.945	&9.939	&9.957	&9.957	&9.967(19)	\\
+	\ce{BH}		&	$^1\Pi$ 		&2.970	&2.955	&2.958	&2.946	&2.947	&2.947	&2.947	&2.947(0)	&2.928	&2.910	&2.900	&2.901	&2.901	&2.901(0)	\\
+	\ce{BF}		&	$^1\Pi$ 		&6.534	&6.478	&6.491	&6.491	&6.484	&6.485	&6.485	&6.485(1)	&6.464	&6.410	&6.423	&6.416	&6.417	&6.418(2)\\
+	\ce{CO}		&	$^1\Pi$ 		&8.671	&8.572	&8.591	&8.574	&8.562	&8.563	&8.561	&8.565(2)	&8.587	&8.486	&8.492	&8.479	&8.480	&	\\
+				&	$^1\Sigma^-$ 	&10.096	&10.122	&10.112	&10.062	&10.055	&10.057	&10.057	&10.056(1)	&9.986	&9.992	&9.940	&9.930	&9.932	&	\\
+				&	$^1\Delta$ 		&10.210	&10.225	&10.220	&10.178	&10.167	&10.169	&10.168	&10.168(1)	&10.123	&10.119	&10.076	&10.064	&10.066	&	\\
+				&	$^1\Sigma^+$ 	&11.171	&10.917	&10.989	&10.944	&10.925	&10.926	&10.919	&			&11.222	&10.943	&10.987	&10.961	&10.963	&	\\
+				&	$^1\Sigma^+$ 	&11.710	&11.483	&11.543	&11.518	&11.510	&11.510	&11.506	&			&11.751	&11.489	&11.540	&11.521	&11.523	&	\\
+				&	$^1\Pi$ 		&11.973	&11.737	&11.802	&11.767	&11.757	&11.758	&11.753	&			&11.960	&11.690	&11.737	&11.719	&11.720	&	\\
+	\ce{N2}		&	$^1\Pi_g$  		&9.495	&9.442	&9.450	&9.417	&9.409	&9.411	&9.409	&9.411(3)	&9.408	&9.344	&9.326	&9.317	&9.319	&	\\
+				&	$^1\Sigma_u^-$	&10.197	&10.059	&10.063	&10.060	&10.063	&10.055	&10.054	&10.054(0)	&9.996	&9.885	&9.890	&9.883	&9.878	&9.879(4)\\
+				&	$^1\Delta_u$ 	&10.607	&10.433	&10.449	&10.436	&10.439	&10.430	&10.428	&10.429(0)	&10.443	&10.293	&10.302	&10.294	&10.287	&10.289(12)\\
+				&	$^1\Sigma_g^+$	&13.326	&13.229	&13.270	&13.202	&13.171	&13.182	&13.181	&13.180(1)	&13.151	&13.013	&12.999	&12.962	&12.974	&	\\
+				&	$^1\Pi_u$  		&13.451	&13.279	&13.323	&13.174	&13.128	&13.131	&13.127	&			&13.422	&13.223	&13.140	&13.091	&13,095	&	\\
+				&	$^1\Sigma_u^+$	&13.250	&13.146	&13.186	&13.130	&13.099	&13.109	&13.107	&			&13.263	&13.120	&13.118	&13.078	&13.090	&	\\
+				&	$^1\Pi_u$ 		&13.765	&13.635	&13.663	&13.591	&13.551	&13.560	&13.558	&			&13.674	&13.494	&13.455	&13.409	&13.419\\
+	\ce{HCl}	&	$^1\Pi$ 		&7.862	&7.819	&7.828	&7.815	&7.822	&7.822	&7.823	&7.823(0)	&7.906	&7.840	&7.834	&7.837	&7.837	&7.838(1)\\
+	\ce{H2S}	&	$^1B_1$  		&6.141	&6.098	&6.110	&6.098	&6.102	&6.103	&6.103	&6.103(1)	&6.294	&6.240	&6.237	&6.238	&6.238	&6.240(7)\\
+				&	$^1A_2$  		&6.343	&6.293	&6.299	&6.286	&6.286	&6.286	&6.286	&6.286(0)	&6.246	&6.192	&6.185	&6.181	&6.181	&6.181(6) \\
+	\ce{H2O}	&	$^1B_1$  		&7.447	&7.511	&7.510	&7.497	&7.531	&7.528	&7.532	&7.533(0)	&7.597	&7.605	&7.591	&7.623	&7.620	&7.626(3)\\
+				&	$^1A_2$  		&9.213	&9.293	&9.291	&9.279	&9.317	&9.313	&9.318	&9.318(0)	&9.361	&9.382	&9.368	&9.405	&9.400	&9.407(7)\\
+				&	$^1A_1$  		&9.861	&9.921	&9.919	&9.903	&9.940	&9.937	&9.941	&9.941(0)	&9.957	&9.966	&9.949	&9.986	&9.981	&9.986(2)\\
 	\hline

### 2021-05-02 Manuscript/CC4.tex
ok for intro for now

@@
 \documentclass[aip,jcp,reprint,noshowkeys,superscriptaddress]{revtex4-1}
-\usepackage{graphicx,dcolumn,bm,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,wrapfig,txfonts,siunitx}
+\usepackage{graphicx,dcolumn,bm,xcolor,microtype,multirow,amscd,amsmath,amssymb,amsfonts,physics,wrapfig,txfonts}
 \usepackage[version=4]{mhchem}
+
+\usepackage{siunitx}
+\DeclareSIUnit[number-unit-product = {\,}]
+\cal{cal}
+\DeclareSIUnit\kcal{\kilo\cal}
 
@@
 
-Taking advantage of the high accuracy of CC and SCI+PT2 methods, we have very recently created a large dataset of more than 500 highly-accurate vertical excitation energies of various natures in small- and medium-sized molecules, many of which can be reasonably considered as chemically accurate (\ie, within $1$ kcal.mol$^{-1}$ of the FCI limit).
+Taking advantage of the high accuracy of CC and SCI+PT2 methods, we have very recently created a large dataset gathering more than 500 highly-accurate vertical excitation energies of various natures (valence, Rydberg, $\npis$, $\pipis$, singlet, doublet, triplet, charge-transfer, and double excitations) in small- and medium-sized molecules ranging from diatomics to molecules as large as naphthalene.
+The main purpose of this so-called QUEST database is to provide reference excitation energies in order to perform fair and reliable comparisons between electronic structure methods and assess their strengths and weakness in a large panel of chemical scenarios.
+Most of these reference transition energies, which rely exclusively on high-level \textit{ab initio} calculations, can be reasonably considered as chemically accurate, \ie, within \SI{1}{\kcal\per\mol} or \SI{0.043}{\eV} of the FCI limit.
+However, their accuracy may rapidly deteriorate, in particular, as the system size grows.
+Indeed, it is usually challenging to compute reliable SCI+PT2 estimates or CCSDTQ excitation energies for molecules with more than 4 non-hydrogen atoms.
+Therefore, for the larger molecules of the QUEST database, we mostly relied on CCSDT to define reference excitation energies.
+Of course, it would be highly valuable to have access to more accurate methods (including, at least, quadruple excitations) in order to refine, in the near future, these theoretical best estimates.
 
-The main purpose of the present study is to assess the relative accuracy of the approximate CC4 model against the most expensive CCSDTQ and CCSDTQP methods in the case of vertical excitation energies.
+In this context, the main purpose of the present study is to assess the relative accuracy of the approximate CC4 model against the most expensive CCSDTQ and CCSDTQP methods in the case of vertical excitation energies.
 We are also interested in its absolute accuracy with respect to FCI.
 To do so, we consider a set of 8 small molecules (\ce{NH3}, \ce{BH}, \ce{BF}, \ce{CO}, \ce{N2}, \ce{HCl}, \ce{H2S}, and \ce{H2O}) and we compare the excitation energies associated with 25 singlet excited states of various natures ($\npis$, $\pipis$, Rydberg, valence, charge-transfer, \ldots) and spatial symmetries obtained with various high-level CC methods.
-Although several studies have been published on the performance of CC4 for ground-state energies and properties, to the best of our knowledge, CC4 has never been used to compute excited-states energies before.
-As we shall see below, CC4 is an excellent approximation to its CCSDTQ parent, and produces excitation energies with sub-kJ/mol accuracy, well below the chemical accuracy threshold.
+Although several studies have been published on the performance of CC4 for ground-state energies and properties, to the best of our knowledge, CC4 has never been considered to compute excited-states energies before.
+As we shall see below, CC4 is an excellent approximation to its CCSDTQ parent, and produces excitation energies with sub-\si{\kJ\per\mol} accuracy for this set of small molecules, well below the chemical accuracy threshold.
 
@@
 
-Each method used in the present study is reported in Table \ref{tab:scaling} alongside its formal computational scaling and the electronic structure software used to compute the excitation energies.
+All the methods considered in the present study are listed in Table \ref{tab:scaling} alongside their formal computational scaling and the electronic structure software employed to compute the excitation energies.
 In a nutshell, we have used by default the {\CFOUR} program to compute the CC energies at the notable exception of CCSDTQP where we have employed {\MRCC} and its automated implementation of high-order CC methods based on the strings of spin-orbital indices.
-The FCI estimates were obtained with the CIPSI algorithm implemented in {\QP}.
-The present {\CFOUR} calculations have been performed with the new and very fast CC module (\texttt{xncc}) written by one of author (DAM) which couples a general algebraic
+The FCI estimates were obtained with the SCI algorithm known as \textit{``configuration interaction using a perturbative selection made iteratively''} (CIPSI) implemented in {\QP}.
+The error bars associated with these CIPSI calculations have been computed using our recently-developed protocol presented in Ref.~\onlinecite{Veril_2021}.
+The present {\CFOUR} calculations have been performed with the new and fast CC module (\texttt{xncc}) written by one of author (DAM) which couples a general algebraic
 and graphical interpretation of the non-orthogonal spin-adaptation approach with highly efficient storage format and set of implementation techniques designed to minimize data movement and to avoid costly tensor transposes.
 
-\titou{The error bars at the CIPSI level have been computed using our recently-developed protocol presented in Ref.~\onlinecite{Veril_2021}.
-Two basis sets are used (aug-cc-pVDZ and aug-cc-pVTZ). 
+All calculations have been performed in the frozen-core calculations and the geometries of the system considered here have been extracted from previous studies at the exception of \ce{BH} and \ce{BF}.
+\titou{Two basis sets are used (aug-cc-pVDZ and aug-cc-pVTZ). 
 For the small ones, we could compute CCSDTQP energies but not in the larger one.}

### 2021-05-02 Manuscript/CC4.tex
ok for now with comp det

@@
 By iteratively increasing the number of determinants of the variational space and supplemented it with a second-order perturbative correction (PT2), the SCI+PT2 family of methods has been recently shown to produce near-FCI correlation and excitation energies for small- and medium-size molecules in compact basis sets.
+Although the formal scaling of such algorithms remain exponential, the prefactor is greatly reduced which explains their current attractiveness in the electronic structure community and much wider applicability than their common FCI parent.
 
-Taking advantage of the high accuracy of CC and SCI+PT2 methods, we have very recently created a large dataset gathering more than 500 highly-accurate vertical excitation energies of various natures (valence, Rydberg, $\npis$, $\pipis$, singlet, doublet, triplet, charge-transfer, and double excitations) in small- and medium-sized molecules ranging from diatomics to molecules as large as naphthalene.
+Taking advantage of the high accuracy of CC and SCI+PT2 methods, we have very recently created a large dataset gathering more than 500 highly-accurate vertical excitation energies for electronic transitions of various natures (valence, Rydberg, $\npis$, $\pipis$, singlet, doublet, triplet, charge-transfer, and double excitations) in small- and medium-sized molecules ranging from diatomics to molecules as large as naphthalene.
 The main purpose of this so-called QUEST database is to provide reference excitation energies in order to perform fair and reliable comparisons between electronic structure methods and assess their strengths and weakness in a large panel of chemical scenarios.
@@
 However, their accuracy may rapidly deteriorate, in particular, as the system size grows.
-Indeed, it is usually challenging to compute reliable SCI+PT2 estimates or CCSDTQ excitation energies for molecules with more than 4 non-hydrogen atoms.
+Indeed, it is usually challenging to compute reliable SCI+PT2 estimates or CCSDTQ excitation energies for molecules with more than four non-hydrogen atoms.
 Therefore, for the larger molecules of the QUEST database, we mostly relied on CCSDT to define reference excitation energies.
@@
 
-In this context, the main purpose of the present study is to assess the relative accuracy of the approximate CC4 model against the most expensive CCSDTQ and CCSDTQP methods in the case of vertical excitation energies.
-We are also interested in its absolute accuracy with respect to FCI.
+In this context, the main purpose of the present study is to assess the relative accuracy of the approximate CC4 model against the most expensive CCSDTQ and CCSDTQP methods in the case of vertical excitation energies, as well as its absolute accuracy with respect to FCI.
 To do so, we consider a set of 8 small molecules (\ce{NH3}, \ce{BH}, \ce{BF}, \ce{CO}, \ce{N2}, \ce{HCl}, \ce{H2S}, and \ce{H2O}) and we compare the excitation energies associated with 25 singlet excited states of various natures ($\npis$, $\pipis$, Rydberg, valence, charge-transfer, \ldots) and spatial symmetries obtained with various high-level CC methods.
@@
 
-All the methods considered in the present study are listed in Table \ref{tab:scaling} alongside their formal computational scaling and the electronic structure software employed to compute the excitation energies.
-In a nutshell, we have used by default the {\CFOUR} program to compute the CC energies at the notable exception of CCSDTQP where we have employed {\MRCC} and its automated implementation of high-order CC methods based on the strings of spin-orbital indices.
-The FCI estimates were obtained with the SCI algorithm known as \textit{``configuration interaction using a perturbative selection made iteratively''} (CIPSI) implemented in {\QP}.
-The error bars associated with these CIPSI calculations have been computed using our recently-developed protocol presented in Ref.~\onlinecite{Veril_2021}.
-The present {\CFOUR} calculations have been performed with the new and fast CC module (\texttt{xncc}) written by one of author (DAM) which couples a general algebraic
-and graphical interpretation of the non-orthogonal spin-adaptation approach with highly efficient storage format and set of implementation techniques designed to minimize data movement and to avoid costly tensor transposes.
-
-All calculations have been performed in the frozen-core calculations and the geometries of the system considered here have been extracted from previous studies at the exception of \ce{BH} and \ce{BF}.
-\titou{Two basis sets are used (aug-cc-pVDZ and aug-cc-pVTZ). 
-For the small ones, we could compute CCSDTQP energies but not in the larger one.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results and discussion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%%% TABLE I %%%
 \begin{table}
-	\caption{Methods considered, their formal computational scaling and the name of the electronic structure software where it has been implemented.
+	\caption{Methods considered in the present study, their formal computational scaling and the electronic structure software employed to compute excitation energies.
 	Here, $N$ is the number of orbitals.
@@
 		\hline
-		CC3			&	$\order*{N^{7}}$	&	\DALTON		&	\onlinecite{dalton}		\\
+		CC3			&	$\order*{N^{7}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
 		CCSDT-3		&	$\order*{N^{7}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
@@
 \end{table}
+%%% %%% %%% %%%
 
+All the methods considered in the present study are listed in Table \ref{tab:scaling} alongside their formal computational scaling and the electronic structure software employed to compute the excitation energies.
+In a nutshell, we have used by default {\CFOUR} to compute the CC energies at the notable exception of CCSDTQP for which we have employed {\MRCC} and its automated implementation of high-order CC methods.
+The present {\CFOUR} calculations have been performed with the new and fast CC module (\texttt{xncc}) written by one of author (DAM) which couples a general algebraic
+and graphical interpretation of the non-orthogonal spin-adaptation approach with highly efficient storage format and implementation techniques designed to minimize data movement and to avoid costly tensor transposes.
+The FCI estimates were obtained with the SCI algorithm known as \textit{``configuration interaction using a perturbative selection made iteratively''} (CIPSI) implemented in {\QP}.
+The error bars associated with these CIPSI calculations have been computed using our recently-developed protocol presented in Ref.~\onlinecite{Veril_2021}.
+
+All calculations have been performed in the frozen-core approximation and the CC3/aug-cc-pVTZ geometries of the system considered here have been extracted from previous studies at the exception of \ce{BH} and \ce{BF}.
+In the following, we consider diffuse-containing Dunning's double- and triple-$\zeta$ basis sets (aug-cc-pVDZ and aug-cc-pVTZ).
+Note that CCSDTQP energies could only be computed for the smaller basis (aug-cc-pVDZ).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results and discussion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%% TABLE II %%%
 \begin{squeezetable}
@@
 \end{squeezetable}
+%%% %%% %%% %%%
+
+Table \ref{tab:BigTab} gathers vertical excitation energies obtained with various CC models as well as FCI estimates.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{References}
 \bibliography{CC4}

### 2021-05-02 Manuscript/CC4.tex
adding references

@@
 
-Single-reference coupled-cluster (CC) theory provides a hierarchy of size-extensive methods which delivers increasingly accurate energies and properties via the systematic increase of the maximum excitation degree of the cluster operator $\hT = \hT_1 + \hT_2 + \ldots + \hT_k$ (where $k \ge n$ and $n$ is the number of electrons).
+Single-reference coupled-cluster (CC) theory cprovides a hierarchy of size-extensive methods which delivers increasingly accurate energies and properties via the systematic increase of the maximum excitation degree of the cluster operator $\hT = \hT_1 + \hT_2 + \ldots + \hT_k$ (where $k \ge n$ and $n$ is the number of electrons).
+\cite{Cizek_1966,Paldus_1972,Crawford_2000,Bartlett_2007,Shavitt_2009}
 Without any truncation (\ie, $k = n$), the so-called full CC (FCC) method is equivalent to full configuration interaction (FCI), hence providing the exact energy and wave function of the system within a given basis set.
 However, it is not computationally viable due to its exponential scaling with system size, and one has to resort to truncated CC methods  (\ie, $k \ll n$) for computational convenience.
-Popular choices are CC with singles and doubles (CCSD), CC with singles, doubles, and triples (CCSDT), CC with singles, doubles, triples, and quadruples (CCSDTQ), and 
-CC with singles, doubles, triples, quadruples, and pentuples (CCSDTQP) with corresponding computational scalings of $\order*{N^{6}}$, $\order*{N^{8}}$,  $\order*{N^{10}}$, and  $\order*{N^{12}}$, respectively (where $N$ denotes the number of orbitals).
-An alternative, systematically-improvable family of methods is defined by the CC2, CC3, and CC4 series of models which have been introduced by the Aarhus group in the context of CC response theory.
+Popular choices are CC with singles and doubles (CCSD), \cite{Cizek_1966,Purvis_1982} CC with singles, doubles, and triples (CCSDT), \cite{Noga_1987a,Scuseria_1988} CC with singles, doubles, triples, and quadruples (CCSDTQ), \cite{Oliphant_1991,Kucharski_1992} and
+CC with singles, doubles, triples, quadruples, and pentuples (CCSDTQP) \cite{Hirata_2000,Kallay_2001} with corresponding computational scalings of $\order*{N^{6}}$, $\order*{N^{8}}$,  $\order*{N^{10}}$, and  $\order*{N^{12}}$, respectively (where $N$ denotes the number of orbitals).
+An alternative, systematically-improvable family of methods is defined by the CC2, \cite{Christiansen_1995a} CC3, \cite{Christiansen_1995b,Koch_1997} and CC4 \cite{Kallay_2005} series of models which have been introduced by the Aarhus group in the context of CC response theory.
+\cite{Christiansen_1998}
 These methods scale as $\order*{N^{5}}$, $\order*{N^{7}}$, and $\order*{N^{9}}$, respectively, and can be seen as cheaper approximations of CCSD, CCSDT, and CCSDTQ, by skipping the most expensive terms and avoiding the storage of the higher-excitation amplitudes.
-A somehow similar strategy has been applied to produce the CCSDT-3 and CCSDTQ-3 models based on arguments stemming from perturbation theory.
-Of course, many more approximate CC models have been developed and we refer the interested reader to specialized reviews for more details.
+A somehow similar strategy has been applied to produce the CCSDT-3 \cite{Urban_1985,Noga_1987b} and CCSDTQ-3 \cite{Kallay_2005} models based on arguments stemming from perturbation theory.
+Of course, many more approximate CC models have been developed and we refer the interested reader to specialized reviews for more details. \cite{Crawford_2000,Bartlett_2007,Shavitt_2009}
 
@@
 	\caption{Vertical excitation energies (in eV) of a selection of molecular excited states obtained at various levels of theory with the aug-cc-pVDZ and aug-cc-pVTZ basis sets. 
+	For the aug-cc-pVDZ basis, the mean absolute error (MAE) and mean signed error (MSE) with respect to CCSDTQP is reported.
 	\label{tab:BigTab}}
@@
 	\hline
-	MAE			&					&	\\
+	MAE			&					&0.112	&0.041	&0.028	&0.018	&0.003	&0.002	\\
+	MSE			&					&0.079	&0.032	&0.014	&0.002	&0.000	&0.000	\\
 	\end{tabular}
@@
 Table \ref{tab:BigTab} gathers vertical excitation energies obtained with various CC models as well as FCI estimates.
+
+%%% FIG 1 %%%
+\begin{figure}
+	\includegraphics[width=\linewidth]{histograms_MAE_AVDZ}
+	\caption{
+	Distribution of the error (in eV) in excitation energies (with respect to the CCSDTQP values) for various methods obtained with the aug-cc-pVDZ basis.
+	See Table \ref{tab:BigTab} for the raw data.
+	\label{fig:MAE}}
+\end{figure}
 

### 2021-05-03 Manuscript/CC4.tex
refs done

@@
 A somehow similar strategy has been applied to produce the CCSDT-3 \cite{Urban_1985,Noga_1987b} and CCSDTQ-3 \cite{Kallay_2005} models based on arguments stemming from perturbation theory.
-Of course, many more approximate CC models have been developed and we refer the interested reader to specialized reviews for more details. \cite{Crawford_2000,Bartlett_2007,Shavitt_2009}
+Of course, many more approximate CC models have been developed and we refer the interested reader to specialized reviews for more details. \cite{Crawford_2000,Piecuch_2002,Bartlett_2007,Shavitt_2009}
 
-Coupled-cluster methods have been particularly successful for small- and medium-sized molecules in the field of thermodynamics, kinetics, and spectroscopy, thanks to the computations of accurate geometries, potential energy surfaces, couplings between electronic states, and a vast panel of properties such as dipoles (and higher moments), vibrational frequencies, NMR chemical shifts, magnetizabilities, polarizabilities, etc.
-Although originally developed for ground-state energies and properties, CC has been successfully extended to excited states thanks to the equation-of-motion (EOM) and linear-response (LR) formalisms which are known to produce identical excitation energies but different properties.
+Coupled-cluster methods have been particularly successful for small- and medium-sized molecules in the field of thermodynamics, kinetics, and spectroscopy, thanks to the computations of accurate equilibrium geometries, \cite{Kallay_2003} potential energy surfaces, vibrational frequencies, \cite{Kallay_2004a} Born-Oppenheimer correction, \cite{Gauss_2006} and a vast panel of properties such as dipoles (and higher moments), \cite{Kallay_2003}  NMR chemical shifts, \cite{Kallay_2004a} magnetizabilities, \cite{Gauss_2009} polarizabilities, \cite{Kallay_2006} etc.
+Although originally developed for ground-state energies and properties, CC has been successfully extended to excited states \cite{Monkhorst_1977} thanks to the equation-of-motion (EOM) \cite{Emrich_1981,Comeau_1993,Stanton_1993,Krylov_2008} and linear-response (LR) \cite{Ghosh_1981,Sekino_1984,Koch_1990a,Koch_1990b,Rico_1993} formalisms which are known to produce identical excitation energies but different properties.
 In EOM-CC, one determines vertical excitation energies via the diagonalization of the similarity-transformed Hamiltonian $\bH = e^{-\hT} \hH e^{\hT}$.
 A more general procedure to compute excitation energies that can be applied to any approximate CC model (as the ones mentioned above) consists in diagonalizing the so-called CC Jacobian obtained via the differentiation of the CC amplitude equations.
-Again, by systematically increasing the maximum excitation degree of $\hT$, one can systematically produce increasingly accurate excitation energies with the ``complete'' series CCSD, CCSDT, CCSDTQ, CCSDTP, \ldots or the ``approximate'' series CC2, CC3, CC4, \ldots while retaining the formal scaling of their ground-state analog.
+Again, by systematically increasing the maximum excitation degree of $\hT$, one can systematically produce increasingly accurate excitation energies with the ``complete'' series CCSD, \cite{Stanton_1993} CCSDT, \cite{Kowalski_2001,Kucharski_2001} CCSDTQ, \cite{Hirata_2004} CCSDTQP, \cite{Kallay_2004b} \ldots~or the ``approximate'' series CC2, \cite{Christiansen_1995a} CC3, \cite{Christiansen_1995b} CC4, \cite{Kallay_2004b} \ldots~while retaining the formal scaling of their ground-state analog.
 
-Recently, a large collection of deterministic, stochastic or hybrid selected CI (SCI) methods has (re)appeared in the electronic structure landscape providing an alternative route to highly-accurate ground- and excited-state energies.
+Recently, a large collection of deterministic, stochastic or hybrid selected CI (SCI) methods \cite{Bender_1969,Whitten_1969,Huron_1973} has (re)appeared \cite{Booth_2009,Deustua_2017,Holmes_2016,Eriksen_2017,Xu_2018,Giner_2013,Giner_2015,Evangelista_2014,Tubman_2016,Liu_2016,Ohtsuka_2017,Zimmerman_2017,Coe_2018,Garniron_2018} in the electronic structure landscape providing an alternative route to highly-accurate ground- and excited-state energies \cite{Holmes_2017,Li_2018,Li_2020,Loos_2018a,Chien_2018,Loos_2019,Loos_2020b,Loos_2020c,Loos_2020e,qp2,Eriksen_2020,Yao_2020,Veril_2021} (see Refs.~\onlinecite{Loos_2020a,Eriksen_2021} for recent reviews).
 The general idea behind SCI methods is simple: rather than exploring the entire FCI space by systematically increasing the maximum excitation degree of the determinants taken into account (leading to the slowly convergent and size-inconsistent series of methods CISD, CISDT, CISDTQ, \ldots), one performs a sparse exploration of the FCI space by selecting only the most energetically-important determinants thanks to a suitable criterion usually based on perturbation theory.
-By iteratively increasing the number of determinants of the variational space and supplemented it with a second-order perturbative correction (PT2), the SCI+PT2 family of methods has been recently shown to produce near-FCI correlation and excitation energies for small- and medium-size molecules in compact basis sets.
+\cite{Huron_1973,Garniron_2017,Sharma_2017,qp2}
+By iteratively increasing the number of determinants of the variational space and supplemented it with a second-order perturbative correction (PT2), the SCI+PT2 family of methods has been recently shown to produce near-FCI correlation and excitation energies for small- and medium-size molecules in compact basis sets.\cite{Holmes_2017,Loos_2018a,Chien_2018,Loos_2019,Loos_2020b,Loos_2020c,qp2,Veril_2021}
 Although the formal scaling of such algorithms remain exponential, the prefactor is greatly reduced which explains their current attractiveness in the electronic structure community and much wider applicability than their common FCI parent.
@@
 Taking advantage of the high accuracy of CC and SCI+PT2 methods, we have very recently created a large dataset gathering more than 500 highly-accurate vertical excitation energies for electronic transitions of various natures (valence, Rydberg, $\npis$, $\pipis$, singlet, doublet, triplet, charge-transfer, and double excitations) in small- and medium-sized molecules ranging from diatomics to molecules as large as naphthalene.
+\cite{Loos_2018a,Loos_2019,Loos_2020a,Loos_2020b,Loos_2020c,Veril_2021}
 The main purpose of this so-called QUEST database is to provide reference excitation energies in order to perform fair and reliable comparisons between electronic structure methods and assess their strengths and weakness in a large panel of chemical scenarios.
@@
 To do so, we consider a set of 8 small molecules (\ce{NH3}, \ce{BH}, \ce{BF}, \ce{CO}, \ce{N2}, \ce{HCl}, \ce{H2S}, and \ce{H2O}) and we compare the excitation energies associated with 25 singlet excited states of various natures ($\npis$, $\pipis$, Rydberg, valence, charge-transfer, \ldots) and spatial symmetries obtained with various high-level CC methods.
-Although several studies have been published on the performance of CC4 for ground-state energies and properties, to the best of our knowledge, CC4 has never been considered to compute excited-states energies before.
+Although several studies have been published on the performance of CC4 for ground-state energies and properties, \cite{Kallay_2005,Matthews_2015a,Matthews_2021} to the best of our knowledge, CC4 has never been considered to compute excited-states energies before.
 As we shall see below, CC4 is an excellent approximation to its CCSDTQ parent, and produces excitation energies with sub-\si{\kJ\per\mol} accuracy for this set of small molecules, well below the chemical accuracy threshold.
@@
 		\hline
+		CC2			&	$\order*{N^{5}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
+		CCSD		&	$\order*{N^{6}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
 		CC3			&	$\order*{N^{7}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
-		CCSDT-3		&	$\order*{N^{7}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
+%		CCSDT-3		&	$\order*{N^{7}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
 		CCSDT		&	$\order*{N^{8}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
 		CC4			&	$\order*{N^{9}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
-		CCSDTQ-3	&	$\order*{N^{9}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
+%		CCSDTQ-3	&	$\order*{N^{9}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
 		CCSDTQ		&	$\order*{N^{10}}$	&	\CFOUR		&	\onlinecite{cfour}		\\
@@
 All the methods considered in the present study are listed in Table \ref{tab:scaling} alongside their formal computational scaling and the electronic structure software employed to compute the excitation energies.
-In a nutshell, we have used by default {\CFOUR} to compute the CC energies at the notable exception of CCSDTQP for which we have employed {\MRCC} and its automated implementation of high-order CC methods.
+In a nutshell, we have used by default {\CFOUR} \cite{cfour} to compute the CC energies at the notable exception of CCSDTQP for which we have employed {\MRCC} and its automated implementation of high-order CC methods.
+\cite{mrcc}
 The present {\CFOUR} calculations have been performed with the new and fast CC module (\texttt{xncc})  written by one of author (DAM) which couples a general algebraic
 and graphical interpretation of the non-orthogonal spin-adaptation approach with highly efficient storage format and implementation techniques designed to minimize data movement and to avoid costly tensor transposes.
-The FCI estimates were obtained with the SCI algorithm known as \textit{``configuration interaction using a perturbative selection made iteratively''} (CIPSI) implemented in {\QP}.
+\cite{Matthews_2015b}
+The FCI estimates were obtained with the SCI algorithm known as \textit{``configuration interaction using a perturbative selection made iteratively''} (CIPSI) implemented in {\QP}. \cite{qp2}
 The error bars associated with these CIPSI calculations have been computed using our recently-developed protocol presented in Ref.~\onlinecite{Veril_2021}.
@@
 All calculations have been performed in the frozen-core approximation and the CC3/aug-cc-pVTZ geometries of the system considered here have been extracted from previous studies at the exception of \ce{BH} and \ce{BF}.
+\cite{Loos_2018a}
 In the following, we consider diffuse-containing Dunning's double- and triple-$\zeta$ basis sets (aug-cc-pVDZ and aug-cc-pVTZ).

### 2021-05-03 Manuscript/CC4.tex
CC2 data

@@
 	\begin{ruledtabular}
-	\begin{tabular}{llrrrrrrrrrrrrrr}
-				&		&	\mc{8}{c}{aug-cc-pVDZ}		&		\mc{6}{c}{aug-cc-pVTZ}		\\	
-				\cline{3-10} \cline{11-16}
-	Mol.	&	State				&CCSD	&CC3	&CCSDT-3&CCSDT	&CC4	&CCSDTQ	&CCSDTQP	&FCI	
-									&CCSD	&CC3	&CCSDT	&CC4	&CCSDTQ	&FCI			\\
+	\begin{tabular}{llrrrrrrrrrrrrrrr}
+				&		&	\mc{8}{c}{aug-cc-pVDZ}		&		\mc{7}{c}{aug-cc-pVTZ}		\\	
+				\cline{3-10} \cline{11-17}
+	Mol.	&	State				&CC2	&CCSD	&CC3	&CCSDT	&CC4	&CCSDTQ	&CCSDTQP	&FCI	
+									&CC2	&CCSD	&CC3	&CCSDT	&CC4	&CCSDTQ	&FCI			\\
 	\hline
-	\ce{NH3}	&	$^1A_2$ 		&6.455	&6.464	&6.472	&6.462	&6.479	&6.480	&6.482	&6.483(1)	&6.600	&6.573	&6.571	&6.585	&6.586	&6.593(22)	\\	
-				&	$^1E$			&8.024	&8.061	&8.065	&8.057	&8.078	&8.079	&8.081	&8.082(1)	&8.148	&8.146	&8.143	&8.161	&8.161	&8.171(20)	\\	
-				&	$^1A_1$ 		&9.649	&9.664	&9.668	&9.659	&9.677	&9.677	&9.680	&9.681(8)	&9.334	&9.318	&9.314	&9.331	&9.331	&9.340(19)	\\
-				&	$^1A_2$ 		&10.376	&10.396	&10.402	&10.391	&10.409	&10.409	&10.411	&10.412(1)	&9.953	&9.945	&9.939	&9.957	&9.957	&9.967(19)	\\
-	\ce{BH}		&	$^1\Pi$ 		&2.970	&2.955	&2.958	&2.946	&2.947	&2.947	&2.947	&2.947(0)	&2.928	&2.910	&2.900	&2.901	&2.901	&2.901(0)	\\
-	\ce{BF}		&	$^1\Pi$ 		&6.534	&6.478	&6.491	&6.491	&6.484	&6.485	&6.485	&6.485(1)	&6.464	&6.410	&6.423	&6.416	&6.417	&6.418(2)\\
-	\ce{CO}		&	$^1\Pi$ 		&8.671	&8.572	&8.591	&8.574	&8.562	&8.563	&8.561	&8.565(2)	&8.587	&8.486	&8.492	&8.479	&8.480	&	\\
-				&	$^1\Sigma^-$ 	&10.096	&10.122	&10.112	&10.062	&10.055	&10.057	&10.057	&10.056(1)	&9.986	&9.992	&9.940	&9.930	&9.932	&	\\
-				&	$^1\Delta$ 		&10.210	&10.225	&10.220	&10.178	&10.167	&10.169	&10.168	&10.168(1)	&10.123	&10.119	&10.076	&10.064	&10.066	&	\\
-				&	$^1\Sigma^+$ 	&11.171	&10.917	&10.989	&10.944	&10.925	&10.926	&10.919	&			&11.222	&10.943	&10.987	&10.961	&10.963	&	\\
-				&	$^1\Sigma^+$ 	&11.710	&11.483	&11.543	&11.518	&11.510	&11.510	&11.506	&			&11.751	&11.489	&11.540	&11.521	&11.523	&	\\
-				&	$^1\Pi$ 		&11.973	&11.737	&11.802	&11.767	&11.757	&11.758	&11.753	&			&11.960	&11.690	&11.737	&11.719	&11.720	&	\\
-	\ce{N2}		&	$^1\Pi_g$  		&9.495	&9.442	&9.450	&9.417	&9.409	&9.411	&9.409	&9.411(3)	&9.408	&9.344	&9.326	&9.317	&9.319	&	\\
-				&	$^1\Sigma_u^-$	&10.197	&10.059	&10.063	&10.060	&10.063	&10.055	&10.054	&10.054(0)	&9.996	&9.885	&9.890	&9.883	&9.878	&9.879(4)\\
-				&	$^1\Delta_u$ 	&10.607	&10.433	&10.449	&10.436	&10.439	&10.430	&10.428	&10.429(0)	&10.443	&10.293	&10.302	&10.294	&10.287	&10.289(12)\\
-				&	$^1\Sigma_g^+$	&13.326	&13.229	&13.270	&13.202	&13.171	&13.182	&13.181	&13.180(1)	&13.151	&13.013	&12.999	&12.962	&12.974	&	\\
-				&	$^1\Pi_u$  		&13.451	&13.279	&13.323	&13.174	&13.128	&13.131	&13.127	&			&13.422	&13.223	&13.140	&13.091	&13,095	&	\\
-				&	$^1\Sigma_u^+$	&13.250	&13.146	&13.186	&13.130	&13.099	&13.109	&13.107	&			&13.263	&13.120	&13.118	&13.078	&13.090	&	\\
-				&	$^1\Pi_u$ 		&13.765	&13.635	&13.663	&13.591	&13.551	&13.560	&13.558	&			&13.674	&13.494	&13.455	&13.409	&13.419\\
-	\ce{HCl}	&	$^1\Pi$ 		&7.862	&7.819	&7.828	&7.815	&7.822	&7.822	&7.823	&7.823(0)	&7.906	&7.840	&7.834	&7.837	&7.837	&7.838(1)\\
-	\ce{H2S}	&	$^1B_1$  		&6.141	&6.098	&6.110	&6.098	&6.102	&6.103	&6.103	&6.103(1)	&6.294	&6.240	&6.237	&6.238	&6.238	&6.240(7)\\
-				&	$^1A_2$  		&6.343	&6.293	&6.299	&6.286	&6.286	&6.286	&6.286	&6.286(0)	&6.246	&6.192	&6.185	&6.181	&6.181	&6.181(6) \\
-	\ce{H2O}	&	$^1B_1$  		&7.447	&7.511	&7.510	&7.497	&7.531	&7.528	&7.532	&7.533(0)	&7.597	&7.605	&7.591	&7.623	&7.620	&7.626(3)\\
-				&	$^1A_2$  		&9.213	&9.293	&9.291	&9.279	&9.317	&9.313	&9.318	&9.318(0)	&9.361	&9.382	&9.368	&9.405	&9.400	&9.407(7)\\
-				&	$^1A_1$  		&9.861	&9.921	&9.919	&9.903	&9.940	&9.937	&9.941	&9.941(0)	&9.957	&9.966	&9.949	&9.986	&9.981	&9.986(2)\\
+	\ce{NH3}	&	$^1A_2$ 		&6.249	&6.455	&6.464	&6.462	&6.479	&6.480	&6.482	&6.483(1)	&6.387	&6.600	&6.573	&6.571	&6.585	&6.586	&6.593(22)	\\	
+				&	$^1E$			&7.733	&8.024	&8.061	&8.057	&8.078	&8.079	&8.081	&8.082(1)	&7.847	&8.148	&8.146	&8.143	&8.161	&8.161	&8.171(20)	\\	
+				&	$^1A_1$ 		&9.400	&9.649	&9.664	&9.659	&9.677	&9.677	&9.680	&9.681(8)	&9.051	&9.334	&9.318	&9.314	&9.331	&9.331	&9.340(19)	\\
+				&	$^1A_2$ 		&10.148	&10.376	&10.396	&10.391	&10.409	&10.409	&10.411	&10.412(1)	&9.654	&9.953	&9.945	&9.939	&9.957	&9.957	&9.967(19)	\\
+	\ce{BH}		&	$^1\Pi$ 		&2.862	&2.970	&2.955	&2.946	&2.947	&2.947	&2.947	&2.947(0)	&2.831	&2.928	&2.910	&2.900	&2.901	&2.901	&2.901(0)	\\
+	\ce{BF}		&	$^1\Pi$ 		&6.509	&6.534	&6.478	&6.491	&6.484	&6.485	&6.485	&6.485(1)	&6.445	&6.464	&6.410	&6.423	&6.416	&6.417	&6.418(2)\\
+	\ce{CO}		&	$^1\Pi$ 		&8.724	&8.671	&8.572	&8.574	&8.562	&8.563	&8.561	&8.565(2)	&8.638	&8.587	&8.486	&8.492	&8.479	&8.480	&	\\
+				&	$^1\Sigma^-$ 	&10.381	&10.096	&10.122	&10.062	&10.055	&10.057	&10.057	&10.056(1)	&10.297	&9.986	&9.992	&9.940	&9.930	&9.932	&	\\
+				&	$^1\Delta$ 		&10.685	&10.210	&10.225	&10.178	&10.167	&10.169	&10.168	&10.168(1)	&10.604	&10.123	&10.119	&10.076	&10.064	&10.066	&	\\
+				&	$^1\Sigma^+$ 	&11.089	&11.171	&10.917	&10.944	&10.925	&10.926	&10.919	&			&11.106	&11.222	&10.943	&10.987	&10.961	&10.963	&	\\
+				&	$^1\Sigma^+$ 	&11.628	&11.710	&11.483	&11.518	&11.510	&11.510	&11.506	&			&11.626	&11.751	&11.489	&11.540	&11.521	&11.523	&	\\
+				&	$^1\Pi$ 		&11.878	&11.973	&11.737	&11.767	&11.757	&11.758	&11.753	&			&11.825	&11.960	&11.690	&11.737	&11.719	&11.720	&	\\
+	\ce{N2}		&	$^1\Pi_g$  		&9,528	&9.495	&9.442	&9.417	&9.409	&9.411	&9.409	&9.411(3)	&9.439	&9.408	&9.344	&9.326	&9.317	&9.319	&	\\
+				&	$^1\Sigma_u^-$	&10.428	&10.197	&10.059	&10.060	&10.063	&10.055	&10.054	&10.054(0)	&10.320	&9.996	&9.885	&9.890	&9.883	&9.878	&9.879(4)\\
+				&	$^1\Delta_u$ 	&10.961	&10.607	&10.433	&10.436	&10.439	&10.430	&10.428	&10.429(0)	&10.863	&10.443	&10.293	&10.302	&10.294	&10.287	&10.289(12)\\
+				&	$^1\Sigma_g^+$	&13.077	&13.326	&13.229	&13.202	&13.171	&13.182	&13.181	&13.180(1)	&12.833	&13.151	&13.013	&12.999	&12.962	&12.974	&	\\
+				&	$^1\Pi_u$  		&13.309	&13.451	&13.279	&13.174	&13.128	&13.131	&13.127	&			&13.152	&13.422	&13.223	&13.140	&13.091	&13,095	&	\\
+				&	$^1\Sigma_u^+$	&12.937	&13.250	&13.146	&13.130	&13.099	&13.109	&13.107	&			&12.888	&13.263	&13.120	&13.118	&13.078	&13.090	&	\\
+				&	$^1\Pi_u$ 		&14.091	&13.765	&13.635	&13.591	&13.551	&13.560	&13.558	&			&13.963	&13.674	&13.494	&13.455	&13.409	&13.419\\
+	\ce{HCl}	&	$^1\Pi$ 		&7.895	&7.862	&7.819	&7.815	&7.822	&7.822	&7.823	&7.823(0)	&7.959	&7.906	&7.840	&7.834	&7.837	&7.837	&7.838(1)\\
+	\ce{H2S}	&	$^1B_1$  		&6.157	&6.141	&6.098	&6.098	&6.102	&6.103	&6.103	&6.103(1)	&6.304	&6.294	&6.240	&6.237	&6.238	&6.238	&6.240(7)\\
+				&	$^1A_2$  		&6.431	&6.343	&6.293	&6.286	&6.286	&6.286	&6.286	&6.286(0)	&6.345	&6.246	&6.192	&6.185	&6.181	&6.181	&6.181(6) \\
+	\ce{H2O}	&	$^1B_1$  		&7.089	&7.447	&7.511	&7.497	&7.531	&7.528	&7.532	&7.533(0)	&7.234	&7.597	&7.605	&7.591	&7.623	&7.620	&7.626(3)\\
+				&	$^1A_2$  		&8.743	&9.213	&9.293	&9.279	&9.317	&9.313	&9.318	&9.318(0)	&8.889	&9.361	&9.382	&9.368	&9.405	&9.400	&9.407(7)\\
+				&	$^1A_1$  		&9.486	&9.861	&9.921	&9.903	&9.940	&9.937	&9.941	&9.941(0)	&9.580	&9.957	&9.966	&9.949	&9.986	&9.981	&9.986(2)\\
 	\hline
-	MAE			&					&0.112	&0.041	&0.028	&0.018	&0.003	&0.002	\\
-	MSE			&					&0.079	&0.032	&0.014	&0.002	&0.000	&0.000	\\
+	MAE			&					&0.257	&0.112	&0.028	&0.018	&0.003	&0.002	\\
+	MSE			&					&0.031	&0.079	&0.014	&0.002	&0.000	&0.000	\\
 	\end{tabular}
@@
 
-Table \ref{tab:BigTab} gathers vertical excitation energies obtained with various CC models as well as FCI estimates.
+Table \ref{tab:BigTab} gathers vertical excitation energies obtained with various CC models as well as FCI estimates for the two basis sets as well as the mean absolute errors (MAEs) and mean signed errors (MSEs) with respect to CCSDTQP for these models.
 

### 2021-05-03 Manuscript/CC4.tex
1st draft

@@
 \begin{abstract}
-\titou{Here comes the abstract.}
+We report the first investigation of the performance of the CC4 model, which approximately includes quadruple excitations within coupled-cluster theory, for vertical excitation energies in molecular systems.
+By considering a set of 25 excited states in 8 small molecules for which we have computed CCSDTQP and FCI reference energies, we show that CC4 yields excitation energies with sub-kJ~mol$^{-1}$ accuracy in very close agreement with its more expensive CCSDTQ parent.
+Therefore, if one aims at high accuracy, CC4 stands as a highly competitive approximate method to model molecular excited states.
 \end{abstract}
@@
 
-Single-reference coupled-cluster (CC) theory cprovides a hierarchy of size-extensive methods which delivers increasingly accurate energies and properties via the systematic increase of the maximum excitation degree of the cluster operator $\hT = \hT_1 + \hT_2 + \ldots + \hT_k$ (where $k \ge n$ and $n$ is the number of electrons).
+Single-reference coupled-cluster (CC) theory provides a hierarchy of size-extensive methods which delivers increasingly accurate energies and properties via the systematic increase of the maximum excitation degree of the cluster operator $\hT = \hT_1 + \hT_2 + \ldots + \hT_k$ (where $k \ge n$ and $n$ is the number of electrons).
 \cite{Cizek_1966,Paldus_1972,Crawford_2000,Bartlett_2007,Shavitt_2009}
@@
 The FCI estimates were obtained with the SCI algorithm known as \textit{``configuration interaction using a perturbative selection made iteratively''} (CIPSI) implemented in {\QP}. \cite{qp2}
-The error bars associated with these CIPSI calculations have been computed using our recently-developed protocol presented in Ref.~\onlinecite{Veril_2021}.
+The error bars associated with the extrapolation step of the CIPSI calculations (see Ref.~\onlinecite{qp2}) have been computed using our recently-developed protocol presented in Ref.~\onlinecite{Veril_2021}.
 
@@
 	\ce{BF}		&	$^1\Pi$ 		&6.509	&6.534	&6.478	&6.491	&6.484	&6.485	&6.485	&6.485(1)	&6.445	&6.464	&6.410	&6.423	&6.416	&6.417	&6.418(2)\\
-	\ce{CO}		&	$^1\Pi$ 		&8.724	&8.671	&8.572	&8.574	&8.562	&8.563	&8.561	&8.565(2)	&8.638	&8.587	&8.486	&8.492	&8.479	&8.480	&	\\
+	\ce{CO}		&	$^1\Pi$ 		&8.724	&8.671	&8.572	&8.574	&8.562	&8.563	&8.561	&8.563(4)	&8.638	&8.587	&8.486	&8.492	&8.479	&8.480	&	\\
 				&	$^1\Sigma^-$ 	&10.381	&10.096	&10.122	&10.062	&10.055	&10.057	&10.057	&10.056(1)	&10.297	&9.986	&9.992	&9.940	&9.930	&9.932	&	\\
@@
 
-Table \ref{tab:BigTab} gathers vertical excitation energies obtained with various CC models as well as FCI estimates for the two basis sets as well as the mean absolute errors (MAEs) and mean signed errors (MSEs) with respect to CCSDTQP for these models.
-
 %%% FIG 1 %%%
@@
 	\caption{
-	Distribution of the error (in eV) in excitation energies (with respect to the CCSDTQP values) for various methods obtained with the aug-cc-pVDZ basis.
+	Distribution of the error (in eV) in excitation energies (with respect to the CCSDTQP values) for CC2, CC3, and CC4 (top) and CCSD, CCSDT, and CCSDTQ (bottom) obtained with the aug-cc-pVDZ basis.
 	See Table \ref{tab:BigTab} for the raw data.
-	\label{fig:MAE}}
+	\label{fig:error}}
 \end{figure}
+%%% %%% %%% %%%
+
+Table \ref{tab:BigTab} gathers, for the two considered basis sets, the 25 vertical excitation energies computed for our set of 8 molecules with various CC models as well as the FCI estimates computed with CIPSI.
+The mean absolute errors (MAEs) and mean signed errors (MSEs) with respect to CCSDTQP are also reported for these models.
+These statistical quantities nicely illustrate the systematic improvement of the transition energies when one ramps up the computational effort following the series CC2, CCSD, CC3, CCSDT, CC4, and CCSDTQ.
+The distribution of the errors are reported in Fig.~\ref{fig:error} for these 6 levels of theory.
+The FCI estimates shows how accurate are the CCSDTQP reference data with a maximum deviation of \SI{0.002}{\eV} when one considers the aug-cc-pVDZ basis.
+For the larger aug-cc-pVTZ basis, the CCSDTQ and FCI remain in excellent agreement although the error bars associated with the extrapolated FCI values prevent us from any quantitative comparisons.
+
+For the two basis sets, the key result that we would like to highlight here is the outstanding similarity of the CC4 and CCSDTQ excitation energies with mean absolute and signed deviations below (equal to) \SI{0.001}{\eV} and a maximum deviation of \SI{0.011}{\eV} (\SI{0.007}{\eV}) between to the two sets of data obtained with the aug-cc-pVDZ (aug-cc-pVTZ) basis set.
+Overall, including quadruples allows to reach sub-\si{\kJ\per\mol} accuracy (\ie, average error below \SI{0.01}{\eV}) with only a rather minor improvement going from CC4 to CCSDTQ.
 
@@
 
-\titou{Here comes the conclusion.}
+We can therefore conclude that, for this set of small molecules at least, CC4 is a rather competitive approximation to its more expensive CCSDTQ parent.
+Although further investigations on larger compounds is definitely required, the present results are very encouraging as CC4, with its $\order*{N^9}$ scaling, can be applied to significantly larger systems than CCSDTQ (which scales as $\order*{N^{10}}$).
+This will certainly allow us to revisit, in the near future, some of the theoretical best estimates defined in the context of the QUEST database.\cite{Loos_2020a,Veril_2021}
 

### 2021-05-04 Manuscript/CC4.tex
OK with 1st draft

@@
 \begin{abstract}
-We report the first investigation of the performance of the CC4 model, which approximately includes quadruple excitations within coupled-cluster theory, for vertical excitation energies in molecular systems.
+We report the first investigation of the performance of CC4 --- an approximate coupled-cluster model which includes iteratively quadruple excitations --- for vertical excitation energies in molecular systems.
 By considering a set of 25 excited states in 8 small molecules for which we have computed CCSDTQP and FCI reference energies, we show that CC4 yields excitation energies with sub-kJ~mol$^{-1}$ accuracy in very close agreement with its more expensive CCSDTQ parent.
@@
 
-Single-reference coupled-cluster (CC) theory provides a hierarchy of size-extensive methods which delivers increasingly accurate energies and properties via the systematic increase of the maximum excitation degree of the cluster operator $\hT = \hT_1 + \hT_2 + \ldots + \hT_k$ (where $k \ge n$ and $n$ is the number of electrons).
+Single-reference coupled-cluster (CC) theory provides a hierarchy of size-extensive methods which delivers increasingly accurate energies and properties via the systematic increase of the maximum excitation degree of the cluster operator $\hT = \hT_1 + \hT_2 + \ldots + \hT_k$ (where $k \le n$ and $n$ is the number of electrons).
 \cite{Cizek_1966,Paldus_1972,Crawford_2000,Bartlett_2007,Shavitt_2009}
-Without any truncation (\ie, $k = n$), the so-called full CC (FCC) method is equivalent to full configuration interaction (FCI), hence providing the exact energy and wave function of the system within a given basis set.
+Without any truncation (\ie, $k = n$), the so-called full CC (FCC) method is equivalent to full configuration interaction (FCI), hence providing the exact energy and wave function of the system for a given basis set.
 However, it is not computationally viable due to its exponential scaling with system size, and one has to resort to truncated CC methods  (\ie, $k \ll n$) for computational convenience.
@@
 \cite{Christiansen_1998}
-These methods scale as $\order*{N^{5}}$, $\order*{N^{7}}$, and $\order*{N^{9}}$, respectively, and can be seen as cheaper approximations of CCSD, CCSDT, and CCSDTQ, by skipping the most expensive terms and avoiding the storage of the higher-excitation amplitudes.
+These iterative methods scale as $\order*{N^{5}}$, $\order*{N^{7}}$, and $\order*{N^{9}}$, respectively, and can be seen as cheaper approximations of CCSD, CCSDT, and CCSDTQ, by skipping the most expensive terms and avoiding the storage of the higher-excitation amplitudes.
 A somehow similar strategy has been applied to produce the CCSDT-3 \cite{Urban_1985,Noga_1987b} and CCSDTQ-3 \cite{Kallay_2005} models based on arguments stemming from perturbation theory.
-Of course, many more approximate CC models have been developed and we refer the interested reader to specialized reviews for more details. \cite{Crawford_2000,Piecuch_2002,Bartlett_2007,Shavitt_2009}
+Of course, a plethora of approximate CC models have been developed over the years and we refer the interested reader to specialized reviews for more details.
+\cite{Crawford_2000,Piecuch_2002,Bartlett_2007,Shavitt_2009}
 
-Coupled-cluster methods have been particularly successful for small- and medium-sized molecules in the field of thermodynamics, kinetics, and spectroscopy, thanks to the computations of accurate equilibrium geometries, \cite{Kallay_2003} potential energy surfaces, vibrational frequencies, \cite{Kallay_2004a} Born-Oppenheimer correction, \cite{Gauss_2006} and a vast panel of properties such as dipoles (and higher moments), \cite{Kallay_2003}  NMR chemical shifts, \cite{Kallay_2004a} magnetizabilities, \cite{Gauss_2009} polarizabilities, \cite{Kallay_2006} etc.
+Coupled-cluster methods have been particularly successful for small- and medium-sized molecules in the field of thermodynamics, kinetics, and spectroscopy, thanks to the computations of accurate equilibrium geometries, \cite{Kallay_2003} potential energy surfaces, vibrational frequencies, \cite{Kallay_2004a} Born-Oppenheimer corrections, \cite{Gauss_2006} and a vast panel of properties such as dipoles (and higher moments), \cite{Kallay_2003}  NMR chemical shifts, \cite{Kallay_2004a} magnetizabilities, \cite{Gauss_2009} polarizabilities, \cite{Kallay_2006} etc.
 Although originally developed for ground-state energies and properties, CC has been successfully extended to excited states \cite{Monkhorst_1977} thanks to the equation-of-motion (EOM) \cite{Emrich_1981,Comeau_1993,Stanton_1993,Krylov_2008} and linear-response (LR) \cite{Ghosh_1981,Sekino_1984,Koch_1990a,Koch_1990b,Rico_1993} formalisms which are known to produce identical excitation energies but different properties.
+\cite{Chrayteh_2021,Sarkar_2021}
 In EOM-CC, one determines vertical excitation energies via the diagonalization of the similarity-transformed Hamiltonian $\bH = e^{-\hT} \hH e^{\hT}$.
@@
 
-Recently, a large collection of deterministic, stochastic or hybrid selected CI (SCI) methods \cite{Bender_1969,Whitten_1969,Huron_1973} has (re)appeared \cite{Booth_2009,Deustua_2017,Holmes_2016,Eriksen_2017,Xu_2018,Giner_2013,Giner_2015,Evangelista_2014,Tubman_2016,Liu_2016,Ohtsuka_2017,Zimmerman_2017,Coe_2018,Garniron_2018} in the electronic structure landscape providing an alternative route to highly-accurate ground- and excited-state energies \cite{Holmes_2017,Li_2018,Li_2020,Loos_2018a,Chien_2018,Loos_2019,Loos_2020b,Loos_2020c,Loos_2020e,qp2,Eriksen_2020,Yao_2020,Veril_2021} (see Refs.~\onlinecite{Loos_2020a,Eriksen_2021} for recent reviews).
-The general idea behind SCI methods is simple: rather than exploring the entire FCI space by systematically increasing the maximum excitation degree of the determinants taken into account (leading to the slowly convergent and size-inconsistent series of methods CISD, CISDT, CISDTQ, \ldots), one performs a sparse exploration of the FCI space by selecting only the most energetically-important determinants thanks to a suitable criterion usually based on perturbation theory.
+Recently, a large collection of deterministic, stochastic or hybrid selected CI (SCI) methods \cite{Bender_1969,Whitten_1969,Huron_1973} has (re)appeared \cite{Booth_2009,Deustua_2017,Holmes_2016,Eriksen_2017,Xu_2018,Giner_2013,Giner_2015,Evangelista_2014,Tubman_2016,Liu_2016,Ohtsuka_2017,Zimmerman_2017,Coe_2018,Garniron_2018,Eriksen_2019} in the electronic structure landscape providing an alternative route to highly-accurate ground- and excited-state energies \cite{Holmes_2017,Li_2018,Li_2020,Loos_2018a,Chien_2018,Loos_2019,Loos_2020b,Loos_2020c,Loos_2020e,qp2,Eriksen_2020,Yao_2020,Veril_2021} (see Refs.~\onlinecite{Loos_2020a,Eriksen_2021} for recent reviews).
+The general idea behind SCI methods is simple: rather than exploring the entire FCI space by systematically increasing the maximum excitation degree of the determinants taken into account (leading to the slowly convergent and size-inconsistent series of methods CISD, CISDT, CISDTQ, \ldots), one performs a sparse exploration of the FCI space by selecting only the most energetically important determinants thanks to a suitable criterion usually based on perturbation theory.
 \cite{Huron_1973,Garniron_2017,Sharma_2017,qp2}
@@
 
-In this context, the main purpose of the present study is to assess the relative accuracy of the approximate CC4 model against the most expensive CCSDTQ and CCSDTQP methods in the case of vertical excitation energies, as well as its absolute accuracy with respect to FCI.
+In this context, the main purpose of the present study is to assess the relative accuracy of the approximate iterative CC4 model against the most expensive CCSDTQ and CCSDTQP methods in the case of vertical excitation energies, as well as its absolute accuracy with respect to FCI.
 To do so, we consider a set of 8 small molecules (\ce{NH3}, \ce{BH}, \ce{BF}, \ce{CO}, \ce{N2}, \ce{HCl}, \ce{H2S}, and \ce{H2O}) and we compare the excitation energies associated with 25 singlet excited states of various natures ($\npis$, $\pipis$, Rydberg, valence, charge-transfer, \ldots) and spatial symmetries obtained with various high-level CC methods.
-Although several studies have been published on the performance of CC4 for ground-state energies and properties, \cite{Kallay_2005,Matthews_2015a,Matthews_2021} to the best of our knowledge, CC4 has never been considered to compute excited-states energies before.
+Although a small number of studies have been published on the performance of CC4 for ground-state energies and properties, \cite{Kallay_2005,Matthews_2015a,Matthews_2021} to the best of our knowledge, CC4 has never been considered to compute excited-states energies before.
 As we shall see below, CC4 is an excellent approximation to its CCSDTQ parent, and produces excitation energies with sub-\si{\kJ\per\mol} accuracy for this set of small molecules, well below the chemical accuracy threshold.
@@
 The FCI estimates were obtained with the SCI algorithm known as \textit{``configuration interaction using a perturbative selection made iteratively''} (CIPSI) implemented in {\QP}. \cite{qp2}
-The error bars associated with the extrapolation step of the CIPSI calculations (see Ref.~\onlinecite{qp2}) have been computed using our recently-developed protocol presented in Ref.~\onlinecite{Veril_2021}.
+The error bars associated with the extrapolation step of the CIPSI calculations (see Ref.~\onlinecite{qp2}) have been computed using our recently developed protocol presented in Ref.~\onlinecite{Veril_2021}.
 
@@
 Table \ref{tab:BigTab} gathers, for the two considered basis sets, the 25 vertical excitation energies computed for our set of 8 molecules with various CC models as well as the FCI estimates computed with CIPSI.
-The mean absolute errors (MAEs) and mean signed errors (MSEs) with respect to CCSDTQP are also reported for these models.
+The mean absolute errors (MAEs) and mean signed errors (MSEs) with respect to CCSDTQP are also reported for these models for the aug-cc-pVDZ basis.
 These statistical quantities nicely illustrate the systematic improvement of the transition energies when one ramps up the computational effort following the series CC2, CCSD, CC3, CCSDT, CC4, and CCSDTQ.
-The distribution of the errors are reported in Fig.~\ref{fig:error} for these 6 levels of theory.
+Note, in particular, the significant improvement brought by CC4 in terms of MAE and MSE as compared to the third-order methods, CC3 and CCSDT, which shows how important can be quadruple excitations when one aims for high accuracy.
+The distribution of the errors are reported in Fig.~\ref{fig:error} for each level of theory.
 The FCI estimates shows how accurate are the CCSDTQP reference data with a maximum deviation of \SI{0.002}{\eV} when one considers the aug-cc-pVDZ basis.
@@
 
-We can therefore conclude that, for this set of small molecules at least, CC4 is a rather competitive approximation to its more expensive CCSDTQ parent.
-Although further investigations on larger compounds is definitely required, the present results are very encouraging as CC4, with its $\order*{N^9}$ scaling, can be applied to significantly larger systems than CCSDTQ (which scales as $\order*{N^{10}}$).
+We can therefore conclude that, for this set of small molecules at least, CC4 is a rather competitive approximation to its more expensive CCSDTQ parent as well as a significant improvement of its third-order version, CC3, and the ``complete'' CCSDT method.
+Although further investigations on larger compounds are definitely required, the present results are very encouraging as CC4, with its $\order*{N^9}$ scaling, can be applied to significantly larger molecules than CCSDTQ [which scales as $\order*{N^{10}}$].
 This will certainly allow us to revisit, in the near future, some of the theoretical best estimates defined in the context of the QUEST database.\cite{Loos_2020a,Veril_2021}
@@
 PFL has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481).
+DJ is indebted to the CCIPL computational center installed in Nantes for (the always very) generous allocation of computational time. 
+He also thanks the ANR for financial support in the framework of the BSE-forces grant (ANR-20-CE29-0005).
 \end{acknowledgements}

### 2021-05-04 Manuscript/CC4.tex
Corrections Denis

@@
 
-\title{How accurate is CC4 for vertical excitation energies?}
+\title{How accurate are EOM-CC4 vertical excitation energies?}
 
@@
 \begin{abstract}
-We report the first investigation of the performance of CC4 --- an approximate coupled-cluster model which includes iteratively quadruple excitations --- for vertical excitation energies in molecular systems.
-By considering a set of 25 excited states in 8 small molecules for which we have computed CCSDTQP and FCI reference energies, we show that CC4 yields excitation energies with sub-kJ~mol$^{-1}$ accuracy in very close agreement with its more expensive CCSDTQ parent.
-Therefore, if one aims at high accuracy, CC4 stands as a highly competitive approximate method to model molecular excited states.
+We report the first investigation of the performance of EOM-CC4 --- an approximate equation-of-motion coupled-cluster model which includes iteratively quadruple excitations --- for vertical excitation energies in molecular systems.
+By considering a set of 25 excited states in 8 small molecules for which we have computed CCSDTQP and FCI reference energies, we show that CC4 yields excitation energies with sub-kJ~mol$^{-1}$ accuracy, in very close agreement with its more expensive CCSDTQ parent.
+Therefore, if one aims at high accuracy, CC4 stands as a highly competitive approximate method to model molecular excited states, significantly improving over both CC3 and CCSDT.
 \end{abstract}
@@
 
-Single-reference coupled-cluster (CC) theory provides a hierarchy of size-extensive methods which delivers increasingly accurate energies and properties via the systematic increase of the maximum excitation degree of the cluster operator $\hT = \hT_1 + \hT_2 + \ldots + \hT_k$ (where $k \le n$ and $n$ is the number of electrons).
+Single-reference coupled-cluster (CC) theory provides a hierarchy of size-extensive methods delivering increasingly accurate energies and properties via the systematic increase of the maximum excitation degree of the cluster operator $\hT = \hT_1 + \hT_2 + \ldots + \hT_k$ (where $k \le n$ and $n$ is the number of electrons).
 \cite{Cizek_1966,Paldus_1972,Crawford_2000,Bartlett_2007,Shavitt_2009}
-Without any truncation (\ie, $k = n$), the so-called full CC (FCC) method is equivalent to full configuration interaction (FCI), hence providing the exact energy and wave function of the system for a given basis set.
+Without any truncation (\ie, $k = n$), the so-called full CC (FCC) method is equivalent to full configuration interaction (FCI), hence providing the exact energy and wave function of the system for a given atomic basis set.
 However, it is not computationally viable due to its exponential scaling with system size, and one has to resort to truncated CC methods  (\ie, $k \ll n$) for computational convenience.
@@
 These iterative methods scale as $\order*{N^{5}}$, $\order*{N^{7}}$, and $\order*{N^{9}}$, respectively, and can be seen as cheaper approximations of CCSD, CCSDT, and CCSDTQ, by skipping the most expensive terms and avoiding the storage of the higher-excitation amplitudes.
-A somehow similar strategy has been applied to produce the CCSDT-3 \cite{Urban_1985,Noga_1987b} and CCSDTQ-3 \cite{Kallay_2005} models based on arguments stemming from perturbation theory.
-Of course, a plethora of approximate CC models have been developed over the years and we refer the interested reader to specialized reviews for more details.
+A somehow similar strategy has been applied to define the CCSDT-3 \cite{Urban_1985,Noga_1987b} and CCSDTQ-3 \cite{Kallay_2005} models based on arguments stemming from perturbation theory.
+Of course, a plethora of other approximate CC models have been developed over the years and we refer the interested reader to specialized reviews for more details.
 \cite{Crawford_2000,Piecuch_2002,Bartlett_2007,Shavitt_2009}
@@
 Although originally developed for ground-state energies and properties, CC has been successfully extended to excited states \cite{Monkhorst_1977} thanks to the equation-of-motion (EOM) \cite{Emrich_1981,Comeau_1993,Stanton_1993,Krylov_2008} and linear-response (LR) \cite{Ghosh_1981,Sekino_1984,Koch_1990a,Koch_1990b,Rico_1993} formalisms which are known to produce identical excitation energies but different properties.
-\cite{Chrayteh_2021,Sarkar_2021}
+\cite{Chrayteh_2021,Sarkar_2021}%DJ: Pas sur que les deux meilleures refs ici, si ?
+Tu veux pas des trucs plus seminaux ?
 In EOM-CC, one determines vertical excitation energies via the diagonalization of the similarity-transformed Hamiltonian $\bH = e^{-\hT} \hH e^{\hT}$.
 A more general procedure to compute excitation energies that can be applied to any approximate CC model (as the ones mentioned above) consists in diagonalizing the so-called CC Jacobian obtained via the differentiation of the CC amplitude equations.
-Again, by systematically increasing the maximum excitation degree of $\hT$, one can systematically produce increasingly accurate excitation energies with the ``complete'' series CCSD, \cite{Stanton_1993} CCSDT, \cite{Kowalski_2001,Kucharski_2001} CCSDTQ, \cite{Hirata_2004} CCSDTQP, \cite{Kallay_2004b} \ldots~or the ``approximate'' series CC2, \cite{Christiansen_1995a} CC3, \cite{Christiansen_1995b} CC4, \cite{Kallay_2004b} \ldots~while retaining the formal scaling of their ground-state analog.
+Again, by systematically increasing the maximum excitation degree of $\hT$, one can systematically produce increasingly accurate EOM/LR excitation energies with the ``complete'' series CCSD, \cite{Stanton_1993} CCSDT, \cite{Kowalski_2001,Kucharski_2001} CCSDTQ, \cite{Hirata_2004} CCSDTQP\cite{Kallay_2004b} \ldots~or the ``approximate'' series CC2, \cite{Christiansen_1995a} CC3, \cite{Christiansen_1995b} CC4 \cite{Kallay_2004b} \ldots~while retaining the formal scaling of their ground-state analog.
+We drop the EOM prefix below as all our calculations are made within that approach.
 
-Recently, a large collection of deterministic, stochastic or hybrid selected CI (SCI) methods \cite{Bender_1969,Whitten_1969,Huron_1973} has (re)appeared \cite{Booth_2009,Deustua_2017,Holmes_2016,Eriksen_2017,Xu_2018,Giner_2013,Giner_2015,Evangelista_2014,Tubman_2016,Liu_2016,Ohtsuka_2017,Zimmerman_2017,Coe_2018,Garniron_2018,Eriksen_2019} in the electronic structure landscape providing an alternative route to highly-accurate ground- and excited-state energies \cite{Holmes_2017,Li_2018,Li_2020,Loos_2018a,Chien_2018,Loos_2019,Loos_2020b,Loos_2020c,Loos_2020e,qp2,Eriksen_2020,Yao_2020,Veril_2021} (see Refs.~\onlinecite{Loos_2020a,Eriksen_2021} for recent reviews).
+Recently, a large collection of deterministic, stochastic or hybrid selected CI (SCI) methods \cite{Bender_1969,Whitten_1969,Huron_1973} made their comeback \cite{Booth_2009,Deustua_2017,Holmes_2016,Eriksen_2017,Xu_2018,Giner_2013,Giner_2015,Evangelista_2014,Tubman_2016,Liu_2016,Ohtsuka_2017,Zimmerman_2017,Coe_2018,Garniron_2018,Eriksen_2019} in the electronic structure landscape providing an alternative route to highly-accurate ground- and excited-state energies \cite{Holmes_2017,Li_2018,Li_2020,Loos_2018a,Chien_2018,Loos_2019,Loos_2020b,Loos_2020c,Loos_2020e,qp2,Eriksen_2020,Yao_2020,Veril_2021} (see Refs.~\onlinecite{Loos_2020a,Eriksen_2021} for recent reviews).
 The general idea behind SCI methods is simple: rather than exploring the entire FCI space by systematically increasing the maximum excitation degree of the determinants taken into account (leading to the slowly convergent and size-inconsistent series of methods CISD, CISDT, CISDTQ, \ldots), one performs a sparse exploration of the FCI space by selecting only the most energetically important determinants thanks to a suitable criterion usually based on perturbation theory.
 \cite{Huron_1973,Garniron_2017,Sharma_2017,qp2}
-By iteratively increasing the number of determinants of the variational space and supplemented it with a second-order perturbative correction (PT2), the SCI+PT2 family of methods has been recently shown to produce near-FCI correlation and excitation energies for small- and medium-size molecules in compact basis sets.\cite{Holmes_2017,Loos_2018a,Chien_2018,Loos_2019,Loos_2020b,Loos_2020c,qp2,Veril_2021}
-Although the formal scaling of such algorithms remain exponential, the prefactor is greatly reduced which explains their current attractiveness in the electronic structure community and much wider applicability than their common FCI parent.
+By iteratively increasing the number of determinants of the variational space and supplementing it with a second-order perturbative correction (PT2), the SCI+PT2 family of methods has been recently shown to produce near-FCI correlation and excitation energies for small- and medium-size molecules in compact basis sets.\cite{Holmes_2017,Loos_2018a,Chien_2018,Loos_2019,Loos_2020b,Loos_2020c,qp2,Veril_2021}
+Although the formal scaling of such algorithms remain exponential, the prefactor is greatly reduced which explains their current attractiveness in the electronic structure community and much wider applicability than their standard FCI parent.
 
@@
 \cite{Loos_2018a,Loos_2019,Loos_2020a,Loos_2020b,Loos_2020c,Veril_2021}
-The main purpose of this so-called QUEST database is to provide reference excitation energies in order to perform fair and reliable comparisons between electronic structure methods and assess their strengths and weakness in a large panel of chemical scenarios.
+The main purpose of this so-called QUEST database is to provide reference excitation energies in order to perform fair and reliable benchmarks between electronic structure methods and assess their strengths and weakness in a large panel of chemical scenarios.
 Most of these reference transition energies, which rely exclusively on high-level \textit{ab initio} calculations, can be reasonably considered as chemically accurate, \ie, within \SI{1}{\kcal\per\mol} or \SI{0.043}{\eV} of the FCI limit.
@@
 Therefore, for the larger molecules of the QUEST database, we mostly relied on CCSDT to define reference excitation energies.
-Of course, it would be highly valuable to have access to more accurate methods (including, at least, quadruple excitations) in order to refine, in the near future, these theoretical best estimates.
+Of course, it would be highly valuable to have access to more accurate methods (including, at least, quadruple excitations) in order to refine these theoretical best estimates.
 
-In this context, the main purpose of the present study is to assess the relative accuracy of the approximate iterative CC4 model against the most expensive CCSDTQ and CCSDTQP methods in the case of vertical excitation energies, as well as its absolute accuracy with respect to FCI.
-To do so, we consider a set of 8 small molecules (\ce{NH3}, \ce{BH}, \ce{BF}, \ce{CO}, \ce{N2}, \ce{HCl}, \ce{H2S}, and \ce{H2O}) and we compare the excitation energies associated with 25 singlet excited states of various natures ($\npis$, $\pipis$, Rydberg, valence, charge-transfer, \ldots) and spatial symmetries obtained with various high-level CC methods.
-Although a small number of studies have been published on the performance of CC4 for ground-state energies and properties, \cite{Kallay_2005,Matthews_2015a,Matthews_2021} to the best of our knowledge, CC4 has never been considered to compute excited-states energies before.
+In this context, the main purpose of the present study is to assess the relative accuracy of the approximate iterative CC4 model against the more expensive CCSDTQ and CCSDTQP methods in the case of vertical excitation energies, as well as its absolute accuracy with respect to FCI.
+To do so, we consider a set of 8 small molecules (\ce{NH3}, \ce{BH}, \ce{BF}, \ce{CO}, \ce{N2}, \ce{HCl}, \ce{H2S}, and \ce{H2O}) and we compare the excitation energies associated with 25 singlet excited states of various natures ($\npis$, $\pipis$, Rydberg, valence, charge-transfer\ldots) and spatial symmetries obtained with various high-level CC methods.
+Although a small number of studies have been published on the performance of CC4 for ground-state energies and properties, \cite{Kallay_2005,Matthews_2015a,Matthews_2021} this work stands, to the best of our knowledge, as the first to consider CC4  to compute excited-states energies.
 As we shall see below, CC4 is an excellent approximation to its CCSDTQ parent, and produces excitation energies with sub-\si{\kJ\per\mol} accuracy for this set of small molecules, well below the chemical accuracy threshold.
@@
 
-All calculations have been performed in the frozen-core approximation and the CC3/aug-cc-pVTZ geometries of the system considered here have been extracted from previous studies at the exception of \ce{BH} and \ce{BF}.
-\cite{Loos_2018a}
+All calculations have been performed in the frozen-core approximation and the CC3/aug-cc-pVTZ geometries of the system considered here have been extracted from previous studies.
+\cite{Loos_2018a,Chrayteh_2021}
 In the following, we consider diffuse-containing Dunning's double- and triple-$\zeta$ basis sets (aug-cc-pVDZ and aug-cc-pVTZ).
@@
 Table \ref{tab:BigTab} gathers, for the two considered basis sets, the 25 vertical excitation energies computed for our set of 8 molecules with various CC models as well as the FCI estimates computed with CIPSI.
-The mean absolute errors (MAEs) and mean signed errors (MSEs) with respect to CCSDTQP are also reported for these models for the aug-cc-pVDZ basis.
-These statistical quantities nicely illustrate the systematic improvement of the transition energies when one ramps up the computational effort following the series CC2, CCSD, CC3, CCSDT, CC4, and CCSDTQ.
-Note, in particular, the significant improvement brought by CC4 in terms of MAE and MSE as compared to the third-order methods, CC3 and CCSDT, which shows how important can be quadruple excitations when one aims for high accuracy.
+First, we underline that the FCI estimates show how accurate are the CCSDTQP reference data are, with a maximum deviation of \SI{0.002}{\eV} when one considers the aug-cc-pVDZ basis.
+For the larger aug-cc-pVTZ basis,
+the CCSDTQ and FCI remain in excellent agreement although the error bars associated with the extrapolated FCI values prevent us from any quantitative comparisons.
+
+The mean absolute errors (MAEs) and mean signed errors (MSEs) with respect to CCSDTQP are reported in the bottom of  Table \ref{tab:BigTab} for the CC2-to-CCSDTQ models for the aug-cc-pVDZ basis.
 The distribution of the errors are reported in Fig.~\ref{fig:error} for each level of theory.
-The FCI estimates shows how accurate are the CCSDTQP reference data with a maximum deviation of \SI{0.002}{\eV} when one considers the aug-cc-pVDZ basis.
-For the larger aug-cc-pVTZ basis, the CCSDTQ and FCI remain in excellent agreement although the error bars associated with the extrapolated FCI values prevent us from any quantitative comparisons.
-
-For the two basis sets, the key result that we would like to highlight here is the outstanding similarity of the CC4 and CCSDTQ excitation energies with mean absolute and signed deviations below (equal to) \SI{0.001}{\eV} and a maximum deviation of \SI{0.011}{\eV} (\SI{0.007}{\eV}) between to the two sets of data obtained with the aug-cc-pVDZ (aug-cc-pVTZ) basis set.
-Overall, including quadruples allows to reach sub-\si{\kJ\per\mol} accuracy (\ie, average error below \SI{0.01}{\eV}) with only a rather minor improvement going from CC4 to CCSDTQ.
+The statistical quantities nicely illustrate the systematic improvement of the transition energies when one ramps up the computational effort following the series CC2, CCSD, CC3, CCSDT, CC4, and CCSDTQ.
+We note that the errors decrease by ca. one order of magnitude when switching from CCSD to CC3 and from CCSDT to CC4, whilst improvements of ca. 50\%\ ``only'' are noted when going from
+approximate to full levels, i.e., when going from CC2 to CCSD, from CC3 to CCSDT, and from CC4 to CCSDTQ. In other works  CC4 brings significant improvement in terms of MAE and MSE as compared to 
+the third-order methods, CC3 and CCSDT, which demonstrates the importance of quadruple excitations when one aims for high accuracy.
+Besides, for the two basis sets, there is an outstanding similarity of the CC4
+and CCSDTQ excitation energies with mean absolute and signed deviations below (equal to) \SI{0.001}{\eV} and a maximum deviation of \SI{0.011}{\eV} (\SI{0.007}{\eV}) between to the two sets of data obtained with
+the aug-cc-pVDZ (aug-cc-pVTZ) basis set.
+Therefore, including quadruples allows to reach sub-\si{\kJ\per\mol} accuracy (\ie, average error below \SI{0.01}{\eV}) with only a rather minor improvement going from CC4 to CCSDTQ.
 
@@
 
-We can therefore conclude that, for this set of small molecules at least, CC4 is a rather competitive approximation to its more expensive CCSDTQ parent as well as a significant improvement of its third-order version, CC3, and the ``complete'' CCSDT method.
-Although further investigations on larger compounds are definitely required, the present results are very encouraging as CC4, with its $\order*{N^9}$ scaling, can be applied to significantly larger molecules than CCSDTQ [which scales as $\order*{N^{10}}$].
-This will certainly allow us to revisit, in the near future, some of the theoretical best estimates defined in the context of the QUEST database.\cite{Loos_2020a,Veril_2021}
+For this set of small molecules at least, CC4 is a rather competitive approximation to its more expensive CCSDTQ parent as well as a very significant improvement of its third-order version, CC3, and the ``complete'' CCSDT method.
+This finding is promising, though we are well aware that the conclusions obtained for small and larger molecules might differ, i.e., CCSD outperforms CC2 for compact molecules (as here), but the reverse trend is often found
+for larger compounds.\cite{Loos_2018a,Loos_2020a,Veril_2021} Therefore, although further investigations on larger compounds are definitely required, the present results are very encouraging as CC4, with its $\order*{N^9}$ scaling,
+can be applied to significantly larger molecules than CCSDTQ [which scales as $\order*{N^{10}}$].
+This will likely allow us to revisit, in the future, some of the theoretical best estimates defined in the context of the QUEST database.\cite{Loos_2020a,Veril_2021}
 
@@
 \begin{acknowledgements}
-This work was performed using HPC resources from CALMIP (Toulouse) under allocation 2021-18005.
 PFL has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481).
-DJ is indebted to the CCIPL computational center installed in Nantes for (the always very) generous allocation of computational time. 
-He also thanks the ANR for financial support in the framework of the BSE-forces grant (ANR-20-CE29-0005).
+This work was performed using HPC resources from CALMIP (Toulouse) under allocation 2021-18005 and of the CCIPL computational center installed in Nantes.
 \end{acknowledgements}

### 2021-05-04 Manuscript/CC4.tex
v2 OK

@@
 By considering a set of 25 excited states in 8 small molecules for which we have computed CCSDTQP and FCI reference energies, we show that CC4 yields excitation energies with sub-kJ~mol$^{-1}$ accuracy, in very close agreement with its more expensive CCSDTQ parent.
-Therefore, if one aims at high accuracy, CC4 stands as a highly competitive approximate method to model molecular excited states, significantly improving over both CC3 and CCSDT.
+Therefore, if one aims at high accuracy, CC4 stands as a highly competitive approximate method to model molecular excited states, with a significant improvement over both CC3 and CCSDT.
 \end{abstract}
@@
 Although originally developed for ground-state energies and properties, CC has been successfully extended to excited states \cite{Monkhorst_1977} thanks to the equation-of-motion (EOM) \cite{Emrich_1981,Comeau_1993,Stanton_1993,Krylov_2008} and linear-response (LR) \cite{Ghosh_1981,Sekino_1984,Koch_1990a,Koch_1990b,Rico_1993} formalisms which are known to produce identical excitation energies but different properties.
-\cite{Chrayteh_2021,Sarkar_2021}%DJ: Pas sur que les deux meilleures refs ici, si ?
-Tu veux pas des trucs plus seminaux ?
 In EOM-CC, one determines vertical excitation energies via the diagonalization of the similarity-transformed Hamiltonian $\bH = e^{-\hT} \hH e^{\hT}$.
 A more general procedure to compute excitation energies that can be applied to any approximate CC model (as the ones mentioned above) consists in diagonalizing the so-called CC Jacobian obtained via the differentiation of the CC amplitude equations.
-Again, by systematically increasing the maximum excitation degree of $\hT$, one can systematically produce increasingly accurate EOM/LR excitation energies with the ``complete'' series CCSD, \cite{Stanton_1993} CCSDT, \cite{Kowalski_2001,Kucharski_2001} CCSDTQ, \cite{Hirata_2004} CCSDTQP\cite{Kallay_2004b} \ldots~or the ``approximate'' series CC2, \cite{Christiansen_1995a} CC3, \cite{Christiansen_1995b} CC4 \cite{Kallay_2004b} \ldots~while retaining the formal scaling of their ground-state analog.
-We drop the EOM prefix below as all our calculations are made within that approach.
+Again, by increasing the maximum excitation degree of $\hT$, one can systematically produce increasingly accurate EOM/LR excitation energies with the ``complete'' series CCSD, \cite{Stanton_1993} CCSDT, \cite{Kowalski_2001,Kucharski_2001} CCSDTQ, \cite{Hirata_2004} CCSDTQP\cite{Kallay_2004b} \ldots~or the ``approximate'' series CC2, \cite{Christiansen_1995a} CC3, \cite{Christiansen_1995b} CC4 \cite{Kallay_2004b} \ldots~while retaining the formal scaling of their ground-state analog.
+From here on, we drop the EOM prefix as all our calculations are performed within this approach.
 
-Recently, a large collection of deterministic, stochastic or hybrid selected CI (SCI) methods \cite{Bender_1969,Whitten_1969,Huron_1973} made their comeback \cite{Booth_2009,Deustua_2017,Holmes_2016,Eriksen_2017,Xu_2018,Giner_2013,Giner_2015,Evangelista_2014,Tubman_2016,Liu_2016,Ohtsuka_2017,Zimmerman_2017,Coe_2018,Garniron_2018,Eriksen_2019} in the electronic structure landscape providing an alternative route to highly-accurate ground- and excited-state energies \cite{Holmes_2017,Li_2018,Li_2020,Loos_2018a,Chien_2018,Loos_2019,Loos_2020b,Loos_2020c,Loos_2020e,qp2,Eriksen_2020,Yao_2020,Veril_2021} (see Refs.~\onlinecite{Loos_2020a,Eriksen_2021} for recent reviews).
+Recently, a large collection of deterministic, stochastic or hybrid selected CI (SCI) methods \cite{Bender_1969,Whitten_1969,Huron_1973} has (re)appeared \cite{Booth_2009,Deustua_2017,Holmes_2016,Eriksen_2017,Xu_2018,Giner_2013,Giner_2015,Evangelista_2014,Tubman_2016,Liu_2016,Ohtsuka_2017,Zimmerman_2017,Coe_2018,Garniron_2018,Eriksen_2019} in the electronic structure landscape providing an alternative route to highly-accurate ground- and excited-state energies \cite{Holmes_2017,Li_2018,Li_2020,Loos_2018a,Chien_2018,Loos_2019,Loos_2020b,Loos_2020c,Loos_2020e,qp2,Eriksen_2020,Yao_2020,Veril_2021} (see Refs.~\onlinecite{Loos_2020a,Eriksen_2021} for recent reviews).
 The general idea behind SCI methods is simple: rather than exploring the entire FCI space by systematically increasing the maximum excitation degree of the determinants taken into account (leading to the slowly convergent and size-inconsistent series of methods CISD, CISDT, CISDTQ, \ldots), one performs a sparse exploration of the FCI space by selecting only the most energetically important determinants thanks to a suitable criterion usually based on perturbation theory.
@@
 To do so, we consider a set of 8 small molecules (\ce{NH3}, \ce{BH}, \ce{BF}, \ce{CO}, \ce{N2}, \ce{HCl}, \ce{H2S}, and \ce{H2O}) and we compare the excitation energies associated with 25 singlet excited states of various natures ($\npis$, $\pipis$, Rydberg, valence, charge-transfer\ldots) and spatial symmetries obtained with various high-level CC methods.
-Although a small number of studies have been published on the performance of CC4 for ground-state energies and properties, \cite{Kallay_2005,Matthews_2015a,Matthews_2021} this work stands, to the best of our knowledge, as the first to consider CC4  to compute excited-states energies.
+Although a small number of studies have been published on the performance of CC4 for ground-state energies and properties, \cite{Kallay_2005,Matthews_2015a,Matthews_2021} this work stands, to the best of our knowledge, as the first to consider CC4 for the computation of excited-states energies.
 As we shall see below, CC4 is an excellent approximation to its CCSDTQ parent, and produces excitation energies with sub-\si{\kJ\per\mol} accuracy for this set of small molecules, well below the chemical accuracy threshold.
@@
 Table \ref{tab:BigTab} gathers, for the two considered basis sets, the 25 vertical excitation energies computed for our set of 8 molecules with various CC models as well as the FCI estimates computed with CIPSI.
-First, we underline that the FCI estimates show how accurate are the CCSDTQP reference data are, with a maximum deviation of \SI{0.002}{\eV} when one considers the aug-cc-pVDZ basis.
-For the larger aug-cc-pVTZ basis,
-the CCSDTQ and FCI remain in excellent agreement although the error bars associated with the extrapolated FCI values prevent us from any quantitative comparisons.
+First, we underline that the FCI estimates show how accurate the CCSDTQP reference data are, with a maximum deviation of \SI{0.002}{\eV} when one considers the aug-cc-pVDZ basis. 
+For the larger aug-cc-pVTZ basis, the CCSDTQ and FCI remain in excellent agreement although the error bars associated with the extrapolated FCI values prevent us from any quantitative comparisons.
 
-The mean absolute errors (MAEs) and mean signed errors (MSEs) with respect to CCSDTQP are reported in the bottom of  Table \ref{tab:BigTab} for the CC2-to-CCSDTQ models for the aug-cc-pVDZ basis.
+The mean absolute errors (MAEs) and mean signed errors (MSEs) with respect to CCSDTQP (and computed in the aug-cc-pVDZ basis) are reported in the bottom of Table \ref{tab:BigTab} for the CC2-to-CCSDTQ models.
 The distribution of the errors are reported in Fig.~\ref{fig:error} for each level of theory.
-The statistical quantities nicely illustrate the systematic improvement of the transition energies when one ramps up the computational effort following the series CC2, CCSD, CC3, CCSDT, CC4, and CCSDTQ.
-We note that the errors decrease by ca. one order of magnitude when switching from CCSD to CC3 and from CCSDT to CC4, whilst improvements of ca. 50\%\ ``only'' are noted when going from
-approximate to full levels, i.e., when going from CC2 to CCSD, from CC3 to CCSDT, and from CC4 to CCSDTQ. In other works  CC4 brings significant improvement in terms of MAE and MSE as compared to 
-the third-order methods, CC3 and CCSDT, which demonstrates the importance of quadruple excitations when one aims for high accuracy.
-Besides, for the two basis sets, there is an outstanding similarity of the CC4
-and CCSDTQ excitation energies with mean absolute and signed deviations below (equal to) \SI{0.001}{\eV} and a maximum deviation of \SI{0.011}{\eV} (\SI{0.007}{\eV}) between to the two sets of data obtained with
+These statistical quantities nicely illustrate the systematic improvement of the transition energies when one ramps up the computational effort following the series CC2, CCSD, CC3, CCSDT, CC4, and CCSDTQ.
+We note that the errors decrease by roughly one order of magnitude when switching from CCSD to CC3 and from CCSDT to CC4, whilst improvements of approximately 50\% ``only'' are noted when going from the ``approximate'' model to the ``complete'' method (\ie, from CC2 to CCSD, from CC3 to CCSDT, and from CC4 to CCSDTQ).
+In other words, CC4 brings significant improvement in terms of MAE and MSE as compared to the third-order methods, CC3 and CCSDT, which demonstrates the importance of quadruple excitations when one aims at high accuracy.
+Besides, for the two basis sets, there is an outstanding similarity between the CC4 and CCSDTQ excitation energies with mean absolute and signed deviations below (equal to) \SI{0.001}{\eV} and a maximum deviation of \SI{0.011}{\eV} (\SI{0.007}{\eV}) between to the two sets of data obtained with
 the aug-cc-pVDZ (aug-cc-pVTZ) basis set. 
@@
 
-For this set of small molecules at least, CC4 is a rather competitive approximation to its more expensive CCSDTQ parent as well as a very significant improvement of its third-order version, CC3, and the ``complete'' CCSDT method.
-This finding is promising, though we are well aware that the conclusions obtained for small and larger molecules might differ, i.e., CCSD outperforms CC2 for compact molecules (as here), but the reverse trend is often found
-for larger compounds.\cite{Loos_2018a,Loos_2020a,Veril_2021} Therefore, although further investigations on larger compounds are definitely required, the present results are very encouraging as CC4, with its $\order*{N^9}$ scaling,
-can be applied to significantly larger molecules than CCSDTQ [which scales as $\order*{N^{10}}$].
+For this set of small molecules at least, CC4 is a rather competitive approximation to its more expensive CCSDTQ parent as well as a very significant improvement over its third-order version, CC3, and the ``complete'' CCSDT method.
+These findings are promising, though we are well aware that the conclusions obtained for small and larger molecules might differ significantly.
+For example, CCSD outperforms CC2 for compact molecules (as here), but the opposite trend is often found for larger compounds.\cite{Loos_2018a,Loos_2020a,Veril_2021} 
+Therefore, although further investigations on larger compounds are definitely required, the present results are very encouraging as CC4, with its $\order*{N^9}$ scaling, can be applied to significantly larger molecules than CCSDTQ [which scales as $\order*{N^{10}}$].
 This will likely allow us to revisit, in the future, some of the theoretical best estimates defined in the context of the QUEST database.\cite{Loos_2020a,Veril_2021}

### 2021-05-04 Manuscript/CC4.tex
Devin comments

@@
 \begin{abstract}
-We report the first investigation of the performance of EOM-CC4 --- an approximate equation-of-motion coupled-cluster model which includes iteratively quadruple excitations --- for vertical excitation energies in molecular systems.
+We report the first investigation of the performance of EOM-CC4 --- an approximate equation-of-motion coupled-cluster model which includes iterative quadruple excitations --- for vertical excitation energies in molecular systems.
 By considering a set of 25 excited states in 8 small molecules for which we have computed CCSDTQP and FCI reference energies, we show that CC4 yields excitation energies with sub-kJ~mol$^{-1}$ accuracy, in very close agreement with its more expensive CCSDTQ parent.
@@
 These iterative methods scale as $\order*{N^{5}}$, $\order*{N^{7}}$, and $\order*{N^{9}}$, respectively, and can be seen as cheaper approximations of CCSD, CCSDT, and CCSDTQ, by skipping the most expensive terms and avoiding the storage of the higher-excitation amplitudes.
-A somehow similar strategy has been applied to define the CCSDT-3 \cite{Urban_1985,Noga_1987b} and CCSDTQ-3 \cite{Kallay_2005} models based on arguments stemming from perturbation theory.
+A somewhat similar strategy has been applied to define the CCSDT-3 \cite{Urban_1985,Noga_1987b} and CCSDTQ-3 \cite{Kallay_2005} models based on arguments stemming from perturbation theory.
 Of course, a plethora of other approximate CC models have been developed over the years and we refer the interested reader to specialized reviews for more details.
@@
 To do so, we consider a set of 8 small molecules (\ce{NH3}, \ce{BH}, \ce{BF}, \ce{CO}, \ce{N2}, \ce{HCl}, \ce{H2S}, and \ce{H2O}) and we compare the excitation energies associated with 25 singlet excited states of various natures ($\npis$, $\pipis$, Rydberg, valence, charge-transfer\ldots) and spatial symmetries obtained with various high-level CC methods.
-Although a small number of studies have been published on the performance of CC4 for ground-state energies and properties, \cite{Kallay_2005,Matthews_2015a,Matthews_2021} this work stands, to the best of our knowledge, as the first to consider CC4 for the computation of excited-states energies.
+Although a small number of studies have been published on the performance of CC4 for ground-state energies and properties, \cite{Kallay_2005,Matthews_2021} this work stands, to the best of our knowledge, as the first to consider CC4 for the computation of excited-states energies.
 As we shall see below, CC4 is an excellent approximation to its CCSDTQ parent, and produces excitation energies with sub-\si{\kJ\per\mol} accuracy for this set of small molecules, well below the chemical accuracy threshold.
@@
 \cite{mrcc}
-The present {\CFOUR} calculations have been performed with the new and fast CC module (\texttt{xncc})  written by one of author (DAM) which couples a general algebraic
+The present {\CFOUR} calculations have been performed with the new and fast CC module (\texttt{xncc})  written by one of authors (DAM) which couples a general algebraic
 and graphical interpretation of the non-orthogonal spin-adaptation approach with highly efficient storage format and implementation techniques designed to minimize data movement and to avoid costly tensor transposes.
@@
 The error bars associated with the extrapolation step of the CIPSI calculations (see Ref.~\onlinecite{qp2}) have been computed using our recently developed protocol presented in Ref.~\onlinecite{Veril_2021}.
+
+Because this is, to our knowledge, the first implementation of EOM-CC4, we have verified its accuracy by comparing the excitation energies obtained from solving for the right- and left-hand wave functions.
+Coupled cluster is a non-hermitian theory and thus the right- and left-hand eigenfunctions of the Jacobian are distinct, albeit with the same eigenvalue. 
+For the left-hand solution, we have reused the already-verified code for the ground-state $\Lambda$	Bequations which describe the amplitude relaxation contribution in the analytic gradient theory.
+\cite{Matthews_2021}
+The structure of the left-hand EOM-CC and $\Lambda$ equations are identical, and so simply interfacing this existing code with a Davidson solver \cite{Davidson_1975} provides left-hand EOM-CC solutions; this procedure has been checked for other known-good methods such as CCSDT and CC3.
 
@@
 	MSE			&					&0.031	&0.079	&0.014	&0.002	&0.000	&0.000	\\
+	\titou{Max}			&						\\
 	\end{tabular}
@@
 
+\titou{T2: add comment on double excitations.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 PFL has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481).
+DAM has received funding from the National Science Foundation (grant No.~OAC-2003931).
 This work was performed using HPC resources from CALMIP (Toulouse) under allocation 2021-18005 and of the CCIPL computational center installed in Nantes.

### 2021-05-04 Manuscript/CC4.tex
savin work doubles

@@
 We report the first investigation of the performance of EOM-CC4 --- an approximate equation-of-motion coupled-cluster model which includes iterative quadruple excitations --- for vertical excitation energies in molecular systems.
-By considering a set of 25 excited states in 8 small molecules for which we have computed CCSDTQP and FCI reference energies, we show that CC4 yields excitation energies with sub-kJ~mol$^{-1}$ accuracy, in very close agreement with its more expensive CCSDTQ parent.
+By considering a set of 28 excited states in 10 small molecules for which we have computed CCSDTQP and FCI reference energies, we show that, in the case of excited states with a dominant contribution from the single excitations, CC4 yields excitation energies with sub-kJ~mol$^{-1}$ accuracy, in very close agreement with its more expensive CCSDTQ parent.
+\titou{doubles?}
 Therefore, if one aims at high accuracy, CC4 stands as a highly competitive approximate method to model molecular excited states, with a significant improvement over both CC3 and CCSDT.
@@
 In this context, the main purpose of the present study is to assess the relative accuracy of the approximate iterative CC4 model against the more expensive CCSDTQ and CCSDTQP methods in the case of vertical excitation energies, as well as its absolute accuracy with respect to FCI.
-To do so, we consider a set of 8 small molecules (\ce{NH3}, \ce{BH}, \ce{BF}, \ce{CO}, \ce{N2}, \ce{HCl}, \ce{H2S}, and \ce{H2O}) and we compare the excitation energies associated with 25 singlet excited states of various natures ($\npis$, $\pipis$, Rydberg, valence, charge-transfer\ldots) and spatial symmetries obtained with various high-level CC methods.
+To do so, we consider a set of 10 small molecules (\ce{NH3}, \ce{C2}, \ce{BH}, \ce{BF}, \ce{CO}, \ce{N2}, \ce{HCl}, \ce{H2S}, \ce{HNO} and \ce{H2O}) and we compare the excitation energies associated with 28 singlet excited states of various natures ($\npis$, $\pipis$, Rydberg, valence, charge-transfer, and double excitations) and spatial symmetries obtained with various high-level CC methods.
 Although a small number of studies have been published on the performance of CC4 for ground-state energies and properties, \cite{Kallay_2005,Matthews_2021} this work stands, to the best of our knowledge, as the first to consider CC4 for the computation of excited-states energies.
-As we shall see below, CC4 is an excellent approximation to its CCSDTQ parent, and produces excitation energies with sub-\si{\kJ\per\mol} accuracy for this set of small molecules, well below the chemical accuracy threshold.
+As we shall see below, CC4 is an excellent approximation to its CCSDTQ parent, and produces, in the case of excited states with a dominant contribution from the single excitations, excitation energies with sub-\si{\kJ\per\mol} accuracy for this set of small molecules, well below the chemical accuracy threshold.
 
@@
 \begin{table*}
-	\caption{Vertical excitation energies (in eV) of a selection of molecular excited states obtained at various levels of theory with the aug-cc-pVDZ and aug-cc-pVTZ basis sets. 
-	For the aug-cc-pVDZ basis, the mean absolute error (MAE) and mean signed error (MSE) with respect to CCSDTQP is reported.
+	\caption{Vertical excitation energies (in eV) of a selection of singly-excited states obtained at various levels of theory with the aug-cc-pVDZ and aug-cc-pVTZ basis sets. 
+	$\%T_1$ is the percentage of single excitations involved in the transition (computed at the CC3/aug-cc-pVTZ level).
+	For the aug-cc-pVDZ basis, the mean absolute error (MAE), mean signed error (MSE), and maximum error (Max) with respect to CCSDTQP is reported.
 	\label{tab:BigTab}}
 	\begin{ruledtabular}
-	\begin{tabular}{llrrrrrrrrrrrrrrr}
+	\begin{tabular}{llrrrrrrrrrrrrrrrr}
 				&		&	\mc{8}{c}{aug-cc-pVDZ}		&		\mc{7}{c}{aug-cc-pVTZ}		\\	
-				\cline{3-10} \cline{11-17}
-	Mol.	&	State				&CC2	&CCSD	&CC3	&CCSDT	&CC4	&CCSDTQ	&CCSDTQP	&FCI	
+				\cline{4-11} \cline{12-18}
+	Mol.	&	State	& $\%T_1$	&CC2	&CCSD	&CC3	&CCSDT	&CC4	&CCSDTQ	&CCSDTQP	&FCI	
 									&CC2	&CCSD	&CC3	&CCSDT	&CC4	&CCSDTQ	&FCI			\\
 	\hline
-	\ce{NH3}	&	$^1A_2$ 		&6.249	&6.455	&6.464	&6.462	&6.479	&6.480	&6.482	&6.483(1)	&6.387	&6.600	&6.573	&6.571	&6.585	&6.586	&6.593(22)	\\	
-				&	$^1E$			&7.733	&8.024	&8.061	&8.057	&8.078	&8.079	&8.081	&8.082(1)	&7.847	&8.148	&8.146	&8.143	&8.161	&8.161	&8.171(20)	\\	
-				&	$^1A_1$ 		&9.400	&9.649	&9.664	&9.659	&9.677	&9.677	&9.680	&9.681(8)	&9.051	&9.334	&9.318	&9.314	&9.331	&9.331	&9.340(19)	\\
-				&	$^1A_2$ 		&10.148	&10.376	&10.396	&10.391	&10.409	&10.409	&10.411	&10.412(1)	&9.654	&9.953	&9.945	&9.939	&9.957	&9.957	&9.967(19)	\\
-	\ce{BH}		&	$^1\Pi$ 		&2.862	&2.970	&2.955	&2.946	&2.947	&2.947	&2.947	&2.947(0)	&2.831	&2.928	&2.910	&2.900	&2.901	&2.901	&2.901(0)	\\
-	\ce{BF}		&	$^1\Pi$ 		&6.509	&6.534	&6.478	&6.491	&6.484	&6.485	&6.485	&6.485(1)	&6.445	&6.464	&6.410	&6.423	&6.416	&6.417	&6.418(2)\\
-	\ce{CO}		&	$^1\Pi$ 		&8.724	&8.671	&8.572	&8.574	&8.562	&8.563	&8.561	&8.563(4)	&8.638	&8.587	&8.486	&8.492	&8.479	&8.480	&	\\
-				&	$^1\Sigma^-$ 	&10.381	&10.096	&10.122	&10.062	&10.055	&10.057	&10.057	&10.056(1)	&10.297	&9.986	&9.992	&9.940	&9.930	&9.932	&	\\
-				&	$^1\Delta$ 		&10.685	&10.210	&10.225	&10.178	&10.167	&10.169	&10.168	&10.168(1)	&10.604	&10.123	&10.119	&10.076	&10.064	&10.066	&	\\
-				&	$^1\Sigma^+$ 	&11.089	&11.171	&10.917	&10.944	&10.925	&10.926	&10.919	&			&11.106	&11.222	&10.943	&10.987	&10.961	&10.963	&	\\
-				&	$^1\Sigma^+$ 	&11.628	&11.710	&11.483	&11.518	&11.510	&11.510	&11.506	&			&11.626	&11.751	&11.489	&11.540	&11.521	&11.523	&	\\
-				&	$^1\Pi$ 		&11.878	&11.973	&11.737	&11.767	&11.757	&11.758	&11.753	&			&11.825	&11.960	&11.690	&11.737	&11.719	&11.720	&	\\
-	\ce{N2}		&	$^1\Pi_g$  		&9,528	&9.495	&9.442	&9.417	&9.409	&9.411	&9.409	&9.411(3)	&9.439	&9.408	&9.344	&9.326	&9.317	&9.319	&	\\
-				&	$^1\Sigma_u^-$	&10.428	&10.197	&10.059	&10.060	&10.063	&10.055	&10.054	&10.054(0)	&10.320	&9.996	&9.885	&9.890	&9.883	&9.878	&9.879(4)\\
-				&	$^1\Delta_u$ 	&10.961	&10.607	&10.433	&10.436	&10.439	&10.430	&10.428	&10.429(0)	&10.863	&10.443	&10.293	&10.302	&10.294	&10.287	&10.289(12)\\
-				&	$^1\Sigma_g^+$	&13.077	&13.326	&13.229	&13.202	&13.171	&13.182	&13.181	&13.180(1)	&12.833	&13.151	&13.013	&12.999	&12.962	&12.974	&	\\
-				&	$^1\Pi_u$  		&13.309	&13.451	&13.279	&13.174	&13.128	&13.131	&13.127	&			&13.152	&13.422	&13.223	&13.140	&13.091	&13,095	&	\\
-				&	$^1\Sigma_u^+$	&12.937	&13.250	&13.146	&13.130	&13.099	&13.109	&13.107	&			&12.888	&13.263	&13.120	&13.118	&13.078	&13.090	&	\\
-				&	$^1\Pi_u$ 		&14.091	&13.765	&13.635	&13.591	&13.551	&13.560	&13.558	&			&13.963	&13.674	&13.494	&13.455	&13.409	&13.419\\
-	\ce{HCl}	&	$^1\Pi$ 		&7.895	&7.862	&7.819	&7.815	&7.822	&7.822	&7.823	&7.823(0)	&7.959	&7.906	&7.840	&7.834	&7.837	&7.837	&7.838(1)\\
-	\ce{H2S}	&	$^1B_1$  		&6.157	&6.141	&6.098	&6.098	&6.102	&6.103	&6.103	&6.103(1)	&6.304	&6.294	&6.240	&6.237	&6.238	&6.238	&6.240(7)\\
-				&	$^1A_2$  		&6.431	&6.343	&6.293	&6.286	&6.286	&6.286	&6.286	&6.286(0)	&6.345	&6.246	&6.192	&6.185	&6.181	&6.181	&6.181(6) \\
-	\ce{H2O}	&	$^1B_1$  		&7.089	&7.447	&7.511	&7.497	&7.531	&7.528	&7.532	&7.533(0)	&7.234	&7.597	&7.605	&7.591	&7.623	&7.620	&7.626(3)\\
-				&	$^1A_2$  		&8.743	&9.213	&9.293	&9.279	&9.317	&9.313	&9.318	&9.318(0)	&8.889	&9.361	&9.382	&9.368	&9.405	&9.400	&9.407(7)\\
-				&	$^1A_1$  		&9.486	&9.861	&9.921	&9.903	&9.940	&9.937	&9.941	&9.941(0)	&9.580	&9.957	&9.966	&9.949	&9.986	&9.981	&9.986(2)\\
+	\ce{NH3}	&	$^1A_2$ 		&93	&6.249	&6.455	&6.464	&6.462	&6.479	&6.480	&6.482	&6.483(1)	&6.387	&6.600	&6.573	&6.571	&6.585	&6.586	&6.593(22)	\\	
+				&	$^1E$			&93	&7.733	&8.024	&8.061	&8.057	&8.078	&8.079	&8.081	&8.082(1)	&7.847	&8.148	&8.146	&8.143	&8.161	&8.161	&8.171(20)	\\	
+				&	$^1A_1$ 		&94	&9.400	&9.649	&9.664	&9.659	&9.677	&9.677	&9.680	&9.681(8)	&9.051	&9.334	&9.318	&9.314	&9.331	&9.331	&9.340(19)	\\
+				&	$^1A_2$ 		&93	&10.148	&10.376	&10.396	&10.391	&10.409	&10.409	&10.411	&10.412(1)	&9.654	&9.953	&9.945	&9.939	&9.957	&9.957	&9.967(19)	\\
+	\ce{BH}		&	$^1\Pi$ 		&95	&2.862	&2.970	&2.955	&2.946	&2.947	&2.947	&2.947	&2.947(0)	&2.831	&2.928	&2.910	&2.900	&2.901	&2.901	&2.901(0)	\\
+	\ce{BF}		&	$^1\Pi$ 		&94	&6.509	&6.534	&6.478	&6.491	&6.484	&6.485	&6.485	&6.485(1)	&6.445	&6.464	&6.410	&6.423	&6.416	&6.417	&6.418(2)\\
+	\ce{CO}		&	$^1\Pi$ 		&93	&8.724	&8.671	&8.572	&8.574	&8.562	&8.563	&8.561	&8.563(4)	&8.638	&8.587	&8.486	&8.492	&8.479	&8.480	&	\\
+				&	$^1\Sigma^-$ 	&93	&10.381	&10.096	&10.122	&10.062	&10.055	&10.057	&10.057	&10.056(1)	&10.297	&9.986	&9.992	&9.940	&9.930	&9.932	&	\\
+				&	$^1\Delta$ 		&91	&10.685	&10.210	&10.225	&10.178	&10.167	&10.169	&10.168	&10.168(1)	&10.604	&10.123	&10.119	&10.076	&10.064	&10.066	&	\\
+				&	$^1\Sigma^+$ 	&91	&11.089	&11.171	&10.917	&10.944	&10.925	&10.926	&10.919	&			&11.106	&11.222	&10.943	&10.987	&10.961	&10.963	&	\\
+				&	$^1\Sigma^+$ 	&92	&11.628	&11.710	&11.483	&11.518	&11.510	&11.510	&11.506	&			&11.626	&11.751	&11.489	&11.540	&11.521	&11.523	&	\\
+				&	$^1\Pi$ 		&92	&11.878	&11.973	&11.737	&11.767	&11.757	&11.758	&11.753	&			&11.825	&11.960	&11.690	&11.737	&11.719	&11.720	&	\\
+	\ce{N2}		&	$^1\Pi_g$  		&92	&9,528	&9.495	&9.442	&9.417	&9.409	&9.411	&9.409	&9.411(3)	&9.439	&9.408	&9.344	&9.326	&9.317	&9.319	&	\\
+				&	$^1\Sigma_u^-$	&97	&10.428	&10.197	&10.059	&10.060	&10.063	&10.055	&10.054	&10.054(0)	&10.320	&9.996	&9.885	&9.890	&9.883	&9.878	&9.879(4)\\
+				&	$^1\Delta_u$ 	&95	&10.961	&10.607	&10.433	&10.436	&10.439	&10.430	&10.428	&10.429(0)	&10.863	&10.443	&10.293	&10.302	&10.294	&10.287	&10.289(12)\\
+				&	$^1\Sigma_g^+$	&92	&13.077	&13.326	&13.229	&13.202	&13.171	&13.182	&13.181	&13.180(1)	&12.833	&13.151	&13.013	&12.999	&12.962	&12.974	&	\\
+				&	$^1\Pi_u$  		&82	&13.309	&13.451	&13.279	&13.174	&13.128	&13.131	&13.127	&			&13.152	&13.422	&13.223	&13.140	&13.091	&13,095	&	\\
+				&	$^1\Sigma_u^+$	&92	&12.937	&13.250	&13.146	&13.130	&13.099	&13.109	&13.107	&			&12.888	&13.263	&13.120	&13.118	&13.078	&13.090	&	\\
+				&	$^1\Pi_u$ 		&87	&14.091	&13.765	&13.635	&13.591	&13.551	&13.560	&13.558	&			&13.963	&13.674	&13.494	&13.455	&13.409	&13.419\\
+	\ce{HCl}	&	$^1\Pi$ 		&94	&7.895	&7.862	&7.819	&7.815	&7.822	&7.822	&7.823	&7.823(0)	&7.959	&7.906	&7.840	&7.834	&7.837	&7.837	&7.838(1)\\
+	\ce{H2S}	&	$^1B_1$  		&94	&6.157	&6.141	&6.098	&6.098	&6.102	&6.103	&6.103	&6.103(1)	&6.304	&6.294	&6.240	&6.237	&6.238	&6.238	&6.240(7)\\
+				&	$^1A_2$  		&94	&6.431	&6.343	&6.293	&6.286	&6.286	&6.286	&6.286	&6.286(0)	&6.345	&6.246	&6.192	&6.185	&6.181	&6.181	&6.181(6) \\
+	\ce{H2O}	&	$^1B_1$  		&93	&7.089	&7.447	&7.511	&7.497	&7.531	&7.528	&7.532	&7.533(0)	&7.234	&7.597	&7.605	&7.591	&7.623	&7.620	&7.626(3)\\
+				&	$^1A_2$  		&93	&8.743	&9.213	&9.293	&9.279	&9.317	&9.313	&9.318	&9.318(0)	&8.889	&9.361	&9.382	&9.368	&9.405	&9.400	&9.407(7)\\
+				&	$^1A_1$  		&93	&9.486	&9.861	&9.921	&9.903	&9.940	&9.937	&9.941	&9.941(0)	&9.580	&9.957	&9.966	&9.949	&9.986	&9.981	&9.986(2)\\
 	\hline
-	MAE			&					&0.257	&0.112	&0.028	&0.018	&0.003	&0.002	\\
-	MSE			&					&0.031	&0.079	&0.014	&0.002	&0.000	&0.000	\\
-	\titou{Max}			&						\\
+	MAE			&					&	&0.257	&0.109	&0.028	&0.018	&0.003	&0.002	\\
+	MSE			&					&	&0.020	&0.075	&0.013	&0.000	&0.000	&0.000	\\
+	Max			&					&	&0.575	&0.324	&0.152	&0.047	&0.011	&0.007	\\
 	\end{tabular}
@@
 
-Table \ref{tab:BigTab} gathers, for the two considered basis sets, the 25 vertical excitation energies computed for our set of 8 molecules with various CC models as well as the FCI estimates computed with CIPSI.
+Table \ref{tab:BigTab} gathers, for the two considered basis sets, 25 vertical excitation energies with a dominant contribution for the single excitations computed for a set of 8 molecules with various CC models as well as the FCI estimates computed with CIPSI.
 First, we underline that the FCI estimates show how accurate the CCSDTQP reference data are, with a maximum deviation of \SI{0.002}{\eV} when one considers the aug-cc-pVDZ basis. 
@@
 the aug-cc-pVDZ (aug-cc-pVTZ) basis set. 
-Therefore, including quadruples allows to reach sub-\si{\kJ\per\mol} accuracy (\ie, average error below \SI{0.01}{\eV}) with only a rather minor improvement going from CC4 to CCSDTQ.
+Therefore, including quadruples allows to reach sub-\si{\kJ\per\mol} accuracy (\ie, average error below \SI{0.01}{\eV}) for singly-excited states with only a rather minor improvement going from CC4 to CCSDTQ.
 
-\titou{T2: add comment on double excitations.}
+Table \ref{tab:doubles} reports vertical excitation energies for double excitations (\ie, transition with a dominant contribution from the doubly-excited determinants) in the carbon dimer, \ce{C2}, and nitroxyl, \ce{HNO}, computed with the aug-cc-pVDZ basis.
+These transitions can be labeled as ``pure'' double excitations as they involve an insignificant amount of single excitations.
+In this case, the differences between methods is magnified.
+
+%%% TABLE II %%%
+\begin{squeezetable}
+\begin{table}
+	\caption{Vertical excitation energies (in eV) of a selection of doubly-excited states obtained at various levels of theory with the aug-cc-pVDZ basis set. 
+	$\%T_1$ is the percentage of single excitations involved in the transition (computed at the CC3/aug-cc-pVTZ level).
+	\label{tab:doubles}}
+	\begin{ruledtabular}
+	\begin{tabular}{llrrrrrrr}
+	Mol.		&	State			& $\%T_1$	&CC3	&CCSDT	&CC4	&CCSDTQ	&CCSDTQP	&FCI	\\
+	\hline
+	\ce{C2}		&	$^1\Delta_g$ 	&	1		&3.107	&2.632	&2.341	&2.241	&2.214	&2.21(0)	\\	
+				&	$^1\Sigma_g^+$ 	&	1		&3.283	&2.874	&2.602	&2.521	&2.505	&2.50(0)	\\	
+	\ce{HNO}	&	$^1A'$ 			&	0		&5.247	&4.756	&4.454	&4.424	&		&4.40(1)	\\
+	\end{tabular}
+	\end{ruledtabular}
+\end{table}
+\end{squeezetable}
+%%% %%% %%% %%%
 

### 2021-05-05 Manuscript/CC4.tex
double excitations

@@
 
-\newcommand{\alert}[1]{\textcolor{black}{#1}}
+\newcommand{\alert}[1]{\textcolor{red}{#1}}
 \usepackage[normalem]{ulem}
@@
 By considering a set of 28 excited states in 10 small molecules for which we have computed CCSDTQP and FCI reference energies, we show that, in the case of excited states with a dominant contribution from the single excitations, CC4 yields excitation energies with sub-kJ~mol$^{-1}$ accuracy, in very close agreement with its more expensive CCSDTQ parent.
-\titou{doubles?}
 Therefore, if one aims at high accuracy, CC4 stands as a highly competitive approximate method to model molecular excited states, with a significant improvement over both CC3 and CCSDT.
+In present results also evidence that, although the same qualitative conclusions still hold, one cannot reach the same type of accuracy for transitions with a strong double excitation character.
 \end{abstract}
@@
 	For the aug-cc-pVDZ basis, the mean absolute error (MAE), mean signed error (MSE), and maximum error (Max) with respect to CCSDTQP is reported.
-	\label{tab:BigTab}}
+	\label{tab:singles}}
 	\begin{ruledtabular}
@@
 %%% FIG 1 %%%
-\begin{figure}
-	\includegraphics[width=\linewidth]{histograms_MAE_AVDZ}
+\begin{figure*}
+	\includegraphics[width=0.7\linewidth]{histograms_MAE_AVDZ}
 	\caption{
-	Distribution of the error (in eV) in excitation energies (with respect to the CCSDTQP values) for CC2, CC3, and CC4 (top) and CCSD, CCSDT, and CCSDTQ (bottom) obtained with the aug-cc-pVDZ basis.
-	See Table \ref{tab:BigTab} for the raw data.
+	Distribution of the error (in eV) in excitation energies (with respect to CCSDTQP) for CC2, CC3, and CC4 (top) and CCSD, CCSDT, and CCSDTQ (bottom) obtained with the aug-cc-pVDZ basis.
+	See Table \ref{tab:singles} for the raw data.
 	\label{fig:error}}
-\end{figure}
+\end{figure*}
 %%% %%% %%% %%%
 
-Table \ref{tab:BigTab} gathers, for the two considered basis sets, 25 vertical excitation energies with a dominant contribution for the single excitations computed for a set of 8 molecules with various CC models as well as the FCI estimates computed with CIPSI.
+Table \ref{tab:singles} gathers, for the two considered basis sets, 25 vertical excitation energies with a dominant contribution for the single excitations computed for a set of 8 molecules with various CC models as well as the FCI estimates computed with CIPSI.
 First, we underline that the FCI estimates show how accurate the CCSDTQP reference data are, with a maximum deviation of \SI{0.002}{\eV} when one considers the aug-cc-pVDZ basis. 
@@
 
-The mean absolute errors (MAEs) and mean signed errors (MSEs) with respect to CCSDTQP (and computed in the aug-cc-pVDZ basis) are reported in the bottom of Table \ref{tab:BigTab} for the CC2-to-CCSDTQ models.
+The mean absolute errors (MAEs) and mean signed errors (MSEs) with respect to CCSDTQP (and computed in the aug-cc-pVDZ basis) are reported in the bottom of Table \ref{tab:singles} for the CC2-to-CCSDTQ models.
 The distribution of the errors are reported in Fig.~\ref{fig:error} for each level of theory.
@@
 Therefore, including quadruples allows to reach sub-\si{\kJ\per\mol} accuracy (\ie, average error below \SI{0.01}{\eV}) for singly-excited states with only a rather minor improvement going from CC4 to CCSDTQ.
-
-Table \ref{tab:doubles} reports vertical excitation energies for double excitations (\ie, transition with a dominant contribution from the doubly-excited determinants) in the carbon dimer, \ce{C2}, and nitroxyl, \ce{HNO}, computed with the aug-cc-pVDZ basis.
-These transitions can be labeled as ``pure'' double excitations as they involve an insignificant amount of single excitations.
-In this case, the differences between methods is magnified.
 
@@
 	\hline
-	\ce{C2}		&	$^1\Delta_g$ 	&	1		&3.107	&2.632	&2.341	&2.241	&2.214	&2.21(0)	\\	
-				&	$^1\Sigma_g^+$ 	&	1		&3.283	&2.874	&2.602	&2.521	&2.505	&2.50(0)	\\	
-	\ce{HNO}	&	$^1A'$ 			&	0		&5.247	&4.756	&4.454	&4.424	&		&4.40(1)	\\
+	\ce{C2}		&	$^1\Delta_g$ 	&	1		&3.107	&2.632	&2.341	&2.241	&2.214	&2.213(0)	\\	
+				&	$^1\Sigma_g^+$ 	&	1		&3.283	&2.874	&2.602	&2.521	&\titou{2.505}	&2.503(1)	\\	
+	\ce{HNO}	&	$^1A'$ 			&	0		&5.247	&4.756	&4.454	&4.424	&\titou{4.XXX}	&\titou{4.40(1)}	\\
 	\end{tabular}
@@
 
+%%% FIG 2 %%%
+\begin{figure*}
+	\includegraphics[width=0.7\linewidth]{doubles}
+	\caption{
+	Error in excitation energies (with respect to CCSDTQP) of CC3, CCSDT, CC4, and CCSDTQ obtained with the aug-cc-pVDZ basis
+	for the double excitations gathered in Table \ref{tab:doubles}.
+	\label{fig:doubles}}
+\end{figure*}
+%%% %%% %%% %%%
+
+A closer inspection at Table \ref{tab:singles} shows that the largest deviations appear for the transitions with the smallest $\%T_1$ values (where $\%T_1$ is the percentage of single excitations involved in the transition which is computed at the CC3/aug-cc-pVTZ level in the present case).
+This is particularly noticeable for the two $^1\Pi_u$ transitions of \ce{N2}.
+This suggests that the performance of the various CC models discussed above might be highly dependent on the nature of the transitions, as discussed in Ref.~\onlinecite{Loos_2019}.
+To investigate further this point, we report in Table \ref{tab:doubles} vertical excitation energies for double excitations (\ie, transition with a dominant contribution from the doubly-excited determinants) in the carbon dimer, \ce{C2}, and nitroxyl, \ce{HNO}, computed with the aug-cc-pVDZ basis for the methods including at least triple excitations.
+(The second-order methods, CC2 and CCSD, are unable to faithfully locate double excitations.)
+These transitions can be labeled as ``pure'' double excitations as they involve an insignificant amount of single excitations ($\%T_1 \approx 0$), hence providing a very stringent test for the EOM-CC formalism.
+In this case, as shown in Fig.~\ref{fig:doubles}, the differences between methods are magnified, but the conclusions drawn in the previous paragraph hold: CC4 is an excellent approximation to CCSDTQ (with a maximum deviation of \SI{0.1}{\eV} in the $^1\Delta_g$ transition of \ce{C2}) and a massive improvement over CC3 (where the error can be as large as \SI{0.9}{\eV}) and, to a lesser extent, over CCSDT.
+However, for these transitions with a dominant double excitation character, CC4 does not permit to reach chemical accuracy with errors of the order of \SI{0.1}{\eV} compared to CCSDTQP and FCI.
+The outcome might differ for transitions of mixed characters ($\%T_1 \approx 70$) such as the well-known $^1 A_g$ excited state of butadiene.\cite{Maitra_2004,Saha_2006,Watson_2012,Shu_2017,Barca_2018a,Loos_2019}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-For this set of small molecules at least, CC4 is a rather competitive approximation to its more expensive CCSDTQ parent as well as a very significant improvement over its third-order version, CC3, and the ``complete'' CCSDT method.
+Thanks to the results gathered in the present study, we can conclude, for this set of small molecules at least, that CC4 is a rather competitive approximation to its more expensive CCSDTQ parent as well as a very significant improvement over its third-order version, CC3, and the ``complete'' CCSDT method.
+This is particularly true in the case of single excitations (Table \ref{tab:singles}) when one reaches sub-kJ~mol$^{-1}$ accuracy.
+For double excitations, we have seen (Table \ref{tab:doubles}) that the same qualitative conclusions hold but one cannot reach chemical accuracy for the set of ``pure'' double excitations that we have considered.
+
 These findings are promising, though we are well aware that the conclusions obtained for small and larger molecules might differ significantly.

### 2021-05-05 Manuscript/CC4.tex
v2 OK

@@
 Therefore, if one aims at high accuracy, CC4 stands as a highly competitive approximate method to model molecular excited states, with a significant improvement over both CC3 and CCSDT.
-In present results also evidence that, although the same qualitative conclusions still hold, one cannot reach the same type of accuracy for transitions with a strong double excitation character.
+Our results also evidence that, although the same qualitative conclusions hold, one cannot reach the same level of accuracy for transitions of double excitation nature.
 \end{abstract}
@@
 \cite{Loos_2018a,Loos_2019,Loos_2020a,Loos_2020b,Loos_2020c,Veril_2021}
-The main purpose of this so-called QUEST database is to provide reference excitation energies in order to perform fair and reliable benchmarks between electronic structure methods and assess their strengths and weakness in a large panel of chemical scenarios.
+The main purpose of this so-called QUEST database is to provide reference excitation energies in order to perform fair and reliable benchmarks between electronic structure methods and assess their strengths and weakness for a large panel of chemical scenarios.
 Most of these reference transition energies, which rely exclusively on high-level \textit{ab initio} calculations, can be reasonably considered as chemically accurate, \ie, within \SI{1}{\kcal\per\mol} or \SI{0.043}{\eV} of the FCI limit.
@@
 
-In this context, the main purpose of the present study is to assess the relative accuracy of the approximate iterative CC4 model against the more expensive CCSDTQ and CCSDTQP methods in the case of vertical excitation energies, as well as its absolute accuracy with respect to FCI.
+In this context, the main purpose of the present study is to assess the relative accuracy of the approximate iterative CC4 model against the more expensive CCSDTQ and CCSDTQP methods in the case of vertical excitation energies, as well as their absolute accuracy with respect to FCI.
 To do so, we consider a set of 10 small molecules (\ce{NH3}, \ce{C2}, \ce{BH}, \ce{BF}, \ce{CO}, \ce{N2}, \ce{HCl}, \ce{H2S}, \ce{HNO} and \ce{H2O}) and we compare the excitation energies associated with 28 singlet excited states of various natures ($\npis$, $\pipis$, Rydberg, valence, charge-transfer, and double excitations) and spatial symmetries obtained with various high-level CC methods.
@@
 Coupled cluster is a non-hermitian theory and thus the right- and left-hand eigenfunctions of the Jacobian are distinct, albeit with the same eigenvalue. 
-For the left-hand solution, we have reused the already-verified code for the ground-state $\Lambda$	Bequations which describe the amplitude relaxation contribution in the analytic gradient theory.
+For the left-hand solution, we have reused the already-verified code for the ground-state $\Lambda$	equations which describe the amplitude relaxation contribution in the analytic gradient theory.
 \cite{Matthews_2021}
@@
 	\caption{Vertical excitation energies (in eV) of a selection of singly-excited states obtained at various levels of theory with the aug-cc-pVDZ and aug-cc-pVTZ basis sets. 
-	$\%T_1$ is the percentage of single excitations involved in the transition (computed at the CC3/aug-cc-pVTZ level).
+	$\%T_1$ is the percentage of single excitations involved in the transition computed at the CC3/aug-cc-pVTZ level.
 	For the aug-cc-pVDZ basis, the mean absolute error (MAE), mean signed error (MSE), and maximum error (Max) with respect to CCSDTQP is reported.
@@
 \begin{figure*}
-	\includegraphics[width=0.7\linewidth]{histograms_MAE_AVDZ}
+	\includegraphics[width=0.7\linewidth]{fig1}
 	\caption{
 	Distribution of the error (in eV) in excitation energies (with respect to CCSDTQP) for CC2, CC3, and CC4 (top) and CCSD, CCSDT, and CCSDTQ (bottom) obtained with the aug-cc-pVDZ basis.
+	Note the various error ranges ($X$ axis) for the various methods.
 	See Table \ref{tab:singles} for the raw data.
@@
 
-Table \ref{tab:singles} gathers, for the two considered basis sets, 25 vertical excitation energies with a dominant contribution for the single excitations computed for a set of 8 molecules with various CC models as well as the FCI estimates computed with CIPSI.
+Table \ref{tab:singles} gathers, for the two considered basis sets, 25 vertical excitation energies with a (strongly) dominant contribution from the single excitations computed for a set of 8 molecules with various CC models as well as the FCI estimates computed with CIPSI.
 First, we underline that the FCI estimates show how accurate the CCSDTQP reference data are, with a maximum deviation of \SI{0.002}{\eV} when one considers the aug-cc-pVDZ basis. 
@@
 
-The mean absolute errors (MAEs) and mean signed errors (MSEs) with respect to CCSDTQP (and computed in the aug-cc-pVDZ basis) are reported in the bottom of Table \ref{tab:singles} for the CC2-to-CCSDTQ models.
+The mean absolute errors (MAEs) and mean signed errors (MSEs) with respect to CCSDTQP  computed in the aug-cc-pVDZ basis are reported in the bottom of Table \ref{tab:singles} for the CC2-to-CCSDTQ models.
 The distribution of the errors are reported in Fig.~\ref{fig:error} for each level of theory.
@@
 We note that the errors decrease by roughly one order of magnitude when switching from CCSD to CC3 and from CCSDT to CC4, whilst improvements of approximately 50\% ``only'' are noted when going from the ``approximate'' model to the ``complete'' method (\ie, from CC2 to CCSD, from CC3 to CCSDT, and from CC4 to CCSDTQ).
-In other words, CC4 brings significant improvement in terms of MAE and MSE as compared to the third-order methods, CC3 and CCSDT, which demonstrates the importance of quadruple excitations when one aims at high accuracy.
+In other words, CC4 brings significant improvements in terms of MAE and MSE as compared to the third-order methods, CC3 and CCSDT, which demonstrates the importance of quadruple excitations when one aims at very high accuracy.
 Besides, for the two basis sets, there is an outstanding similarity between the CC4 and CCSDTQ excitation energies with mean absolute and signed deviations below (equal to) \SI{0.001}{\eV} and a maximum deviation of \SI{0.011}{\eV} (\SI{0.007}{\eV}) between to the two sets of data obtained with
 the aug-cc-pVDZ (aug-cc-pVTZ) basis set. 
-Therefore, including quadruples allows to reach sub-\si{\kJ\per\mol} accuracy (\ie, average error below \SI{0.01}{\eV}) for singly-excited states with only a rather minor improvement going from CC4 to CCSDTQ.
+Therefore, including quadruples allows to reach sub-\si{\kJ\per\mol} accuracy (\ie, average error below \SI{0.01}{\eV}) for singly-excited states with only a rather minor improvement in going from CC4 to CCSDTQ.
 
@@
 	\ce{C2}		&	$^1\Delta_g$ 	&	1		&3.107	&2.632	&2.341	&2.241	&2.214	&2.213(0)	\\	
-				&	$^1\Sigma_g^+$ 	&	1		&3.283	&2.874	&2.602	&2.521	&\titou{2.505}	&2.503(1)	\\	
-	\ce{HNO}	&	$^1A'$ 			&	0		&5.247	&4.756	&4.454	&4.424	&\titou{4.XXX}	&\titou{4.40(1)}	\\
+				&	$^1\Sigma_g^+$ &	1		&3.283	&2.874	&2.602	&2.521	&2.505	&2.503(1)	\\	
+	\ce{HNO}	&	$^1A'$ 			&	0		&5.247	&4.756	&4.454	&4.424	&		&\titou{4.397(2)}	\\
 	\end{tabular}
@@
 \begin{figure*}
-	\includegraphics[width=0.7\linewidth]{doubles}
+	\includegraphics[width=0.7\linewidth]{fig2}
 	\caption{
-	Error in excitation energies (with respect to CCSDTQP) of CC3, CCSDT, CC4, and CCSDTQ obtained with the aug-cc-pVDZ basis
+	Error in excitation energies (with respect to FCI) computed with CC3, CCSDT, CC4, and CCSDTQ in the aug-cc-pVDZ basis
 	for the double excitations gathered in Table \ref{tab:doubles}.
@@
 This suggests that the performance of the various CC models discussed above might be highly dependent on the nature of the transitions, as discussed in Ref.~\onlinecite{Loos_2019}.
-To investigate further this point, we report in Table \ref{tab:doubles} vertical excitation energies for double excitations (\ie, transition with a dominant contribution from the doubly-excited determinants) in the carbon dimer, \ce{C2}, and nitroxyl, \ce{HNO}, computed with the aug-cc-pVDZ basis for the methods including at least triple excitations.
-(The second-order methods, CC2 and CCSD, are unable to faithfully locate double excitations.)
+To investigate further this point, we report in Table \ref{tab:doubles} vertical excitation energies for double excitations (\ie, transition with a dominant contribution from the doubly-excited determinants) in the carbon dimer, \ce{C2}, and nitroxyl, \ce{HNO}, computed with the aug-cc-pVDZ basis for the methods including at least triple excitations; the second-order methods, CC2 and CCSD, being unable to faithfully locate double excitations.
 These transitions can be labeled as ``pure'' double excitations as they involve an insignificant amount of single excitations ($\%T_1 \approx 0$), hence providing a very stringent test for the EOM-CC formalism.
-In this case, as shown in Fig.~\ref{fig:doubles}, the differences between methods are magnified, but the conclusions drawn in the previous paragraph hold: CC4 is an excellent approximation to CCSDTQ (with a maximum deviation of \SI{0.1}{\eV} in the $^1\Delta_g$ transition of \ce{C2}) and a massive improvement over CC3 (where the error can be as large as \SI{0.9}{\eV}) and, to a lesser extent, over CCSDT.
+In this case, as shown in Fig.~\ref{fig:doubles}, the differences between methods are magnified, but the conclusions drawn in the previous paragraph hold: CC4 is an excellent approximation to CCSDTQ (with a maximum deviation of \SI{0.1}{\eV} for the $^1\Delta_g$ transition of \ce{C2}) and a massive improvement over CC3 (where the error can be as large as \SI{0.9}{\eV}) and, to a lesser extent, over CCSDT.
 However, for these transitions with a dominant double excitation character, CC4 does not permit to reach chemical accuracy with errors of the order of \SI{0.1}{\eV} compared to CCSDTQP and FCI.
@@
 
-Thanks to the results gathered in the present study, we can conclude, for this set of small molecules at least, that CC4 is a rather competitive approximation to its more expensive CCSDTQ parent as well as a very significant improvement over its third-order version, CC3, and the ``complete'' CCSDT method.
+Thanks to the results gathered in the present study, we can conclude, for this set of small molecules at least, that CC4 is a rather competitive approximation to its more expensive CCSDTQ parent as well as a very significant improvement over both its third-order version, CC3, and the ``complete'' CCSDT method.
 This is particularly true in the case of single excitations (Table \ref{tab:singles}) when one reaches sub-kJ~mol$^{-1}$ accuracy.
@@
 Therefore, although further investigations on larger compounds are definitely required, the present results are very encouraging as CC4, with its $\order*{N^9}$ scaling, can be applied to significantly larger molecules than CCSDTQ [which scales as $\order*{N^{10}}$].
-This will likely allow us to revisit, in the future, some of the theoretical best estimates defined in the context of the QUEST database.\cite{Loos_2020a,Veril_2021}
+This will likely allow us to revisit, in the future, some of the theoretical best estimates defined in the QUEST database.\cite{Loos_2020a,Veril_2021}
 

### 2021-05-05 Manuscript/CC4.tex
cover letter

@@
 A somewhat similar strategy has been applied to define the CCSDT-3 \cite{Urban_1985,Noga_1987b} and CCSDTQ-3 \cite{Kallay_2005} models based on arguments stemming from perturbation theory.
-Of course, a plethora of other approximate CC models have been developed over the years and we refer the interested reader to specialized reviews for more details.
+Of course, a large number of other approximate CC models have been developed over the years and we refer the interested reader to specialized reviews for more details.
 \cite{Crawford_2000,Piecuch_2002,Bartlett_2007,Shavitt_2009}

### 2021-05-05 Manuscript/Cover_Letter/CoverLetter.tex
cover letter

\documentclass[10pt]{letter}
\usepackage{UPS_letterhead,xcolor,mhchem,mathpazo,ragged2e}
\newcommand{\alert}[1]{\textcolor{red}{#1}}
\definecolor{darkgreen}{HTML}{009900}

\begin{document}

\begin{letter}%
{To the Editors of the Journal of Chemical Physics}

\opening{Dear Editors,}

\justifying
Please find enclosed our manuscript entitled \textit{``How accurate are EOM-CC4 vertical excitation energies?''}, which we would like you to consider as a \textit{Communication} in the \textit{Journal of Chemical Physics}.

In this communication, we report what we believe is the very first investigation of the performance of EOM-CC4, an approximate equation-of-motion coupled-cluster model which includes iterative quadruple excitations, for vertical excitation energies in molecular systems.
For a set of 28 excited states in 10 small molecules, CC4 is compared to other coupled-cluster models up EOM-CCSDTQP as well as FCI.
The present results nicely illustrate the systematic improvement of the transition energies when one ramps up the computational effort following the series CC2, CCSD, CC3, CCSDT, CC4, and CCSDTQ.
Our main conclusions are that CC4 is a rather competitive approximation to its more expensive CCSDTQ parent as well as a very significant improvement over both its third-order version, CC3, and the ``complete'' CCSDT method.
This is particularly true in the case of single excitations when one reaches sub-kJ~mol$^{-1}$ accuracy at the CC4 level.
Our results also evidence that, although the same qualitative conclusions hold, one cannot reach the same level of accuracy for transitions of double excitation nature.

Due to the usefulness of benchmark sets and their corresponding reference data for the electronic structure community, we expect this work to be of interest to a wide audience within the chemistry and physics communities.
We suggest Jurgen Gauss, John Stanton, So Hirata, Marcel Nooijen, Henrik Koch, and Don Truhlar as potential referees.	
We look forward to hearing from you soon.

\closing{Sincerely, the authors.}

\end{letter}
\end{document}

### 2021-05-05 Manuscript/CC4.tex
v3 OK
CC data
last value
arXiv version

@@
 In other words, CC4 brings significant improvements in terms of MAE and MSE as compared to the third-order methods, CC3 and CCSDT, which demonstrates the importance of quadruple excitations when one aims at very high accuracy.
-Besides, for the two basis sets, there is an outstanding similarity between the CC4 and CCSDTQ excitation energies with mean absolute and signed deviations below (equal to) \SI{0.001}{\eV} and a maximum deviation of \SI{0.011}{\eV} (\SI{0.007}{\eV}) between to the two sets of data obtained with
-the aug-cc-pVDZ (aug-cc-pVTZ) basis set. 
+Besides, for the two basis sets, there is an outstanding similarity between the CC4 and CCSDTQ excitation energies with mean absolute and signed deviations below (equal to) \SI{0.001}{\eV} and a maximum deviation of \SI{0.011}{\eV} (\SI{0.007}{\eV}) between to the two sets of data obtained with the aug-cc-pVDZ (aug-cc-pVTZ) basis set.
 Therefore, including quadruples allows to reach sub-\si{\kJ\per\mol} accuracy (\ie, average error below \SI{0.01}{\eV}) for singly-excited states with only a rather minor improvement in going from CC4 to CCSDTQ.
@@
 				&	$^1\Sigma_g^+$ &	1		&3.283	&2.874	&2.602	&2.521	&2.505	&2.503(1)	\\	
-	\ce{HNO}	&	$^1A'$ 			&	0		&5.247	&4.756	&4.454	&4.424	&		&\titou{4.397(2)}	\\
+	\ce{HNO}	&	$^1A'$ 			&	0		&5.247	&4.756	&4.454	&4.424	&		&4.399(2)	\\
 	\end{tabular}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The data that support the findings of this study are openly available in Zenodo at \href{http://doi.org/XX.XXXX/zenodo.XXXXXXX}{http://doi.org/XX.XXXX/zenodo.XXXXXXX}.
+The data that support the findings of this study are openly available in Zenodo at \href{http://doi.org/10.5281/zenodo.4739288}{http://doi.org/10.5281/zenodo.4739288}.
 

### 2021-05-24 Manuscript/Response_Letter/Response_Letter.tex
response letter

\documentclass[10pt]{letter}
\usepackage{UPS_letterhead,xcolor,mhchem,mathpazo,ragged2e,hyperref}
\newcommand{\alert}[1]{\textcolor{red}{#1}}
\definecolor{darkgreen}{HTML}{009900}

\begin{document}

\begin{letter}%
{To the Editors of the Journal of Chemical Physics}

\opening{Dear Editors,}

\justifying
Please find attached a revised version of our \textit{Communication} entitled 
\begin{quote}
\textit{``How accurate are EOM-CC4 vertical excitation energies?''}.
\end{quote}
We thank the reviewers for their constructive comments.
Our detailed responses to their comments can be found below.
For convenience, changes are highlighted in red in the revised version of the manuscript.

We look forward to hearing from you.

\closing{Sincerely, the authors.}

%%% REVIEWER 1 %%%
\noindent \textbf{\large Authors' answer to Reviewer \#1}

\begin{itemize}

	\item 
	{In this short manuscript, the CC4 method is applied to excitation energies at the first time. 
	The manuscript is well-written, and the good performance of the CC4 approach for excitation energies is an important piece of information for computational chemists who are interested in calculating benchmark-quality excitation energies. 
	Nevertheless, the paper would probably benefit from the extension of the study. 
	E.g., the performance of the CCn methods is relatively weak for potential energy surfaces or geometries. 
	It would be instructive to see how CC4 performs for excited states.}
	\\
	\alert{We thank the reviewer for his/her positive comments.
	The present \textit{Communication} deals specifically with vertical transition energies.
	Although extension to excited-state potential energy surfaces would definitely deliver some interesting new insights on the performance of CC4, we believe that it is outside the scope of the present study.
	However, we hope to answer these important questions in a future manuscript.}

	\item 
	{In the abstract and conclusions, the approximate error of the approach should be given in eV instead of kJ/mol as excitation energies are usually presented in eV.}
	\\
	\alert{We have added the corresponding value in eV.}

	\item 
	{The terms ``singly/doubly-excited states'' or ``single/double excitations'' are misleading. 
	E.g., ``states dominated by single/double excitations'' should be used instead. }
	\\
	\alert{We have modified these terms in accordance with the reviewer's comment.}

	\item 
	{Tables: the numbers in parentheses at the FCI values is probably the uncertainty of the FCI excitation energy. 
	This should be mentioned in the caption of the tables. }
	\\
	\alert{Thank you for spotting this. This has been added.}

	\item 
	{Sect. II, last para: system considered $\to$ systems considered.}
	\\
	\alert{Fixed.}

	\item 
	{Ref. 69: gaussian-2 $\to$ Gaussian-2}
	\\
	\alert{Fixed.}

\end{itemize}

\end{letter}
\end{document}

### 2021-05-24 Manuscript/CC4.tex
response letter

@@
 We report the first investigation of the performance of EOM-CC4 --- an approximate equation-of-motion coupled-cluster model which includes iterative quadruple excitations --- for vertical excitation energies in molecular systems.
-By considering a set of 28 excited states in 10 small molecules for which we have computed CCSDTQP and FCI reference energies, we show that, in the case of excited states with a dominant contribution from the single excitations, CC4 yields excitation energies with sub-kJ~mol$^{-1}$ accuracy, in very close agreement with its more expensive CCSDTQ parent.
+By considering a set of 28 excited states in 10 small molecules for which we have computed CCSDTQP and FCI reference energies, we show that, in the case of excited states with a dominant contribution from the single excitations, CC4 yields excitation energies with sub-kJ~mol$^{-1}$ accuracy \alert{(\textit{i.e.}, error below $0.01$ eV)}, in very close agreement with its more expensive CCSDTQ parent.
 Therefore, if one aims at high accuracy, CC4 stands as a highly competitive approximate method to model molecular excited states, with a significant improvement over both CC3 and CCSDT.
-Our results also evidence that, although the same qualitative conclusions hold, one cannot reach the same level of accuracy for transitions of double excitation nature.
+Our results also evidence that, although the same qualitative conclusions hold, one cannot reach the same level of accuracy for transitions \alert{with a dominant contribution from the double excitations}.
 \end{abstract}
@@
 Although a small number of studies have been published on the performance of CC4 for ground-state energies and properties, \cite{Kallay_2005,Matthews_2021} this work stands, to the best of our knowledge, as the first to consider CC4 for the computation of excited-states energies.
-As we shall see below, CC4 is an excellent approximation to its CCSDTQ parent, and produces, in the case of excited states with a dominant contribution from the single excitations, excitation energies with sub-\si{\kJ\per\mol} accuracy for this set of small molecules, well below the chemical accuracy threshold.
+As we shall see below, CC4 is an excellent approximation to its CCSDTQ parent, and produces, in the case of excited states with a dominant contribution from the single excitations, excitation energies with sub-\si{\kJ\per\mol} accuracy \alert{(\textit{i.e.}, error below $0.01$ eV)} for this set of small molecules, well below the chemical accuracy threshold.
 
@@
 
-All calculations have been performed in the frozen-core approximation and the CC3/aug-cc-pVTZ geometries of the system considered here have been extracted from previous studies.
+All calculations have been performed in the frozen-core approximation and the CC3/aug-cc-pVTZ geometries of the \alert{systems considered} here have been extracted from previous studies.
 \cite{Loos_2018a,Chrayteh_2021}
@@
 	For the aug-cc-pVDZ basis, the mean absolute error (MAE), mean signed error (MSE), and maximum error (Max) with respect to CCSDTQP is reported.
+	\alert{The error bars reported in parenthesis correspond to one standard deviation.}
 	\label{tab:singles}}
@@
 \begin{table}
-	\caption{Vertical excitation energies (in eV) of a selection of doubly-excited states obtained at various levels of theory with the aug-cc-pVDZ basis set. 
+	\caption{Vertical excitation energies (in eV) for a selection of \alert{transitions with a dominant contribution from the double excitations} obtained at various levels of theory with the aug-cc-pVDZ basis set.
 	$\%T_1$ is the percentage of single excitations involved in the transition (computed at the CC3/aug-cc-pVTZ level).
@@
 	Error in excitation energies (with respect to FCI) computed with CC3, CCSDT, CC4, and CCSDTQ in the aug-cc-pVDZ basis
-	for the double excitations gathered in Table \ref{tab:doubles}.
+	for \alert{transitions with a dominant contribution from the double excitations} gathered in Table \ref{tab:doubles}.
 	\label{fig:doubles}}
@@
 This suggests that the performance of the various CC models discussed above might be highly dependent on the nature of the transitions, as discussed in Ref.~\onlinecite{Loos_2019}.
-To investigate further this point, we report in Table \ref{tab:doubles} vertical excitation energies for double excitations (\ie, transition with a dominant contribution from the doubly-excited determinants) in the carbon dimer, \ce{C2}, and nitroxyl, \ce{HNO}, computed with the aug-cc-pVDZ basis for the methods including at least triple excitations; the second-order methods, CC2 and CCSD, being unable to faithfully locate double excitations.
+To investigate further this point, we report in Table \ref{tab:doubles} vertical excitation energies for \titou{transitions with a dominant contribution from the doubly-excited determinants} in the carbon dimer, \ce{C2}, and nitroxyl, \ce{HNO}, computed with the aug-cc-pVDZ basis for the methods including at least triple excitations; the second-order methods, CC2 and CCSD, being unable to faithfully locate these \titou{states with a large contribution of double excitations.}
 These transitions can be labeled as ``pure'' double excitations as they involve an insignificant amount of single excitations ($\%T_1 \approx 0$), hence providing a very stringent test for the EOM-CC formalism.
@@
 Thanks to the results gathered in the present study, we can conclude, for this set of small molecules at least, that CC4 is a rather competitive approximation to its more expensive CCSDTQ parent as well as a very significant improvement over both its third-order version, CC3, and the ``complete'' CCSDT method.
-This is particularly true in the case of single excitations (Table \ref{tab:singles}) when one reaches sub-kJ~mol$^{-1}$ accuracy.
-For double excitations, we have seen (Table \ref{tab:doubles}) that the same qualitative conclusions hold but one cannot reach chemical accuracy for the set of ``pure'' double excitations that we have considered.
+This is particularly true in the case of \alert{transitions with a dominant contribution from the single excitations} (Table \ref{tab:singles}) when one reaches sub-kJ~mol$^{-1}$ accuracy.
+\titou{For states with a dominant contribution from the double excitations}, we have seen (Table \ref{tab:doubles}) that the same qualitative conclusions hold but one cannot reach chemical accuracy for the set of ``pure'' double excitations that we have considered.
 

### 2021-05-26 Manuscript/CC4.tex
CC4 updated accepted version

@@
 
-\newcommand{\alert}[1]{\textcolor{red}{#1}}
+\newcommand{\alert}[1]{\textcolor{black}{#1}}
 \usepackage[normalem]{ulem}
-\newcommand{\titou}[1]{\textcolor{red}{#1}}
-\newcommand{\trashPFL}[1]{\textcolor{red}{\sout{#1}}}
-\newcommand{\PFL}[1]{\titou{(\underline{\bf PFL}: #1)}}
 
@@
 	For the aug-cc-pVDZ basis, the mean absolute error (MAE), mean signed error (MSE), and maximum error (Max) with respect to CCSDTQP is reported.
-	\alert{The error bars reported in parenthesis correspond to one standard deviation.}
+	\alert{For the FCI data, the error bars reported in parenthesis correspond to one standard deviation.}
 	\label{tab:singles}}
@@
 				&	$^1\Sigma_g^+$ &	1		&3.283	&2.874	&2.602	&2.521	&2.505	&2.503(1)	\\	
-	\ce{HNO}	&	$^1A'$ 			&	0		&5.247	&4.756	&4.454	&4.424	&		&4.399(2)	\\
+	\ce{HNO}	&	$^1A'$ 			&	0		&5.247	&4.756	&4.454	&4.424	&		&4.397(1)	\\
 	\end{tabular}
@@
 This suggests that the performance of the various CC models discussed above might be highly dependent on the nature of the transitions, as discussed in Ref.~\onlinecite{Loos_2019}.
-To investigate further this point, we report in Table \ref{tab:doubles} vertical excitation energies for \titou{transitions with a dominant contribution from the doubly-excited determinants} in the carbon dimer, \ce{C2}, and nitroxyl, \ce{HNO}, computed with the aug-cc-pVDZ basis for the methods including at least triple excitations; the second-order methods, CC2 and CCSD, being unable to faithfully locate these \titou{states with a large contribution of double excitations.}
+To investigate further this point, we report in Table \ref{tab:doubles} vertical excitation energies for \alert{transitions with a dominant contribution from the doubly-excited determinants} in the carbon dimer, \ce{C2}, and nitroxyl, \ce{HNO}, computed with the aug-cc-pVDZ basis for the methods including at least triple excitations; the second-order methods, CC2 and CCSD, being unable to faithfully locate these \alert{states with a large contribution of double excitations.}
 These transitions can be labeled as ``pure'' double excitations as they involve an insignificant amount of single excitations ($\%T_1 \approx 0$), hence providing a very stringent test for the EOM-CC formalism.
@@
 This is particularly true in the case of \alert{transitions with a dominant contribution from the single excitations} (Table \ref{tab:singles}) when one reaches sub-kJ~mol$^{-1}$ accuracy.
-\titou{For states with a dominant contribution from the double excitations}, we have seen (Table \ref{tab:doubles}) that the same qualitative conclusions hold but one cannot reach chemical accuracy for the set of ``pure'' double excitations that we have considered.
+\alert{For states with a dominant contribution from the double excitations}, we have seen (Table \ref{tab:doubles}) that the same qualitative conclusions hold but one cannot reach chemical accuracy for the set of ``pure'' double excitations that we have considered.
 
